### 2023-03-28 outputs/paper/paper.qmd
new

---
title: "Exploring Relationships between Demographic Characteristics, Health, Finances, Living Arrangements, and Happiness: An Analysis of the General Social Survey (GSS) Data from 1972 to 2012"
subtitle: ""
author: 
  - SHAOHAN CHANG
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This paper presents an analysis of a subset of the General Social Survey (GSS) data from the year 1972, which includes information on individuals' demographic characteristics, health, finances, living arrangements, and subjective well-being. The study aimed to explore various aspects of individuals' lives during the early 1970s in the United States, such as social stratification, gender roles, family dynamics, health disparities, and subjective well-being.The dataset consists of 5 observations and 10 variables, including year, age, sex, babies, divorce, health, finance_satisfied, living_area, and happy. The study used graphical representation to analyze the relationships between different variables in the dataset and individuals' level of happiness. The results of the analysis suggest that there is a positive relationship between people's satisfaction with their current financial situation, their self-rated health, and their level of happiness in life. Additionally, being divorced may have a slight impact on one's level of happiness in life, with a small proportion of individuals feeling not too happy. Moreover, the study found that people's level of education is positively associated with their level of happiness in life, as people's education level increases, their level of happiness also gradually increases.Overall, this study provides valuable insights into various aspects of individuals' lives during the early 1970s in the United States. The findings can be useful for researchers and students interested in exploring topics such as social stratification, gender roles, family dynamics, health disparities, and subjective well-being. The study highlights the importance of considering different factors that can influence individuals' level of happiness and well-being, such as their financial situation, health status, and level of education. Further research could investigate more recent data from the GSS to examine changes in these relationships over time."
format: pdf
number-sections: true
bibliography: references.bib
---

# Introduction

Surveys are a common method for collecting data on individuals' attitudes, behaviors, and experiences in social science research. One such survey is the General Social Survey (GSS), which has been conducted in the United States since 1972 to 2012. This data set is a subset of the GSS data from the year 1972, which includes information on individuals' demographic characteristics, health, finances, living arrangements, and subjective well-being. While this is a relatively small data set, it provides a glimpse into the lives of individuals in the United States during a particular period in time.This paper aims to explore various aspects of individuals' lives during the early 1970s in the United States using the GSS data set. The variables in this data set are diverse and reflect a range of aspects of individuals' lives. For instance, the variables on babies and divorce provide information on individuals' family structures, while the variables on health and finance satisfaction offer insights into their well-being and financial stability [@b]. The data set also includes variables on individuals' living arrangements and their subjective well-being, providing a glimpse into their social context and overall happiness.

The paper presents a comprehensive analysis of the relationships between different variables in the data set and individuals' level of happiness. The analysis includes a graphical representation of the relationship between the number of children and happiness in the family, individuals' self-rated health and their self-rated level of happiness, people's satisfaction with their financial situation and their happiness, the level of happiness in life for individuals in two different states: divorced or married, and the relationship between people's level of education and their level of happiness in life.The results of the analysis suggest that there is a positive relationship between people's satisfaction with their current financial situation, their self-rated health, and their level of happiness in life [@a]. The analysis also indicates that being divorced may have a slight impact on one's level of happiness in life, with a small proportion of individuals feeling "not too happy." Additionally, as people's education level increases, their level of happiness also gradually increases.

Overall, this paper provides valuable insights into various aspects of individuals' lives during the early 1970s in the United States. The findings can be useful for researchers and students interested in exploring topics such as social stratification, gender roles, family dynamics, health disparities, and subjective well-being.

## Methodology

This study will combine data sources, including surveys and academic literature. The collected data will be analyzed to determine the trends and changes in public attitudes towards sexual morality over time (1972 to 2012). The study will also examine differences in attitudes between men and women, as well as work attitudes, and the relationship between education levels and happiness in daily life.

# Data Resource

Used some R language packages, such as tidyverse [@ti], dplyr [@dplyr], janitor [@janitor] , knitr [@knitr], here [@here], haven [@haven], ggplot [@ggplot] , kableExtra [@kableExtra] to assist in data analysis, and the data from General Social Survey [@gss].

## Data {#sec-data}

After cleaning the data and selecting the main variables, the following table shows the first five rows of data and their corresponding parameters.The following data section provides a more detailed explanation of the selected variables for the data.

```{r}
#| echo: false
#| warning: false
library(tidyverse)
library(dplyr)
library(tidyr)
library(kableExtra)
library(janitor)
library(knitr)
library(haven)
library(here)
library(ggplot2)
library(tinytex)
data <- read_csv(here::here("inputs/data/cleaned_data.csv"))
```

This data-set contains information on various personal and demographic characteristics of individuals, collected between the years 1972 and 2012. The data-set includes variables such as age, sex, number of babies, divorce status, self-reported health status, financial satisfaction, living area, and level of happiness. The data-set can be used to study the relationships between these variables and to gain insights into factors that may influence an individual's overall life satisfaction.

```{r}
#| eval: true
#| warning: false
#| echo: false
data %>%
  select(1:8) %>%
  slice(1:5) %>%
  kable(caption = "Table of Happy by Various Variables") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

```

```{r}
#| eval: true
#| warning: false
#| echo: false
#| label: table-one
#| table-cap: Report Data (First 5 rows)

data %>%
  select(-1:-8) %>%
  slice(1:5) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

-   year: This variable indicates the year in which the data was collected. In this data-set, all the observations are from the year 1972 to 2012.
-   age: This variable indicates the age of the individual at the time the data was collected. It is a continuous variable measured in years.
-   sex: This variable indicates the biological sex of the individual. It is a categorical variable with two levels: male and female.
-   babies: This variable indicates the number of babies the individual had at the time the data was collected. It is a categorical variable with different levels, depending on the number of babies: 0, 1, 2, 3, 4, or 5+.
-   divorce: This variable indicates whether or not the individual had ever been divorced at the time the data was collected. It is a categorical variable with two levels: yes and no.
-   health: This variable indicates the self-reported health status of the individual at the time the data was collected. It is a categorical variable with different levels, depending on the health status: excellent, good, fair, or poor.
-   finance_satisfied: This variable indicates the individual's level of satisfaction with their current financial situation. It is a categorical variable with different levels of satisfaction: very satisfied, more or less satisfied, not very satisfied, and not at all satisfied.
-   living_area: This variable indicates the type of living area in which the individual resided at the time the data was collected. It is a categorical variable with different levels: large city, small city, suburban, and rural.
-   happy: This variable indicates the individual's level of happiness or life satisfaction. It is a categorical variable with different levels of happiness: very happy, pretty happy, not too happy, and not at all happy.

In [@fig-one], this chart shows the number of people who are very happy, not too happy, and happy. Overall, the data indicates that the largest number of people are happy, with approximately 15,000 individuals falling into this category. On the other hand, the smallest number of people are not too happy, with significantly fewer individuals in this category compared to the other two variables. In summary, the data suggests that the number of unhappy individuals is a relatively small group.

```{r}
#| label: fig-one
#| fig-cap: Couning of Happiness
#| echo: false
#| warning: false

ggplot(data, aes(x = happy, fill = happy)) +
  geom_bar() +
  scale_fill_manual(values = c("#FFC107", "#FF5722", "#4CAF50", "#2196F3")) +
  labs(fill = "Happiness level")+
  coord_flip()

```

### Baby

In [@fig-two], through the graph showing the relationship between the number of children and happiness in the family, it is obvious that when people have no children, the largest number of 'very happy', 'pretty happy', and 'not too happy' are shown. Although The preliminary judgment is that the number of people who are happy without children is the largest. But among the data, the data collected without children is the most. In order to ensure the accuracy of the data, it is necessary to further analyze the proportion of the number of children in the family for the next part of the analysis.

```{r}
#| label: fig-two
#| fig-cap: Relationship between Number of Babies and Happiness
#| echo: false
#| warning: false

data %>% 
  filter(babies != "unknown") %>% 
  group_by(babies, happy) %>% 
  summarize(n = n()) %>% 
  mutate(prop = n / sum(n)) %>% 
  ggplot(aes(x = factor(babies), y = prop, group = happy, color = happy)) +
  geom_line(size = 1.5) +
  stat_smooth(geom = "ribbon", alpha = 0.2) +
  scale_x_discrete(name = "Number of Babies", expand = c(0.1, 0.1)) +
  scale_y_continuous(labels = scales::percent_format(), name = "Percentage", expand = c(0.05, 0)) +
  scale_color_discrete(name = "Happiness") +
  theme_minimal() +
  theme(plot.title = element_text(size = 16, face = "bold", margin = margin(b = 10)),
        plot.subtitle = element_text(size = 14, margin = margin(b = 20)),
        axis.title = element_text(size = 12, face = "bold"),
        axis.text = element_text(size = 10),
        legend.title = element_text(size = 12, face = "bold"),
        legend.text = element_text(size = 10),
        legend.position = "bottom")

```

In [@fig-three], which to provide a more detailed and comprehensive view of the data, the chart displays an analysis and visualization of the number of children had each year from 1972 to 2012, in relation to the level of happiness. In regards to the variable "not too happy," the proportion of individuals who reported feeling unhappy was relatively high in 1974, 1985, 1993, 2004, 2006, and 2008. On the other hand, in regards to the variable "happy," the percentage of individuals reporting feeling happy was relatively high in 1973, 1977, 1994, 2006, and 2012.

```{r fig.width= 9,fig.height= 6}
#| label: fig-three
#| fig-cap: Relationship between Number of Babies and Happiness by Year
#| echo: false
#| warning: false

data %>%
  filter(babies != "unknown") %>%
  group_by(year, babies, happy) %>%
  summarize(n = n()) %>%
  mutate(prop = n / sum(n)) %>%
  ggplot(aes(x = factor(babies), y = prop, group = happy, color = happy)) +
  geom_line(size = 1.5) +
  stat_smooth(geom = "ribbon", alpha = 0.2) +
  facet_wrap(~ year) +
  scale_x_discrete(name = "Number of Babies", expand = c(0.1, 0.1)) +
  scale_y_continuous(labels = scales::percent_format(), name = "Percentage", expand = c(0.05, 0)) +
  scale_color_discrete(name = "Happiness") +
  theme_minimal() +
  theme(plot.title = element_text(size = 14, face = "bold", margin = margin(b = 10)),
        plot.subtitle = element_text(size = 14, margin = margin(b = 20)),
        axis.title = element_text(size = 12, face = "bold"),
        axis.text = element_text(size = 10),
        legend.title = element_text(size = 12, face = "bold"),
        legend.text = element_text(size = 10),
        legend.position = "bottom")

```

### Health

In [@fig-four], which represents the relationship between participants' self-rated health and their self-rated level of happiness. The chart shows that the proportion of participants who rated themselves as "very happy" was the highest among those who rated their health as "excellent". On the other hand, the proportion of participants who rated themselves as "not too happy" was the lowest among those who rated their health as "poor".From the overall trend, it can be inferred that the higher the participants' self-rated health, the higher their self-rated level of satisfaction with life.

```{r}
#| label: fig-four
#| fig-cap: Relationship between Health and Happiness
#| echo: false
#| warning: false
ggplot(data, aes(x = health, fill = happy)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Health", y = "Percentage of Happy Cases") +
  theme_minimal() +
  coord_flip()
```

In [@fig-five], which spanning from 1970 to 2010, illustrates the relationship between participants' self-reported happiness levels and their health states. It is evident that when participants rated their health as 'poor', the proportion of those who identified as 'very happy' was notably lower compared to other health states. On the other hand, when participants reported their health as 'excellent' or 'good', the number of 'very happy' responses regarding their life satisfaction increased significantly. In summary, this chart suggests a positive correlation between people's health and their happiness in life.

```{r}
#| label: fig-five
#| fig-cap: Relationship between Health and "Very Happy" With Year
#| echo: false
#| warning: false
ggplot(data[data$happy == "very happy", ], aes(x = year, y = health)) +
  geom_point(position = position_jitter(width = 0.2, height = 0.1), size = 2, color = "#4daf4a") +
  facet_wrap(~health, ncol = 5, scales = "free_y") +
  labs(x = "Year", y = "Self-rated Health") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.major.x = element_line(color = "grey", size = 0.1),
        strip.text = element_text(size = 10),
        panel.spacing = unit(0.2, "lines"))

```

### Financial Satisfaction

In [@fig-six], the graph depicts the relationship between people's satisfaction with their financial situation and their happiness.It is clear that when people are not very satisfied with their current finances, the proportion of unhappy people in their lives is the highest. On the other hand, when people are very satisfied with their finances, the proportion of happy people in their lives is the highest, and the proportion of unhappy people is also the lowest. Therefore, it can be concluded that there is a positive relationship between people's satisfaction with their current financial situation and their level of happiness in life.

```{r}
#| label: fig-six
#| fig-cap: Relationship between Happiness and finance satified
#| echo: false
#| warning: false
#| 
ggplot(data, aes(x = finance_satified, fill = happy)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Rate of Finance Satified ",
       y = "Percentage of Happy Cases") +
  theme_minimal() +
  coord_flip()
```

### Divorce

In [@fig-seven], the graph represents the level of happiness in life for individuals in two different states: divorced or married. The graph shows that the levels of happiness in both marital states are almost similar. However, the proportion of people who feel "not too happy" in their lives is slightly higher among the divorced group than among the married group. In conclusion, being divorced may have a slight impact on one's level of happiness in life, with a small proportion of individuals feeling "not too happy."

```{r}
#| label: fig-seven
#| fig-cap: Relationship between Happiness and Divorce
#| echo: false
#| warning: false
ggplot(data, aes(x = divorce, fill = happy)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Divorce",
       y = "Percentage of Happy Cases") +
  theme_minimal() +
  coord_flip()

```

In [@fig-eight], which based on the analysis of the charts, it appears that for the years 1972, 1975, 1982, 1990, 1996, 2002, and 2010, individuals who reported being divorced also reported a higher percentage of happy responses. On the other hand, for the years 1976, 1980, 1984, 1987, 1989, and 2006, individuals who reported being married reported a higher percentage of happy responses. Additionally, the percentage of individuals who reported "not too happy" was significantly higher for individuals who reported being divorced than for those who reported being married in the years 1973, 1984, 1987, 1990, 1991, 1993, 2008, and 2012.

```{r fig.width= 8,fig.height= 4}
#| label: fig-eight 
#| fig-cap: Relationship between Divorce and Happiness by Year
#| echo: false
#| warning: false
data %>%
  filter(divorce != "unknown") %>%
  group_by(year, divorce, happy) %>%
  summarize(n = n()) %>%
  mutate(prop = n / sum(n)) %>%
  ggplot(aes(x = factor(divorce), y = prop, group = happy, color = happy)) +
  geom_line(size = 1.5) +
  stat_smooth(geom = "ribbon", alpha = 0.2) +
  facet_wrap(~ year, nrow = 2) +
  scale_x_discrete(name = "Divorce", expand = c(0.1, 0.1)) +
  scale_y_continuous(labels = scales::percent_format(), name = "Percentage", expand = c(0.05, 0)) +
  scale_color_discrete(name = "Happiness") +
  theme_minimal() +
  theme(plot.title = element_text(size = 16, face = "bold", margin = margin(b = 10)),
        plot.subtitle = element_text(size = 14, margin = margin(b = 20)),
        axis.title = element_text(size = 12, face = "bold"),
        axis.text = element_text(size = 10),
        legend.title = element_text(size = 12, face = "bold"),
        legend.text = element_text(size = 10),
        legend.position = "bottom")

```

### Degree

In [@fig-nine], which shows that there is a certain relationship between people's level of education and their level of happiness in life. From the graph, it can be observed that the proportion of people who feel "not too happy" is the highest among those with education levels lower than high school. However, the proportion of unhappy individuals is the lowest among those with bachelor's and graduate degrees, suggesting that as people's education level increases, their level of happiness also gradually increases.

```{r}
#| label: fig-nine
#| fig-cap: Relationship between Happiness and Degree
#| echo: false
#| warning: false
ggplot(data, aes(x = degree, fill = happy)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Degree",
       y = "Percentage of Happy Cases") +
  theme_minimal() +
  coord_flip()

```

# Model

```{r}
#| warning: false
#| echo: false
# create a new variable "divorce_score" based on the "divorce" variable
data$divorce_score <- ifelse(data$divorce == "no", 0, 1)

data$happy_score <- ifelse(data$happy == "not too happy", 1,
                      ifelse(data$happy == "not satisfied at all", 2,
                      ifelse(data$happy == "more or less satisfied", 3,
                      ifelse(data$happy == "pretty well satisfied", 4, 5))))

# Create ordinal variable for degree score
data$degree_score <- ifelse(data$degree == "Less than high school", 1,
                            ifelse(data$degree == "High school graduate", 2,
                                   ifelse(data$degree == "Some college", 3,
                                          ifelse(data$degree == "Bachelor's degree", 4,
                                                 ifelse(data$degree == "Advanced degree", 5, NA)))))

# Create ordinal variable for health score
data$health_score <- ifelse(data$health == "Poor", 1,
                            ifelse(data$health == "Fair", 2,
                                   ifelse(data$health == "Good", 3,
                                          ifelse(data$health == "Very good", 4,
                                                 ifelse(data$health == "Excellent", 5, NA)))))

# Create ordinal variable for finance score
data$finance_score <- ifelse(data$finance_satified == "Not at all satisfied", 1,
                            ifelse(data$finance_satified == "Not too satisfied", 2,
                                   ifelse(data$finance_satified == "More or less satisfied", 3,
                                          ifelse(data$finance_satified == "Pretty well satisfied", 4,
                                                 ifelse(data$finance_satified == "Completely satisfied", 5, NA)))))

# convert age variable from character to numeric
data$age <- as.numeric(data$age)

# perform linear regression of age and divorce_score
model <- lm(happy_score ~ age +  degree + finance_satified + health + divorce, data=data)
model
```

# summary

## Table of Relationship between Number of Children and Happiness in the Family.

In the table two, which appears to be presenting data on the happiness levels of babies, as rated by some measure or criteria, at different ages from 0 to 4 years old. The three categories of happiness levels are "not too happy," "happy," and "very happy." Looking at the data for 4-year-old, we can see that 48.15% of them were rated as "not too happy," 14.81% as "very happy," and the remaining 37.04% as simply "happy." This suggests that the majority of 4-year-old were not rated as particularly happy, with less than half of them falling into the happy or very happy categories.

```{r}
#| eval: true
#| warning: false
#| echo: false
#| label: table-two
#| table-cap: Table of Happy by Various Variables
happy_table <- data %>% 
  filter(babies != "unknown") %>%
  group_by(babies, happy) %>% 
  summarize(response = n(), variance = var(as.numeric(happy))) %>%
  mutate(percent = round(response/sum(response)*100, 2)) %>%
  select(babies, happy, percent) %>%
  spread(happy, percent)

kable(happy_table, caption = "Table of Happy by Various Variables") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

```

## Table of Health and Happiness in the Family

In table three, which appears to be presenting data on the relationship between the health and happiness levels of families, based on some measure or criteria. The three categories of happiness levels are "not too happy," "happy," and "very happy," while the four categories of health are "excellent," "fair," "good," and "poor." Looking at the data, we can see that families who rated their health as "excellent" had the highest proportion of respondents who reported being "very happy," at 53.70%, and the lowest proportion of those who were "not too happy," at only 4.94%. In contrast, families who rated their health as "fair" had the highest proportion of respondents who were "not too happy," at 15.92%, and the lowest proportion of those who were "very happy," at only 25.81%.

```{r}
#| eval: true
#| warning: false
#| echo: false
#| label: table-three
#| table-cap: Table of Health and Happiness in the Family
health_happy_table <- data %>%
  group_by(health, happy) %>%
  summarize(response = n(), variance = var(as.numeric(happy))) %>%
  mutate(percent = round(response / sum(response) * 100, 2)) %>%
  select(health, happy, percent) %>%
  spread(happy, percent)

kable(health_happy_table, caption = "Table of Health and Happiness in the Family") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

```

## Table of Financial Satisfaction and Happiness in the Family

In table four, which appears that the table is presenting data on the relationship between financial satisfaction and happiness levels in families, based on some measure or criteria. The three categories of happiness levels are "not too happy," "happy," and "very happy," while the three categories of financial satisfaction are "more or less satisfied," "not satisfied at all," and "pretty well satisfied." Looking at the data, we can see that families who reported being "pretty well satisfied" with their finances had the highest proportion of respondents who were "very happy," at 52.0%, and the lowest proportion of those who were "not too happy," at only 5.24%. On the other hand, families who reported being "not satisfied at all" with their finances had the highest proportion of respondents who were "not too happy," at 20.92%, and the lowest proportion of those who were "very happy," at only 22.5%.

```{r}
#| eval: true
#| warning: false
#| echo: false
#| label: table-four
#| table-cap: Table of Financial Satisfaction and Happiness in the Family

finance_happy_table <- data %>%
  group_by(finance_satified, happy) %>%
  summarize(response = n(), variance = var(as.numeric(happy))) %>%
  mutate(percent = round(response / sum(response) * 100, 2)) %>%
  select(finance_satified, happy, percent) %>%
  spread(happy, percent)

kable(finance_happy_table, caption = "Table of Financial Satisfaction and Happiness in the Family") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

```

In table five, which appears to be presenting data on the relationship between divorce and happiness levels in families, based on some measure or criteria. The three categories of happiness levels are "not too happy," "happy," and "very happy," while the two categories of divorce are "no" and "yes." Looking at the data, we can see that there are only small differences in the proportions of families who reported being "happy" or "not too happy" depending on whether or not they had experienced divorce. Specifically, families who reported "no" to divorce had a slightly higher proportion of respondents who were "very happy," at 38.61%, compared to those who reported "yes" to divorce, at 36.24%. However, families who reported "yes" to divorce had a slightly higher proportion of respondents who were "not too happy," at 11.53%, compared to those who reported "no" to divorce, at 9.29%.

```{r}
#| eval: true
#| warning: false
#| echo: false
#| label: table-five
#| table-cap: Table of Divorce and Happiness in the Family
divorce_happy_table <- data %>%
  group_by(divorce, happy) %>%
  summarize(response = n(), variance = var(as.numeric(happy))) %>%
  mutate(percent = round(response / sum(response) * 100, 2)) %>%
  select(divorce, happy, percent) %>%
  spread(happy, percent)

kable(divorce_happy_table, caption = "Table of Divorce and Happiness in the Family") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

```

In table six, which appears to be presenting data on the relationship between educational attainment and happiness levels in families, based on some measure or criteria. The three categories of happiness levels are "not too happy," "happy," and "very happy," while the categories of educational attainment are "associate/junior college," "bachelor's," "graduate," "high school," and "less than high school." Looking at the data, we can see that families with different levels of educational attainment generally reported similar levels of happiness. The proportions of respondents who reported being "very happy" were similar across all levels of educational attainment, ranging from 41.24% for those with an associate/junior college degree to 44.28% for those with a graduate degree. The proportions of respondents who reported being "not too happy" were also similar across all levels of educational attainment, ranging from 5.26% for those with a graduate degree to 14.96% for those with less than a high school education.

```{r}
#| eval: true
#| warning: false
#| echo: false
#| label: table-six
#| table-cap: Table of Degree and Happiness in the Family
degree_happy_table <- data %>%
  group_by(degree, happy) %>%
  summarize(response = n(), variance = var(as.numeric(happy))) %>%
  mutate(percent = round(response / sum(response) * 100, 2)) %>%
  select(degree, happy, percent) %>%
  spread(happy, percent)

kable(degree_happy_table, caption = "Table of Degree and Happiness in the Family") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

```

# Results

The analysis of the General Social Survey data-set from 1972 provides insights into various aspects of individuals' lives in the United States during that time period. The results suggest that several variables, such as financial satisfaction, self-reported health status, and level of education, have a positive relationship with individuals' level of happiness.Regarding family dynamics, the analysis indicates that individuals with no children reported the highest levels of happiness, although the data set's limitations require further exploration of the proportion of individuals with different numbers of children. Being divorced may have a slight impact on one's level of happiness in life, with a small proportion of individuals feeling "not too happy" compared to married individuals.

Furthermore, the analysis suggests that individuals' self-rated health status has a positive relationship with their self-rated level of happiness. The higher the participants' self-rated health, the higher their self-rated level of satisfaction with life. Similarly, there is a positive relationship between people's satisfaction with their current financial situation and their level of happiness in life. The higher people's satisfaction with their finances, the higher their level of happiness.The analysis suggests that there is a certain relationship between people's level of education and their level of happiness in life. The proportion of people who feel "not too happy" is the highest among those with education levels lower than high school. However, the proportion of unhappy individuals is the lowest among those with bachelor's and graduate degrees, suggesting that as people's education level increases, their level of happiness also gradually increases.

Overall, these findings provide valuable insights into the factors that may influence individuals' overall life satisfaction during the early 1970s in the United States. The results can be useful for researchers and students interested in exploring topics such as social stratification, gender roles, family dynamics, health disparities, and subjective well-being.

# Discussion

## Factors influencing individuals' level of happiness

The study's findings on the positive relationship between financial satisfaction, health, and happiness underscore the importance of financial stability and access to healthcare for overall well-being. These findings have important implications for policymakers and practitioners working to improve individuals' quality of life [@c] . For example, policies aimed at increasing access to affordable healthcare and financial assistance programs can help individuals improve their financial stability and access to essential services, ultimately contributing to overall well-being.

The study's results also suggest that education is an important factor in individuals' overall well-being and happiness. As people's education level increases, their level of happiness also gradually increases. This highlights the need for policies and programs that support educational attainment, particularly for disadvantaged populations [@d]. Such programs can include initiatives to improve access to education and financial aid for those who may face barriers to education.

Overall, this study demonstrates the importance of considering various factors that can influence individuals' well-being and happiness. By understanding the complex relationships between different variables, policymakers and practitioners can develop targeted interventions aimed at improving individuals' quality of life. Additionally, the findings can serve as a foundation for further research on the topic, particularly in examining changes in these relationships over time.

## Impact of divorce on individuals' happiness

Divorce is a significant life event that can have profound effects on an individual's overall well-being and happiness. The findings of this study suggest that individuals who have experienced divorce may have lower levels of happiness than those who are married or have never been married. This could be due to a range of factors, including the loss of social support and economic stability that often accompanies divorce [@o].

One possible explanation for the association between divorce and happiness is the impact of social support. Marriage provides a source of emotional support, and individuals who divorce may experience a loss of this support network. Furthermore, divorce can result in the breakdown of extended family relationships, reducing the availability of social support. This loss of social support could contribute to lower levels of happiness and well-being. Economic factors may also play a role in the relationship between divorce and happiness [@e]. Divorce can result in significant financial upheaval, particularly for individuals who were financially dependent on their partner. This financial instability could contribute to lower levels of happiness and well-being, as financial stress can be a significant source of anxiety and depression.

Further research could explore the reasons behind the association between divorce and happiness. Qualitative studies could be conducted to explore the experiences of individuals who have gone through divorce and how this event has affected their well-being. Longitudinal studies could also be conducted to examine changes in individuals' happiness levels before and after a divorce[@f].

Overall, the findings of this study highlight the importance of considering the impact of divorce on individuals' well-being and happiness. Policies and interventions aimed at supporting individuals going through divorce, such as access to counseling and financial support, could help to mitigate the negative effects of this life event and improve individuals' overall well-being.

## The importance of historical context in understanding well-being

The historical context of the early 1970s in the United States is essential in understanding individuals' well-being during that period. Societal norms, values, and attitudes during this time were different from those of today, and these differences could have influenced individuals' well-being. These social movements may have influenced individuals' attitudes towards social stratification, gender roles, and family dynamics, which, in turn, could have affected their well-being.

Understanding the historical context is also essential in developing interventions that can address the unique challenges faced by individuals during a particular period in time [@g]. For example, the economic conditions during the early 1970s, such as high inflation and high unemployment rates, could have affected individuals' financial stability and, ultimately, their well-being. Interventions that address these economic challenges may have had a significant impact on individuals' well-being during this period.

Furthermore, the study's findings can be compared to more recent data to examine changes in the relationships between different factors and well-being over time [@h]. For example, the impact of divorce on well-being may have changed over time, as societal attitudes towards divorce have shifted. Comparing the study's findings to more recent data can provide insights into how societal changes have influenced individuals' well-being over time.Overall, the historical context is essential in understanding individuals' well-being during a particular period in time. The study's focus on the early 1970s in the United States provides valuable insights into the factors that influenced individuals' well-being during that period. These findings can be used to develop interventions that address the unique challenges faced by individuals during a particular historical context, as well as to compare changes in the relationships between different factors and well-being over time.

## Impact of Financial Stability on Happiness

As the analysis of the GSS dataset shows, there is a positive correlation between individuals' satisfaction with their financial situation and overall well-being, an important finding. This correlation underscores the importance of U.S. financial stability in determining a person's happiness in the early 1970s. In this discussion, we will further explore the impact of these factors on individual well-being during that time.

In the early 1970s, the United States was going through a period of economic turmoil. One of the most important factors is the rapid rise in inflation. The country faces a phenomenon known as "stagflation," which is characterized by a stagnant economy, high inflation, and high unemployment. This unusual economic situation is largely attributable to the 1973 oil crisis, which caused a spike in oil prices and disrupted the global economy [@i]. The rise in inflation during this period has a direct impact on individuals' financial satisfaction. As the cost of goods and services increases, people find it a challenge to maintain their previous standard of living [@j]. This is further exacerbated by high unemployment, as many people struggle to find stable employment.Analysis of the GSS dataset highlights the importance of financial stability in determining individual well-being, emphasizing the need for effective economic policies to ensure the financial security and well-being of populations.

## The Role of Education in Happiness

The study found that as an individual's education level increased, their level of happiness also gradually increased. This finding prompts a discussion on the role of education in determining one's overall happiness and well-being during the early 1970s. It would be interesting to explore the potential reasons behind this correlation, such as the opportunities for personal development, improved employment prospects, and social mobility that education provides[@k]. Moreover, examining the accessibility and quality of education during that period could offer further insights into the impact of education on happiness. By understanding the role of education in shaping individuals' happiness, researchers and policymakers can better appreciate the significance of investing in education and ensuring equal access to quality education for all.One possible explanation is that education provides individuals with the tools and resources they need to achieve personal goals and fulfill their potential[@l]. Education can help individuals develop a sense of purpose, autonomy, and mastery, which are important factors in promoting happiness and well-being. In addition, education can provide individuals with the skills and knowledge needed to pursue meaningful and fulfilling careers, which can also contribute to their overall sense of well-being.

Moreover, education can provide opportunities for social mobility, which can enhance individuals' sense of self-worth and life satisfaction. Education can help individuals acquire the social and cultural capital necessary to succeed in their professional and personal lives, which can lead to increased opportunities and social status [@m]. This, in turn, can contribute to individuals' overall sense of happiness and well-being.However, it is important to note that not all forms of education may have the same impact on individuals' happiness and well-being. The accessibility and quality of education are crucial factors that can influence the extent to which education promotes happiness and well-being. For example, individuals who have access to high-quality education may experience greater benefits in terms of personal development, employment prospects, and social mobility than those who do not have access to such education [@n].

Therefore, policymakers and educators must work to ensure that all individuals have equal access to high-quality education. Investing in education can not only promote individuals' personal and professional growth but also contribute to the overall well-being and happiness of society as a whole. By understanding the role of education in shaping individuals' happiness, we can work towards building a more just and equitable society.

# Weaknesses and next steps

## Weakness:

-   The data-set used in the study is small, consisting of only 5 observations and 10 variables, which may limit the generalization of the findings.
-   The study only examines data from the year 1972, which may not be representative of individuals' lives in the United States today or even in the 1970s as a whole.
-   The study only uses graphical representation to analyze the relationships between variables, which may not provide a comprehensive understanding of the complex relationships between variables.
-   The study only examines a limited set of variables and does not consider other factors that could impact individuals' level of happiness and well-being, such as social support, employment status, and cultural factors.

## Next Steps:

-   Further research could expand the data-set to include more observations and variables, which could provide a more comprehensive understanding of individuals' lives during the early 1970s in the United States.
-   Future studies could examine more recent data from the GSS to investigate changes in the relationships between variables over time.
-   Future studies could use more advanced statistical methods to analyze the relationships between variables, such as regression analysis, to provide a more robust understanding of the relationships between variables.
-   Future studies could consider other factors that may impact individuals' level of happiness and well-being, such as social support, employment status, and cultural factors.

\newpage

\appendix

# Appendix {.unnumbered}

# Additional details

## Survey Question

Welcome to this survey on gender differences and equality in education, employment, and well-being. Your participation is crucial in helping us gain a deeper understanding of the factors that contribute to gender disparities and the potential strategies for promoting gender equality in various aspects of life. By answering the following questions, you will provide valuable insights that can be used to inform policies and initiatives aimed at creating a more inclusive and equitable society for all. Please note that your responses will remain confidential and will be used solely for research purposes. We appreciate your time and effort in completing this survey.

Contact Information: If you have any questions or concerns about this survey, please feel free to contact the research team:

NAME : SHAOHAN CHANG Institution/Department : Department of statistics (University of Toronto) Email Address : shaohan.chang\@utoronto.ca

### 1. How many children do you currently have?

a.  0
b.  1
c.  2
d.  3
e.  4
f.  5 or more

#### 2. How would you rate your overall level of happiness or life satisfaction?

a.  Very happy
b.  Pretty happy
c.  Not too happy
d.  Not at all happy

### 3. How would you rate your current health status?

a.  Excellent
b.  Good
c.  Fair
d.  Poor

### 4. How satisfied are you with your current financial situation?

a.  Very satisfied
b.  More or less satisfied
c.  Not very satisfied
d.  Not at all satisfied

### 5. Have you ever been divorced?

a.  Yes
b.  No

### 6. What is your current living area?

a.  Large city
b.  Small city
c.  Suburban
d.  Rural

### 7. What is your age? (Please enter a number)

### 8. What is your biological sex?

a.  Male
b.  Female

### 9. What is the highest level of education you have completed?

a.  Less than high school
b.  High school or equivalent
c.  Some college or associate degree
d.  Bachelor's degree
e.  Graduate or professional degree

### 10. How would you rate your overall level of well-being?

a.  Very good
b.  Good
c.  Fair
d.  Poor

\newpage

# References

### 2023-03-28 scripts/00-simulate_data.R

@@ -1,0 +1,39 @@
+#### Preamble ####
+# Purpose:The code above simulates a dataset called "happiness_and_income" with information on individuals' happiness, income, and other characteristics. 
+#The "set.seed" function sets a specific seed for the random number generator, ensuring that the same random values are generated each time the code is run.
+#The "size_of_population" variable sets the number of individuals in the simulated population.The "tibble" function creates a table with columns for the year of observation, 
+#age, sex, education level ("degree"), job satisfaction ("job_satisfied"), happiness level ("happy"), satisfaction level ("sat"), and age group ("age2").The "sample" function generates 
+#random samples for each of these variables, with the "replace" argument set to TRUE so that each individual can be sampled more than once.The "mutate" function creates a new column for 
+#age group based on the age variable, with individuals grouped into "age 18-39", "age 40-59", or "age 60+" based on their age.Overall, this code is simulating a population of individuals 
+#with varying characteristics, including their level of happiness, income, and education, among other variables. This type of simulation could be used to explore relationships between 
+#these variables and test different hypotheses.
+# Author: SHAOHAN CHANG  
+# Data: 14 March 2023 
+# Contact: SHAOHAN.CHANG@utoronto.ca
+# License: MIT
+# Pre-requisites: You have downloaded the data from the library. To do that:
+## 1. Go the website : https://gss.norc.org/get-the-data/stata
+## 2.Download the all file from 1972 to the 2012 file. 
+## 3. Click the file of download.
+## 4. select the SATA file 
+## 5. Can select all variables by clicking button next to the green colored 'ALL'. Then continue 
+## 6. Create the file, download and save the file. 
+# Any other information needed? 
+## 1. It is important to note the location where the downloaded data file is saved on your computer, as this will be needed when reading the data into R.
+## 2. The downloaded data file is likely to be very large, as it contains survey data from 1972 to 2012. It may be necessary to filter the data to a specific 
+# time period or subset of variables in order to work with it more efficiently.
+## 3. The downloaded data file is likely to be in Stata format, so it will need to be read into R using a package like "haven" or "foreign".
+## 4. It is also important to familiarize oneself with the codebook or documentation for the dataset, which can be found on the GSS website or in the downloaded file. 
+# This will provide information on the variables and their meanings, as well as any codes or missing values used in the dataset.
[…]

### 2023-03-28 scripts/02-data_cleaning.R

@@ -1,0 +1,105 @@
+#### Preamble ####
+# Purpose: The purpose of this code is to clean and preprocess a dataset called "the_raw_data", which contains information about individuals' demographics, 
+#employment status, job satisfaction, and happiness. The code selects relevant variables from the dataset, converts them into factors, and renames them to 
+#more understandable names. It also removes any observations with missing or invalid values and filters the data to only include years between 1972 and 2012 
+#and individuals under the age of 89. Additionally, the code creates a new variable called "age_range" based on the age variable, which categorizes individuals 
+#into different age groups. Finally, the cleaned dataset is saved as a CSV file called "cleaned_data.csv" in the "outputs" folder. The cleaned dataset is now ready 
+# to be used for further analysis and modeling.
+# Author: SHAOHAN CHANG  
+# Data: 14 March 2023 
+# Contact: SHAOHAN.CHANG@utoronto.ca 
+# License: MIT
+# Pre-requisites:
+## 1. Go the website : https://gss.norc.org/get-the-data/stata
+## 2.Scroll down to the "Stata Data" section and click the "Download the GSS Stata data files" link.
+## 3. Select the years you want to download from the list provided. You can select multiple years by holding down the "Ctrl" key on your keyboard while clicking on the years you want.
+## 4. Click the "Download Selected Files" button at the bottom of the page. 
+## 5. On the next page, select the "Stata" file format.
+## 6. Select "ALL" from the dropdown menu next to the green "ALL" button to download all variables.
+## 7. Click the "Create File" button and wait for the file to be generated.
+## 8. Once the file has been created, click the "Download File" button to save the file to your computer.
+# Any other information needed? [...UPDATE THIS...]
+## 1. Make sure to note the location where the downloaded data file is saved on your computer, as you will need to provide the file path when reading the data into R.
+## 2. The GSS data file is likely to be very large, especially if you downloaded the data for multiple years. It may be necessary to filter the data to a specific time period or subset of 
+# variables in order to work with it more efficiently. This can be done using functions like subset() or dplyr::select().
[…]

### 2023-03-28 outputs/paper/paper.qmd
Add files via upload

@@
   - SHAOHAN CHANG
-thanks: "Code and data are available at: LINK."
+thanks: "Code and data are available at: https://github.com/lucas11333/Factor_of_Wellbeing"
 date: "`r Sys.time()`"

### 2023-03-28 outputs/paper/paper.tex
Add files via upload

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Exploring Relationships between Demographic Characteristics, Health, Finances, Living Arrangements, and Happiness: An Analysis of the General Social Survey (GSS) Data from 1972 to 2012},
  pdfauthor={SHAOHAN CHANG},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Exploring Relationships between Demographic Characteristics,
Health, Finances, Living Arrangements, and Happiness: An Analysis of the
General Social Survey (GSS) Data from 1972 to 2012\thanks{Code and data
are available at: https://github.com/lucas11333/Factor\_of\_Wellbeing}}
\author{SHAOHAN CHANG}
\date{28 March 2023}

\begin{document}
\maketitle
\begin{abstract}
This paper presents an analysis of a subset of the General Social Survey
(GSS) data from the year 1972, which includes information on
individuals' demographic characteristics, health, finances, living
arrangements, and subjective well-being. The study aimed to explore
various aspects of individuals' lives during the early 1970s in the
United States, such as social stratification, gender roles, family
dynamics, health disparities, and subjective well-being.The dataset
consists of 5 observations and 10 variables, including year, age, sex,
babies, divorce, health, finance\_satisfied, living\_area, and happy.
The study used graphical representation to analyze the relationships
between different variables in the dataset and individuals' level of
happiness. The results of the analysis suggest that there is a positive
relationship between people's satisfaction with their current financial
situation, their self-rated health, and their level of happiness in
life. Additionally, being divorced may have a slight impact on one's
level of happiness in life, with a small proportion of individuals
feeling not too happy. Moreover, the study found that people's level of
education is positively associated with their level of happiness in
life, as people's education level increases, their level of happiness
also gradually increases.Overall, this study provides valuable insights
into various aspects of individuals' lives during the early 1970s in the
United States. The findings can be useful for researchers and students
interested in exploring topics such as social stratification, gender
roles, family dynamics, health disparities, and subjective well-being.
The study highlights the importance of considering different factors
that can influence individuals' level of happiness and well-being, such
as their financial situation, health status, and level of education.
Further research could investigate more recent data from the GSS to
examine changes in these relationships over time.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, breakable, borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced, interior hidden, boxrule=0pt]}{\end{tcolorbox}}\fi

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Surveys are a common method for collecting data on individuals'
attitudes, behaviors, and experiences in social science research. One
such survey is the General Social Survey (GSS), which has been conducted
in the United States since 1972 to 2012. This data set is a subset of
the GSS data from the year 1972, which includes information on
individuals' demographic characteristics, health, finances, living
arrangements, and subjective well-being. While this is a relatively
small data set, it provides a glimpse into the lives of individuals in
the United States during a particular period in time.This paper aims to
explore various aspects of individuals' lives during the early 1970s in
the United States using the GSS data set. The variables in this data set
are diverse and reflect a range of aspects of individuals' lives. For
instance, the variables on babies and divorce provide information on
individuals' family structures, while the variables on health and
finance satisfaction offer insights into their well-being and financial
stability (Vlaev 2014). The data set also includes variables on
individuals' living arrangements and their subjective well-being,
providing a glimpse into their social context and overall happiness.

The paper presents a comprehensive analysis of the relationships between
different variables in the data set and individuals' level of happiness.
The analysis includes a graphical representation of the relationship
between the number of children and happiness in the family, individuals'
self-rated health and their self-rated level of happiness, people's
satisfaction with their financial situation and their happiness, the
level of happiness in life for individuals in two different states:
divorced or married, and the relationship between people's level of
education and their level of happiness in life.The results of the
analysis suggest that there is a positive relationship between people's
satisfaction with their current financial situation, their self-rated
health, and their level of happiness in life (RSiahpush 2008). The
analysis also indicates that being divorced may have a slight impact on
one's level of happiness in life, with a small proportion of individuals
feeling ``not too happy.'' Additionally, as people's education level
increases, their level of happiness also gradually increases.

Overall, this paper provides valuable insights into various aspects of
individuals' lives during the early 1970s in the United States. The
findings can be useful for researchers and students interested in
exploring topics such as social stratification, gender roles, family
dynamics, health disparities, and subjective well-being.

\hypertarget{methodology}{%
\subsection{Methodology}\label{methodology}}

This study will combine data sources, including surveys and academic
literature. The collected data will be analyzed to determine the trends
and changes in public attitudes towards sexual morality over time (1972
to 2012). The study will also examine differences in attitudes between
men and women, as well as work attitudes, and the relationship between
education levels and happiness in daily life.

\hypertarget{data-resource}{%
\section{Data Resource}\label{data-resource}}

Used some R language packages, such as tidyverse (Wickham et al. 2019),
dplyr (Wickham et al. 2023), janitor (Firke 2023) , knitr (Xie 2014),
here (Müller 2020), haven (Wickham, Miller, and Smith 2022), ggplot
(Wickham 2016) , kableExtra (Zhu 2021) to assist in data analysis, and
the data from General Social Survey ({``GSS General Social Survey''}
2023).

\hypertarget{sec-data}{%
\subsection{Data}\label{sec-data}}

After cleaning the data and selecting the main variables, the following
table shows the first five rows of data and their corresponding
parameters.The following data section provides a more detailed
explanation of the selected variables for the data.

This data-set contains information on various personal and demographic
characteristics of individuals, collected between the years 1972 and
2012. The data-set includes variables such as age, sex, number of
babies, divorce status, self-reported health status, financial
satisfaction, living area, and level of happiness. The data-set can be
used to study the relationships between these variables and to gain
insights into factors that may influence an individual's overall life
satisfaction.

\begin{table}

\caption{Table of Happy by Various Variables}
\centering
\begin{tabular}[t]{r|l|l|l|l|l|l|l}
\hline
year & age & sex & babies & divorce & health & finance\_satified & living\_area\\
\hline
1972 & 70 & male & 0 & no & fair & more or less satisfied & large city\\
\hline
1972 & 48 & female & 0 & no & excellent & pretty well satisfied & large city\\
\hline
1972 & 27 & female & 0 & no & good & not satisfied at all & large city\\
\hline
1972 & 61 & female & 0 & no & good & pretty well satisfied & unknown\\
\hline
1972 & 30 & female & 2 & no & fair & not satisfied at all & unknown\\
\hline
\end{tabular}
\end{table}

\begin{table}
\centering
\begin{tabular}{l|l}
\hline
happy & degree\\
\hline
not too happy & less than high school\\
\hline
happy & high school\\
\hline
not too happy & bachelor's\\
\hline
happy & high school\\
\hline
happy & high school\\
\hline
\end{tabular}
\end{table}

\begin{itemize}
\tightlist
\item
  year: This variable indicates the year in which the data was
  collected. In this data-set, all the observations are from the year
  1972 to 2012.
\item
  age: This variable indicates the age of the individual at the time the
  data was collected. It is a continuous variable measured in years.
\item
  sex: This variable indicates the biological sex of the individual. It
  is a categorical variable with two levels: male and female.
\item
  babies: This variable indicates the number of babies the individual
  had at the time the data was collected. It is a categorical variable
  with different levels, depending on the number of babies: 0, 1, 2, 3,
  4, or 5+.
\item
  divorce: This variable indicates whether or not the individual had
  ever been divorced at the time the data was collected. It is a
  categorical variable with two levels: yes and no.
\item
  health: This variable indicates the self-reported health status of the
  individual at the time the data was collected. It is a categorical
  variable with different levels, depending on the health status:
  excellent, good, fair, or poor.
\item
  finance\_satisfied: This variable indicates the individual's level of
  satisfaction with their current financial situation. It is a
  categorical variable with different levels of satisfaction: very
  satisfied, more or less satisfied, not very satisfied, and not at all
  satisfied.
\item
  living\_area: This variable indicates the type of living area in which
  the individual resided at the time the data was collected. It is a
  categorical variable with different levels: large city, small city,
  suburban, and rural.
\item
  happy: This variable indicates the individual's level of happiness or
  life satisfaction. It is a categorical variable with different levels
  of happiness: very happy, pretty happy, not too happy, and not at all
  happy.
\end{itemize}

In Figure~\ref{fig-one}, this chart shows the number of people who are
very happy, not too happy, and happy. Overall, the data indicates that
the largest number of people are happy, with approximately 15,000
individuals falling into this category. On the other hand, the smallest
number of people are not too happy, with significantly fewer individuals
in this category compared to the other two variables. In summary, the
data suggests that the number of unhappy individuals is a relatively
small group.

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-one-1.pdf}

}

\caption{\label{fig-one}Couning of Happiness}

\end{figure}

\hypertarget{baby}{%
\subsubsection{Baby}\label{baby}}

In Figure~\ref{fig-two}, through the graph showing the relationship
between the number of children and happiness in the family, it is
obvious that when people have no children, the largest number of `very
happy', `pretty happy', and `not too happy' are shown. Although The
preliminary judgment is that the number of people who are happy without
children is the largest. But among the data, the data collected without
children is the most. In order to ensure the accuracy of the data, it is
necessary to further analyze the proportion of the number of children in
the family for the next part of the analysis.

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-two-1.pdf}

}

\caption{\label{fig-two}Relationship between Number of Babies and
Happiness}

\end{figure}

In Figure~\ref{fig-three}, which to provide a more detailed and
comprehensive view of the data, the chart displays an analysis and
visualization of the number of children had each year from 1972 to 2012,
in relation to the level of happiness. In regards to the variable ``not
too happy,'' the proportion of individuals who reported feeling unhappy
was relatively high in 1974, 1985, 1993, 2004, 2006, and 2008. On the
other hand, in regards to the variable ``happy,'' the percentage of
individuals reporting feeling happy was relatively high in 1973, 1977,
1994, 2006, and 2012.

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-three-1.pdf}

}

\caption{\label{fig-three}Relationship between Number of Babies and
Happiness by Year}

\end{figure}

\hypertarget{health}{%
\subsubsection{Health}\label{health}}

In Figure~\ref{fig-four}, which represents the relationship between
participants' self-rated health and their self-rated level of happiness.
The chart shows that the proportion of participants who rated themselves
as ``very happy'' was the highest among those who rated their health as
``excellent''. On the other hand, the proportion of participants who
rated themselves as ``not too happy'' was the lowest among those who
rated their health as ``poor''.From the overall trend, it can be
inferred that the higher the participants' self-rated health, the higher
their self-rated level of satisfaction with life.

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-four-1.pdf}

}

\caption{\label{fig-four}Relationship between Health and Happiness}

\end{figure}

In Figure~\ref{fig-five}, which spanning from 1970 to 2010, illustrates
the relationship between participants' self-reported happiness levels
and their health states. It is evident that when participants rated
their health as `poor', the proportion of those who identified as `very
happy' was notably lower compared to other health states. On the other
hand, when participants reported their health as `excellent' or `good',
the number of `very happy' responses regarding their life satisfaction
increased significantly. In summary, this chart suggests a positive
correlation between people's health and their happiness in life.

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-five-1.pdf}

}

\caption{\label{fig-five}Relationship between Health and ``Very Happy''
With Year}

\end{figure}

\hypertarget{financial-satisfaction}{%
\subsubsection{Financial Satisfaction}\label{financial-satisfaction}}

In Figure~\ref{fig-six}, the graph depicts the relationship between
people's satisfaction with their financial situation and their
happiness.It is clear that when people are not very satisfied with their
current finances, the proportion of unhappy people in their lives is the
highest. On the other hand, when people are very satisfied with their
finances, the proportion of happy people in their lives is the highest,
and the proportion of unhappy people is also the lowest. Therefore, it
can be concluded that there is a positive relationship between people's
satisfaction with their current financial situation and their level of
happiness in life.

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-six-1.pdf}

}

\caption{\label{fig-six}Relationship between Happiness and finance
satified}

\end{figure}

\hypertarget{divorce}{%
\subsubsection{Divorce}\label{divorce}}

In Figure~\ref{fig-seven}, the graph represents the level of happiness
in life for individuals in two different states: divorced or married.
The graph shows that the levels of happiness in both marital states are
almost similar. However, the proportion of people who feel ``not too
happy'' in their lives is slightly higher among the divorced group than
among the married group. In conclusion, being divorced may have a slight
impact on one's level of happiness in life, with a small proportion of
individuals feeling ``not too happy.''

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-seven-1.pdf}

}

\caption{\label{fig-seven}Relationship between Happiness and Divorce}

\end{figure}

In Figure~\ref{fig-eight}, which based on the analysis of the charts, it
appears that for the years 1972, 1975, 1982, 1990, 1996, 2002, and 2010,
individuals who reported being divorced also reported a higher
percentage of happy responses. On the other hand, for the years 1976,
1980, 1984, 1987, 1989, and 2006, individuals who reported being married
reported a higher percentage of happy responses. Additionally, the
percentage of individuals who reported ``not too happy'' was
significantly higher for individuals who reported being divorced than
for those who reported being married in the years 1973, 1984, 1987,
1990, 1991, 1993, 2008, and 2012.

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-eight-1.pdf}

}

\caption{\label{fig-eight}Relationship between Divorce and Happiness by
Year}

\end{figure}

\hypertarget{degree}{%
\subsubsection{Degree}\label{degree}}

In Figure~\ref{fig-nine}, which shows that there is a certain
relationship between people's level of education and their level of
happiness in life. From the graph, it can be observed that the
proportion of people who feel ``not too happy'' is the highest among
those with education levels lower than high school. However, the
proportion of unhappy individuals is the lowest among those with
bachelor's and graduate degrees, suggesting that as people's education
level increases, their level of happiness also gradually increases.

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-nine-1.pdf}

}

\caption{\label{fig-nine}Relationship between Happiness and Degree}

\end{figure}

\hypertarget{model}{%
\section{Model}\label{model}}

\begin{verbatim}

Call:
lm(formula = happy_score ~ age + degree + finance_satified + 
    health + divorce, data = data)

Coefficients:
                          (Intercept)                                    age  
                             4.951478                              -0.002144  
                     degreebachelor's                         degreegraduate  
                             0.028053                               0.026886  
                    degreehigh school            degreeless than high school  
                            -0.005915                              -0.106730  
 finance_satifiednot satisfied at all  finance_satifiedpretty well satisfied  
                            -0.471882                               0.087194  
                           healthfair                             healthgood  
                            -0.315050                              -0.063929  
                           healthpoor                             divorceyes  
                            -0.747780                              -0.018373  
\end{verbatim}

\hypertarget{summary}{%
\section{summary}\label{summary}}

\hypertarget{table-of-relationship-between-number-of-children-and-happiness-in-the-family.}{%
\subsection{Table of Relationship between Number of Children and
Happiness in the
Family.}\label{table-of-relationship-between-number-of-children-and-happiness-in-the-family.}}

In the table two, which appears to be presenting data on the happiness
levels of babies, as rated by some measure or criteria, at different
ages from 0 to 4 years old. The three categories of happiness levels are
``not too happy,'' ``happy,'' and ``very happy.'' Looking at the data
for 4-year-old, we can see that 48.15\% of them were rated as ``not too
happy,'' 14.81\% as ``very happy,'' and the remaining 37.04\% as simply
``happy.'' This suggests that the majority of 4-year-old were not rated
as particularly happy, with less than half of them falling into the
happy or very happy categories.

\begin{table}

\caption{Table of Happy by Various Variables}
\centering
\begin{tabular}[t]{l|r|r|r}
\hline
babies & happy & not too happy & very happy\\
\hline
0 & 51.37 & 10.04 & 38.59\\
\hline
1 & 55.13 & 8.96 & 35.91\\
\hline
2 & 54.97 & 7.46 & 37.57\\
\hline
3 & 52.36 & 10.63 & 37.01\\
\hline
4 & 48.15 & 14.81 & 37.04\\
\hline
\end{tabular}
\end{table}

\hypertarget{table-of-health-and-happiness-in-the-family}{%
\subsection{Table of Health and Happiness in the
Family}\label{table-of-health-and-happiness-in-the-family}}

In table three, which appears to be presenting data on the relationship
between the health and happiness levels of families, based on some
measure or criteria. The three categories of happiness levels are ``not
too happy,'' ``happy,'' and ``very happy,'' while the four categories of
health are ``excellent,'' ``fair,'' ``good,'' and ``poor.'' Looking at
the data, we can see that families who rated their health as
``excellent'' had the highest proportion of respondents who reported
being ``very happy,'' at 53.70\%, and the lowest proportion of those who
were ``not too happy,'' at only 4.94\%. In contrast, families who rated
their health as ``fair'' had the highest proportion of respondents who
were ``not too happy,'' at 15.92\%, and the lowest proportion of those
who were ``very happy,'' at only 25.81\%.

\begin{table}

\caption{Table of Health and Happiness in the Family}
\centering
\begin{tabular}[t]{l|r|r|r}
\hline
health & happy & not too happy & very happy\\
\hline
excellent & 41.37 & 4.94 & 53.70\\
\hline
fair & 58.27 & 15.92 & 25.81\\
\hline
good & 57.14 & 7.76 & 35.10\\
\hline
poor & 50.14 & 29.09 & 20.77\\
\hline
\end{tabular}
\end{table}

\hypertarget{table-of-financial-satisfaction-and-happiness-in-the-family}{%
\subsection{Table of Financial Satisfaction and Happiness in the
Family}\label{table-of-financial-satisfaction-and-happiness-in-the-family}}

In table four, which appears that the table is presenting data on the
relationship between financial satisfaction and happiness levels in
families, based on some measure or criteria. The three categories of
happiness levels are ``not too happy,'' ``happy,'' and ``very happy,''
while the three categories of financial satisfaction are ``more or less
satisfied,'' ``not satisfied at all,'' and ``pretty well satisfied.''
Looking at the data, we can see that families who reported being
``pretty well satisfied'' with their finances had the highest proportion
of respondents who were ``very happy,'' at 52.0\%, and the lowest
proportion of those who were ``not too happy,'' at only 5.24\%. On the
other hand, families who reported being ``not satisfied at all'' with
their finances had the highest proportion of respondents who were ``not
too happy,'' at 20.92\%, and the lowest proportion of those who were
``very happy,'' at only 22.5\%.

\begin{table}

\caption{Table of Financial Satisfaction and Happiness in the Family}
\centering
\begin{tabular}[t]{l|r|r|r}
\hline
finance\_satified & happy & not too happy & very happy\\
\hline
more or less satisfied & 56.76 & 7.74 & 35.5\\
\hline
not satisfied at all & 56.59 & 20.92 & 22.5\\
\hline
pretty well satisfied & 42.75 & 5.24 & 52.0\\
\hline
\end{tabular}
\end{table}

In table five, which appears to be presenting data on the relationship
between divorce and happiness levels in families, based on some measure
or criteria. The three categories of happiness levels are ``not too
happy,'' ``happy,'' and ``very happy,'' while the two categories of
divorce are ``no'' and ``yes.'' Looking at the data, we can see that
there are only small differences in the proportions of families who
reported being ``happy'' or ``not too happy'' depending on whether or
not they had experienced divorce. Specifically, families who reported
``no'' to divorce had a slightly higher proportion of respondents who
were ``very happy,'' at 38.61\%, compared to those who reported ``yes''
to divorce, at 36.24\%. However, families who reported ``yes'' to
divorce had a slightly higher proportion of respondents who were ``not
too happy,'' at 11.53\%, compared to those who reported ``no'' to
divorce, at 9.29\%.

\begin{table}

\caption{Table of Divorce and Happiness in the Family}
\centering
\begin{tabular}[t]{l|r|r|r}
\hline
divorce & happy & not too happy & very happy\\
\hline
no & 52.10 & 9.29 & 38.61\\
\hline
yes & 52.23 & 11.53 & 36.24\\
\hline
\end{tabular}
\end{table}

In table six, which appears to be presenting data on the relationship
between educational attainment and happiness levels in families, based
on some measure or criteria. The three categories of happiness levels
are ``not too happy,'' ``happy,'' and ``very happy,'' while the
categories of educational attainment are ``associate/junior college,''
``bachelor's,'' ``graduate,'' ``high school,'' and ``less than high
school.'' Looking at the data, we can see that families with different
levels of educational attainment generally reported similar levels of
happiness. The proportions of respondents who reported being ``very
happy'' were similar across all levels of educational attainment,
ranging from 41.24\% for those with an associate/junior college degree
to 44.28\% for those with a graduate degree. The proportions of
respondents who reported being ``not too happy'' were also similar
across all levels of educational attainment, ranging from 5.26\% for
those with a graduate degree to 14.96\% for those with less than a high
school education.

\begin{table}

\caption{Table of Degree and Happiness in the Family}
\centering
\begin{tabular}[t]{l|r|r|r}
\hline
degree & happy & not too happy & very happy\\
\hline
associate/junior college & 50.85 & 7.91 & 41.24\\
\hline
bachelor's & 50.66 & 5.63 & 43.71\\
\hline
graduate & 50.47 & 5.26 & 44.28\\
\hline
high school & 53.48 & 8.86 & 37.66\\
\hline
less than high school & 50.90 & 14.96 & 34.13\\
\hline
\end{tabular}
\end{table}

\hypertarget{results}{%
\section{Results}\label{results}}

The analysis of the General Social Survey data-set from 1972 provides
insights into various aspects of individuals' lives in the United States
during that time period. The results suggest that several variables,
such as financial satisfaction, self-reported health status, and level
of education, have a positive relationship with individuals' level of
happiness.Regarding family dynamics, the analysis indicates that
individuals with no children reported the highest levels of happiness,
although the data set's limitations require further exploration of the
proportion of individuals with different numbers of children. Being
divorced may have a slight impact on one's level of happiness in life,
with a small proportion of individuals feeling ``not too happy''
compared to married individuals.

Furthermore, the analysis suggests that individuals' self-rated health
status has a positive relationship with their self-rated level of
happiness. The higher the participants' self-rated health, the higher
their self-rated level of satisfaction with life. Similarly, there is a
positive relationship between people's satisfaction with their current
financial situation and their level of happiness in life. The higher
people's satisfaction with their finances, the higher their level of
happiness.The analysis suggests that there is a certain relationship
between people's level of education and their level of happiness in
life. The proportion of people who feel ``not too happy'' is the highest
among those with education levels lower than high school. However, the
proportion of unhappy individuals is the lowest among those with
bachelor's and graduate degrees, suggesting that as people's education
level increases, their level of happiness also gradually increases.

Overall, these findings provide valuable insights into the factors that
may influence individuals' overall life satisfaction during the early
1970s in the United States. The results can be useful for researchers
and students interested in exploring topics such as social
stratification, gender roles, family dynamics, health disparities, and
subjective well-being.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{factors-influencing-individuals-level-of-happiness}{%
\subsection{Factors influencing individuals' level of
happiness}\label{factors-influencing-individuals-level-of-happiness}}

The study's findings on the positive relationship between financial
satisfaction, health, and happiness underscore the importance of
financial stability and access to healthcare for overall well-being.
These findings have important implications for policymakers and
practitioners working to improve individuals' quality of life (Ory 1994)
. For example, policies aimed at increasing access to affordable
healthcare and financial assistance programs can help individuals
improve their financial stability and access to essential services,
ultimately contributing to overall well-being.

The study's results also suggest that education is an important factor
in individuals' overall well-being and happiness. As people's education
level increases, their level of happiness also gradually increases. This
highlights the need for policies and programs that support educational
attainment, particularly for disadvantaged populations (Rothstein 1994).
Such programs can include initiatives to improve access to education and
financial aid for those who may face barriers to education.

Overall, this study demonstrates the importance of considering various
factors that can influence individuals' well-being and happiness. By
understanding the complex relationships between different variables,
policymakers and practitioners can develop targeted interventions aimed
at improving individuals' quality of life. Additionally, the findings
can serve as a foundation for further research on the topic,
particularly in examining changes in these relationships over time.

\hypertarget{impact-of-divorce-on-individuals-happiness}{%
\subsection{Impact of divorce on individuals'
happiness}\label{impact-of-divorce-on-individuals-happiness}}

Divorce is a significant life event that can have profound effects on an
individual's overall well-being and happiness. The findings of this
study suggest that individuals who have experienced divorce may have
lower levels of happiness than those who are married or have never been
married. This could be due to a range of factors, including the loss of
social support and economic stability that often accompanies divorce
(Headey 1989).

One possible explanation for the association between divorce and
happiness is the impact of social support. Marriage provides a source of
emotional support, and individuals who divorce may experience a loss of
this support network. Furthermore, divorce can result in the breakdown
of extended family relationships, reducing the availability of social
support. This loss of social support could contribute to lower levels of
happiness and well-being. Economic factors may also play a role in the
relationship between divorce and happiness (Çakar 2020). Divorce can
result in significant financial upheaval, particularly for individuals
who were financially dependent on their partner. This financial
instability could contribute to lower levels of happiness and
well-being, as financial stress can be a significant source of anxiety
and depression.

Further research could explore the reasons behind the association
between divorce and happiness. Qualitative studies could be conducted to
explore the experiences of individuals who have gone through divorce and
how this event has affected their well-being. Longitudinal studies could
also be conducted to examine changes in individuals' happiness levels
before and after a divorce(Lucas 2003).

Overall, the findings of this study highlight the importance of
considering the impact of divorce on individuals' well-being and
happiness. Policies and interventions aimed at supporting individuals
going through divorce, such as access to counseling and financial
support, could help to mitigate the negative effects of this life event
and improve individuals' overall well-being.

\hypertarget{the-importance-of-historical-context-in-understanding-well-being}{%
\subsection{The importance of historical context in understanding
well-being}\label{the-importance-of-historical-context-in-understanding-well-being}}

The historical context of the early 1970s in the United States is
essential in understanding individuals' well-being during that period.
Societal norms, values, and attitudes during this time were different
from those of today, and these differences could have influenced
individuals' well-being. These social movements may have influenced
individuals' attitudes towards social stratification, gender roles, and
family dynamics, which, in turn, could have affected their well-being.

Understanding the historical context is also essential in developing
interventions that can address the unique challenges faced by
individuals during a particular period in time (Cooper 2005). For
example, the economic conditions during the early 1970s, such as high
inflation and high unemployment rates, could have affected individuals'
financial stability and, ultimately, their well-being. Interventions
that address these economic challenges may have had a significant impact
on individuals' well-being during this period.

Furthermore, the study's findings can be compared to more recent data to
examine changes in the relationships between different factors and
well-being over time (CBrunstein 1993). For example, the impact of
divorce on well-being may have changed over time, as societal attitudes
towards divorce have shifted. Comparing the study's findings to more
recent data can provide insights into how societal changes have
influenced individuals' well-being over time.Overall, the historical
context is essential in understanding individuals' well-being during a
particular period in time. The study's focus on the early 1970s in the
United States provides valuable insights into the factors that
influenced individuals' well-being during that period. These findings
can be used to develop interventions that address the unique challenges
faced by individuals during a particular historical context, as well as
to compare changes in the relationships between different factors and
well-being over time.

\hypertarget{impact-of-financial-stability-on-happiness}{%
\subsection{Impact of Financial Stability on
Happiness}\label{impact-of-financial-stability-on-happiness}}

As the analysis of the GSS dataset shows, there is a positive
correlation between individuals' satisfaction with their financial
situation and overall well-being, an important finding. This correlation
underscores the importance of U.S. financial stability in determining a
person's happiness in the early 1970s. In this discussion, we will
further explore the impact of these factors on individual well-being
during that time.

In the early 1970s, the United States was going through a period of
economic turmoil. One of the most important factors is the rapid rise in
inflation. The country faces a phenomenon known as ``stagflation,''
which is characterized by a stagnant economy, high inflation, and high
unemployment. This unusual economic situation is largely attributable to
the 1973 oil crisis, which caused a spike in oil prices and disrupted
the global economy (Barsky 2001). The rise in inflation during this
period has a direct impact on individuals' financial satisfaction. As
the cost of goods and services increases, people find it a challenge to
maintain their previous standard of living (Diener 2009). This is
further exacerbated by high unemployment, as many people struggle to
find stable employment.Analysis of the GSS dataset highlights the
importance of financial stability in determining individual well-being,
emphasizing the need for effective economic policies to ensure the
financial security and well-being of populations.

\hypertarget{the-role-of-education-in-happiness}{%
\subsection{The Role of Education in
Happiness}\label{the-role-of-education-in-happiness}}

The study found that as an individual's education level increased, their
level of happiness also gradually increased. This finding prompts a
discussion on the role of education in determining one's overall
happiness and well-being during the early 1970s. It would be interesting
to explore the potential reasons behind this correlation, such as the
opportunities for personal development, improved employment prospects,
and social mobility that education provides(Warr 1992). Moreover,
examining the accessibility and quality of education during that period
could offer further insights into the impact of education on happiness.
By understanding the role of education in shaping individuals'
happiness, researchers and policymakers can better appreciate the
significance of investing in education and ensuring equal access to
quality education for all.One possible explanation is that education
provides individuals with the tools and resources they need to achieve
personal goals and fulfill their potential(Jenkins 2009). Education can
help individuals develop a sense of purpose, autonomy, and mastery,
which are important factors in promoting happiness and well-being. In
addition, education can provide individuals with the skills and
knowledge needed to pursue meaningful and fulfilling careers, which can
also contribute to their overall sense of well-being.

Moreover, education can provide opportunities for social mobility, which
can enhance individuals' sense of self-worth and life satisfaction.
Education can help individuals acquire the social and cultural capital
necessary to succeed in their professional and personal lives, which can
lead to increased opportunities and social status (Keller 1964). This,
in turn, can contribute to individuals' overall sense of happiness and
well-being.However, it is important to note that not all forms of
education may have the same impact on individuals' happiness and
well-being. The accessibility and quality of education are crucial
factors that can influence the extent to which education promotes
happiness and well-being. For example, individuals who have access to
high-quality education may experience greater benefits in terms of
personal development, employment prospects, and social mobility than
those who do not have access to such education (Margolis 2014).

Therefore, policymakers and educators must work to ensure that all
individuals have equal access to high-quality education. Investing in
education can not only promote individuals' personal and professional
growth but also contribute to the overall well-being and happiness of
society as a whole. By understanding the role of education in shaping
individuals' happiness, we can work towards building a more just and
equitable society.

\hypertarget{weaknesses-and-next-steps}{%
\section{Weaknesses and next steps}\label{weaknesses-and-next-steps}}

\hypertarget{weakness}{%
\subsection{Weakness:}\label{weakness}}

\begin{itemize}
\tightlist
\item
  The data-set used in the study is small, consisting of only 5
  observations and 10 variables, which may limit the generalization of
  the findings.
\item
  The study only examines data from the year 1972, which may not be
  representative of individuals' lives in the United States today or
  even in the 1970s as a whole.
\item
  The study only uses graphical representation to analyze the
  relationships between variables, which may not provide a comprehensive
  understanding of the complex relationships between variables.
\item
  The study only examines a limited set of variables and does not
  consider other factors that could impact individuals' level of
  happiness and well-being, such as social support, employment status,
  and cultural factors.
\end{itemize}

\hypertarget{next-steps}{%
\subsection{Next Steps:}\label{next-steps}}

\begin{itemize}
\tightlist
\item
  Further research could expand the data-set to include more
  observations and variables, which could provide a more comprehensive
  understanding of individuals' lives during the early 1970s in the
  United States.
\item
  Future studies could examine more recent data from the GSS to
  investigate changes in the relationships between variables over time.
\item
  Future studies could use more advanced statistical methods to analyze
  the relationships between variables, such as regression analysis, to
  provide a more robust understanding of the relationships between
  variables.
\item
  Future studies could consider other factors that may impact
  individuals' level of happiness and well-being, such as social
  support, employment status, and cultural factors.
\end{itemize}

\newpage

\appendix

\hypertarget{appendix}{%
\section*{Appendix}\label{appendix}}
\addcontentsline{toc}{section}{Appendix}

\hypertarget{additional-details}{%
\section{Additional details}\label{additional-details}}

\hypertarget{survey-question}{%
\subsection{Survey Question}\label{survey-question}}

Welcome to this survey on gender differences and equality in education,
employment, and well-being. Your participation is crucial in helping us
gain a deeper understanding of the factors that contribute to gender
disparities and the potential strategies for promoting gender equality
in various aspects of life. By answering the following questions, you
will provide valuable insights that can be used to inform policies and
initiatives aimed at creating a more inclusive and equitable society for
all. Please note that your responses will remain confidential and will
be used solely for research purposes. We appreciate your time and effort
in completing this survey.

Contact Information: If you have any questions or concerns about this
survey, please feel free to contact the research team:

NAME : SHAOHAN CHANG Institution/Department : Department of statistics
(University of Toronto) Email Address : shaohan.chang@utoronto.ca

\hypertarget{how-many-children-do-you-currently-have}{%
\subsubsection{1. How many children do you currently
have?}\label{how-many-children-do-you-currently-have}}

\begin{enumerate}
\def\labelenumi{\alph{enumi}.}
\tightlist
\item
  0
\item
  1
\item
  2
\item
  3
\item
  4
\item
  5 or more
\end{enumerate}

\hypertarget{how-would-you-rate-your-overall-level-of-happiness-or-life-satisfaction}{%
\paragraph{2. How would you rate your overall level of happiness or life
satisfaction?}\label{how-would-you-rate-your-overall-level-of-happiness-or-life-satisfaction}}

\begin{enumerate}
\def\labelenumi{\alph{enumi}.}
\tightlist
\item
  Very happy
\item
  Pretty happy
\item
  Not too happy
\item
  Not at all happy
\end{enumerate}

\hypertarget{how-would-you-rate-your-current-health-status}{%
\subsubsection{3. How would you rate your current health
status?}\label{how-would-you-rate-your-current-health-status}}

\begin{enumerate}
\def\labelenumi{\alph{enumi}.}
\tightlist
\item
  Excellent
\item
  Good
\item
  Fair
\item
  Poor
\end{enumerate}

\hypertarget{how-satisfied-are-you-with-your-current-financial-situation}{%
\subsubsection{4. How satisfied are you with your current financial
situation?}\label{how-satisfied-are-you-with-your-current-financial-situation}}

\begin{enumerate}
\def\labelenumi{\alph{enumi}.}
\tightlist
\item
  Very satisfied
\item
  More or less satisfied
\item
  Not very satisfied
\item
  Not at all satisfied
\end{enumerate}

\hypertarget{have-you-ever-been-divorced}{%
\subsubsection{5. Have you ever been
divorced?}\label{have-you-ever-been-divorced}}

\begin{enumerate}
\def\labelenumi{\alph{enumi}.}
\tightlist
\item
  Yes
\item
  No
\end{enumerate}

\hypertarget{what-is-your-current-living-area}{%
\subsubsection{6. What is your current living
area?}\label{what-is-your-current-living-area}}

\begin{enumerate}
\def\labelenumi{\alph{enumi}.}
\tightlist
\item
  Large city
\item
  Small city
\item
  Suburban
\item
  Rural
\end{enumerate}

\hypertarget{what-is-your-age-please-enter-a-number}{%
\subsubsection{7. What is your age? (Please enter a
number)}\label{what-is-your-age-please-enter-a-number}}

\hypertarget{what-is-your-biological-sex}{%
\subsubsection{8. What is your biological
sex?}\label{what-is-your-biological-sex}}

\begin{enumerate}
\def\labelenumi{\alph{enumi}.}
\tightlist
\item
  Male
\item
  Female
\end{enumerate}

\hypertarget{what-is-the-highest-level-of-education-you-have-completed}{%
\subsubsection{9. What is the highest level of education you have
completed?}\label{what-is-the-highest-level-of-education-you-have-completed}}

\begin{enumerate}
\def\labelenumi{\alph{enumi}.}
\tightlist
\item
  Less than high school
\item
  High school or equivalent
\item
  Some college or associate degree
\item
  Bachelor's degree
\item
  Graduate or professional degree
\end{enumerate}

\hypertarget{how-would-you-rate-your-overall-level-of-well-being}{%
\subsubsection{10. How would you rate your overall level of
well-being?}\label{how-would-you-rate-your-overall-level-of-well-being}}

\begin{enumerate}
\def\labelenumi{\alph{enumi}.}
\tightlist
\item
  Very good
\item
  Good
\item
  Fair
\item
  Poor
\end{enumerate}

\newpage

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-i}{}}%
Barsky, \& Kilian, R. 2001. {``Do We Really Know That Oil Caused the
Great Stagflation? A Monetary Alternative.''} \emph{Nber Macroeconomics
Annual} 16 (5): 137--83.

\leavevmode\vadjust pre{\hypertarget{ref-e}{}}%
Çakar, F. S. 2020. {``The Role of Social Support in the Relationship
Between Adolescents' Level of Loss and Grief and Well-Being.''}
\emph{International Education Studies} 13 (12): 27.

\leavevmode\vadjust pre{\hypertarget{ref-h}{}}%
CBrunstein, J. C. 1993. {``Personal Goals and Subjective Well-Being: A
Longitudinal Study.''} \emph{Journal of Personality and Social
Psychology} 65 (5): 1061--70.

\leavevmode\vadjust pre{\hypertarget{ref-g}{}}%
Cooper, Scandura, C. D. 2005. {``Looking Forward but Learning from Our
Past: Potential Challenges to Developing Authentic Leadership Theory and
Authentic Leaders.''} \emph{Leadership Quarterly} 16 (3): 475--93.

\leavevmode\vadjust pre{\hypertarget{ref-j}{}}%
Diener, \& Biswas-Diener, E. 2009. {``Will Money Increase Subjective
Well-Being?: A Literature Review and Guide to Needed Research.''}
\emph{Springer EBooks}, 119--54.

\leavevmode\vadjust pre{\hypertarget{ref-janitor}{}}%
Firke, Sam. 2023. \emph{Janitor: Simple Tools for Examining and Cleaning
Dirty Data}. \url{https://CRAN.R-project.org/package=janitor}.

\leavevmode\vadjust pre{\hypertarget{ref-gss}{}}%
{``GSS General Social Survey.''} 2023. NORC at the University of
Chicago; \url{https://gss.norc.org/}.

\leavevmode\vadjust pre{\hypertarget{ref-o}{}}%
Headey, \& Wearing, B. 1989. {``Personality, Life Events, and Subjective
Well-Being: Toward a Dynamic Equilibrium Model.''} \emph{Journal of
Personality and Social Psychology}.

\leavevmode\vadjust pre{\hypertarget{ref-l}{}}%
Jenkins, H. 2009. {``Confronting the Challenges of Participatory
Culture.''} \emph{The MIT Press EBooks}.

\leavevmode\vadjust pre{\hypertarget{ref-m}{}}%
Keller, \& Zavalloni, S. 1964. {``Ambition and Social Class: A
Respecification.''} \emph{A Respecification. Social Forces}.

\leavevmode\vadjust pre{\hypertarget{ref-f}{}}%
Lucas, Clark, R. E. 2003. {``Reexamining Adaptation and the Set Point
Model of Happiness: Reactions to Changes in Marital Status.''}
\emph{Journal of Personality and Social Psychology} 84 (3): 527--39.

\leavevmode\vadjust pre{\hypertarget{ref-n}{}}%
Margolis, Hodge, J. 2014. {``The Teacher Educator's Role in Promoting
Institutional Versus Individual Teacher Well-Being.''} \emph{Journal of
Education for Teaching}.

\leavevmode\vadjust pre{\hypertarget{ref-here}{}}%
Müller, Kirill. 2020. \emph{Here: A Simpler Way to Find Your Files}.
\url{https://CRAN.R-project.org/package=here}.

\leavevmode\vadjust pre{\hypertarget{ref-c}{}}%
Ory, \& Cox, M. G. 1994. {``Forging Ahead: Linking Health and Behavior
to Improve Quality of Life in Older People.''} \emph{Social Indicators
Research} 33 (3): 89--120.

\leavevmode\vadjust pre{\hypertarget{ref-d}{}}%
Rothstein, \& Uslaner, B. 1994. {``All for All: Equality, Corruption,
and Social Trust.''} \emph{World Politics} 58 (1): 41--72.

\leavevmode\vadjust pre{\hypertarget{ref-a}{}}%
RSiahpush, Spittal, M. 2008. {``Happiness and Life Satisfaction
Prospectively Predict Self-Rated Health, Physical Health, and the
Presence of Limiting, Long-Term Health Conditions.''} \emph{American
Journal of Health Promotion,} 23 (1): 18--26.

\leavevmode\vadjust pre{\hypertarget{ref-b}{}}%
Vlaev, \& Elliott, I. 2014. {``Financial Well-Being Components.''}
\emph{Social Indicators Research} 118 (3): 1103--23.

\leavevmode\vadjust pre{\hypertarget{ref-k}{}}%
Warr, P. 1992. {``Age and Occupational Well-Being.''} \emph{Psychology
and Aging}.

\leavevmode\vadjust pre{\hypertarget{ref-ggplot}{}}%
Wickham, Hadley. 2016. \emph{Ggplot2: Elegant Graphics for Data
Analysis}. Springer-Verlag New York.
\url{https://ggplot2.tidyverse.org}.

\leavevmode\vadjust pre{\hypertarget{ref-ti}{}}%
Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy
D'Agostino McGowan, Romain François, Garrett Grolemund, et al. 2019.
{``Welcome to the {tidyverse}.''} \emph{Journal of Open Source Software}
4 (43): 1686. \url{https://doi.org/10.21105/joss.01686}.

\leavevmode\vadjust pre{\hypertarget{ref-dplyr}{}}%
Wickham, Hadley, Romain François, Lionel Henry, Kirill Müller, and Davis
Vaughan. 2023. \emph{Dplyr: A Grammar of Data Manipulation}.
\url{https://CRAN.R-project.org/package=dplyr}.

\leavevmode\vadjust pre{\hypertarget{ref-haven}{}}%
Wickham, Hadley, Evan Miller, and Danny Smith. 2022. \emph{Haven: Import
and Export 'SPSS', 'Stata' and 'SAS' Files}.
\url{https://CRAN.R-project.org/package=haven}.

\leavevmode\vadjust pre{\hypertarget{ref-knitr}{}}%
Xie, Yihui. 2014. {``Knitr: A Comprehensive Tool for Reproducible
Research in {R}.''} \url{https://yihui.org/knitr/}.

\leavevmode\vadjust pre{\hypertarget{ref-kableExtra}{}}%
Zhu, Hao. 2021. \emph{kableExtra: Construct Complex Table with 'Kable'
and Pipe Syntax}. \url{https://CRAN.R-project.org/package=kableExtra}.

\end{CSLReferences}

\end{document}

### 2023-03-29 scripts/00-simulate_data.R
Delete scripts directory

@@ -1,39 +1,0 @@
-#### Preamble ####
-# Purpose:The code above simulates a dataset called "happiness_and_income" with information on individuals' happiness, income, and other characteristics. 
-#The "set.seed" function sets a specific seed for the random number generator, ensuring that the same random values are generated each time the code is run.
-#The "size_of_population" variable sets the number of individuals in the simulated population.The "tibble" function creates a table with columns for the year of observation, 
-#age, sex, education level ("degree"), job satisfaction ("job_satisfied"), happiness level ("happy"), satisfaction level ("sat"), and age group ("age2").The "sample" function generates 
-#random samples for each of these variables, with the "replace" argument set to TRUE so that each individual can be sampled more than once.The "mutate" function creates a new column for 
-#age group based on the age variable, with individuals grouped into "age 18-39", "age 40-59", or "age 60+" based on their age.Overall, this code is simulating a population of individuals 
-#with varying characteristics, including their level of happiness, income, and education, among other variables. This type of simulation could be used to explore relationships between 
-#these variables and test different hypotheses.
-# Author: SHAOHAN CHANG  
-# Data: 14 March 2023 
-# Contact: SHAOHAN.CHANG@utoronto.ca
-# License: MIT
-# Pre-requisites: You have downloaded the data from the library. To do that:
-## 1. Go the website : https://gss.norc.org/get-the-data/stata
-## 2.Download the all file from 1972 to the 2012 file. 
-## 3. Click the file of download.
-## 4. select the SATA file 
-## 5. Can select all variables by clicking button next to the green colored 'ALL'. Then continue 
-## 6. Create the file, download and save the file. 
-# Any other information needed? 
-## 1. It is important to note the location where the downloaded data file is saved on your computer, as this will be needed when reading the data into R.
-## 2. The downloaded data file is likely to be very large, as it contains survey data from 1972 to 2012. It may be necessary to filter the data to a specific 
-# time period or subset of variables in order to work with it more efficiently.
-## 3. The downloaded data file is likely to be in Stata format, so it will need to be read into R using a package like "haven" or "foreign".
-## 4. It is also important to familiarize oneself with the codebook or documentation for the dataset, which can be found on the GSS website or in the downloaded file. 
-# This will provide information on the variables and their meanings, as well as any codes or missing values used in the dataset.
[…]

### 2023-03-29 scripts/02-data_cleaning.R

@@ -1,105 +1,0 @@
-#### Preamble ####
-# Purpose: The purpose of this code is to clean and preprocess a dataset called "the_raw_data", which contains information about individuals' demographics, 
-#employment status, job satisfaction, and happiness. The code selects relevant variables from the dataset, converts them into factors, and renames them to 
-#more understandable names. It also removes any observations with missing or invalid values and filters the data to only include years between 1972 and 2012 
-#and individuals under the age of 89. Additionally, the code creates a new variable called "age_range" based on the age variable, which categorizes individuals 
-#into different age groups. Finally, the cleaned dataset is saved as a CSV file called "cleaned_data.csv" in the "outputs" folder. The cleaned dataset is now ready 
-# to be used for further analysis and modeling.
-# Author: SHAOHAN CHANG  
-# Data: 14 March 2023 
-# Contact: SHAOHAN.CHANG@utoronto.ca 
-# License: MIT
-# Pre-requisites:
-## 1. Go the website : https://gss.norc.org/get-the-data/stata
-## 2.Scroll down to the "Stata Data" section and click the "Download the GSS Stata data files" link.
-## 3. Select the years you want to download from the list provided. You can select multiple years by holding down the "Ctrl" key on your keyboard while clicking on the years you want.
-## 4. Click the "Download Selected Files" button at the bottom of the page. 
-## 5. On the next page, select the "Stata" file format.
-## 6. Select "ALL" from the dropdown menu next to the green "ALL" button to download all variables.
-## 7. Click the "Create File" button and wait for the file to be generated.
-## 8. Once the file has been created, click the "Download File" button to save the file to your computer.
-# Any other information needed? [...UPDATE THIS...]
-## 1. Make sure to note the location where the downloaded data file is saved on your computer, as you will need to provide the file path when reading the data into R.
-## 2. The GSS data file is likely to be very large, especially if you downloaded the data for multiple years. It may be necessary to filter the data to a specific time period or subset of 
-# variables in order to work with it more efficiently. This can be done using functions like subset() or dplyr::select().
[…]

### 2023-03-29 outputs/paper/paper.qmd
Add files via upload

@@
 
-Used some R language packages, such as tidyverse [@ti], dplyr [@dplyr], janitor [@janitor] , knitr [@knitr], here [@here], haven [@haven], ggplot [@ggplot] , kableExtra [@kableExtra] to assist in data analysis, and the data from General Social Survey [@gss].
+Used some R language packages, such as tidyverse [@ti], dplyr [@dplyr], janitor [@janitor] , knitr [@knitr], here [@here], haven [@haven], ggplot [@ggplot] , kableExtra [@kableExtra] , model summary [@modelsummary] to assist in data analysis, and the data from General Social Survey [@gss].
 
@@
 library(tinytex)
+library(modelsummary)
 data <- read_csv(here::here("inputs/data/cleaned_data.csv"))
@@
 data %>%
-  select(-1:-8) %>%
+  select(9:13) %>%
+  slice(1:5) %>%
+  kable() %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+```
+
+```{r}
+#| eval: true
+#| warning: false
+#| echo: false
+data %>%
+  select(14:16) %>%
   slice(1:5) %>%
@@
 It is a categorical variable with different levels of happiness: very happy, pretty happy, not too happy, and not at all happy.
+-   divorce_score: This variable is a binary representation of the divorce status of an individual in the dataset.
+The value '0' denotes that the individual is not divorced, while the value '1' indicates that they are divorced.
+-   happy_score: The happy_score variable is an ordinal variable representing the self-reported happiness levels of the individuals in the dataset.
+It ranges from 0 to 3, with 0 representing "not too happy," 1 representing "happy," 2 representing "very happy," and 3 reserved for any unclassified or missing responses.
+-   degree_score: This ordinal variable represents the educational attainment of the individuals in the dataset.
+It ranges from 1 to 5, where 1 signifies "less than high school," 2 denotes "high school," 3 represents "associate/junior college," 4 refers to "bachelor's," and 5 indicates "graduate" level education.
+The value 6 is reserved for any unclassified or missing responses.
+-   health_score: The health_score variable is an ordinal variable indicating the self-reported health status of the individuals in the dataset.
+It ranges from 1 to 4, with 1 denoting "poor" health, 2 signifying "fair" health, 3 representing "good" health, and 4 referring to "excellent" health.
+The value 5 is reserved for any unclassified or missing responses.
+-   finance_score: This ordinal variable represents the financial satisfaction level of the individuals in the dataset.
+It ranges from 1 to 3, with 1 indicating "Not at all satisfied," 2 denoting "more or less satisfied," and 3 signifying "pretty well satisfied." The value 4 is reserved for any unclassified or missing responses.
+-   babies_number: The babies_number variable is an ordinal variable denoting the number of babies an individual in the dataset has.
+It ranges from 0 to 4, where 0 represents "0" babies, 1 denotes "1" baby, 2 signifies "2" babies, 3 indicates "3" babies, and 4 refers to "4" babies.
+The value 5 is reserved for any unclassified or missing responses.
 
@@
 
+$$
+\hat{Y}=\hat{\beta_0}+\hat{\beta_1}X_{age}+\hat{\beta_2}X_{degree-score}+\hat{\beta_3}X_{finance-score}+\hat{\beta_4}X_{health-score} + \hat{\beta_5}X_{divorce-score} + 
+\hat{\beta_6}X_{babies-number}
+$$ {#eq-model}
+
 ```{r}
+#| message: false
+#| echo: false
 #| warning: false
-#| echo: false
-# create a new variable "divorce_score" based on the "divorce" variable
-data$divorce_score <- ifelse(data$divorce == "no", 0, 1)
+#| label: tbl-lm
+#| tbl-cap: Linear Model and its Summary Statistics
+model <- lm(data$happy_score ~ age +  degree_score + finance_score + health_score + divorce_score + babies_number, data=data)
 
-data$happy_score <- ifelse(data$happy == "not too happy", 1,
-                      ifelse(data$happy == "not satisfied at all", 2,
-                      ifelse(data$happy == "more or less satisfied", 3,
-                      ifelse(data$happy == "pretty well satisfied", 4, 5))))
+modelsummary :: modelsummary(
+  list(
+    "Well-Being" = model
+  ),
+  fmt = 2,
+  statistic = "conf.int"
+)
+```
 
-# Create ordinal variable for degree score
-data$degree_score <- ifelse(data$degree == "Less than high school", 1,
-                            ifelse(data$degree == "High school graduate", 2,
-                                   ifelse(data$degree == "Some college", 3,
-                                          ifelse(data$degree == "Bachelor's degree", 4,
-                                                 ifelse(data$degree == "Advanced degree", 5, NA)))))
+The [@tbl-lm], which is based the equation of @eq-model :
 
-# Create ordinal variable for health score
-data$health_score <- ifelse(data$health == "Poor", 1,
-                            ifelse(data$health == "Fair", 2,
-                                   ifelse(data$health == "Good", 3,
-                                          ifelse(data$health == "Very good", 4,
-                                                 ifelse(data$health == "Excellent", 5, NA)))))
+-   Overall model significance: The F-statistic (314.461) indicates that the overall model is statistically significant, suggesting that the predictors included in the model collectively explain a meaningful portion of the variance in well-being.
+-   Model fit: The R-squared (0.070) and adjusted R-squared (0.070) values are relatively low, indicating that only 7% of the variation in well-being is explained by the predictors in the model.
+This suggests that there may be other factors influencing well-being that have not been included in the model.
+-   Age as a predictor: The coefficient for age (0.00) and its confidence interval (\[0.00, 0.00\]) suggest that age does not have a statistically significant effect on well-being in this model.
+-   Degree score as a predictor: The positive coefficient for degree_score (0.02) and its confidence interval (\[0.01, 0.03\]) indicate that higher degree scores are associated with higher well-being.
+This suggests a positive relationship between educational achievement and well-being.
+-   Finance score as a predictor: The negative coefficient for finance_score (−0.09) and its confidence interval (\[−0.11, −0.08\]) demonstrate that higher finance scores are associated with lower well-being.
+This indicates a negative relationship between financial stress and well-being.
+-   Health score as a predictor: The positive coefficient for health_score (0.32) and its confidence interval (\[0.30, 0.34\]) show that higher health scores are associated with higher well-being.
+This suggests a strong positive relationship between health and well-being.
+-   Divorce score as a predictor: The coefficient for divorce_score (−0.02) and its confidence interval (\[−0.05, 0.01\]) indicate that the effect of divorce_score on well-being is not statistically significant.
+This suggests that the relationship between divorce and well-being is inconclusive in this model.
+-   Number of babies as a predictor: The negative coefficient for babies_number (−0.03) and its confidence interval (\[−0.05, −0.01\]) demonstrate that having more babies is associated with lower well-being.
+This indicates a negative relationship between the number of children and well-being.
 
-# Create ordinal variable for finance score
-data$finance_score <- ifelse(data$finance_satified == "Not at all satisfied", 1,
-                            ifelse(data$finance_satified == "Not too satisfied", 2,
-                                   ifelse(data$finance_satified == "More or less satisfied", 3,
-                                          ifelse(data$finance_satified == "Pretty well satisfied", 4,
-                                                 ifelse(data$finance_satified == "Completely satisfied", 5, NA)))))
-
-# convert age variable from character to numeric
-data$age <- as.numeric(data$age)
-
-# perform linear regression of age and divorce_score
-model <- lm(happy_score ~ age +  degree + finance_satified + health + divorce, data=data)
-model
-```
+In conclusion of this result, the model shows that degree_score, finance_score, health_score, and babies_number are statistically significant predictors of well-being, while age and divorce_score are not.
+However, the low R-squared value suggests that there are likely other factors affecting well-being that have not been included in the model.
 

### 2023-03-29 scripts/01-download_data.R

@@ -1,0 +1,12 @@
+# Explain how you download the data
+
+#The General Social Survey (GSS) is a nationally representative survey conducted in the United States since 1972 to 2012. 
+# It gathers information on various social and demographic trends and attitudes, including residents' living conditions, working status, 
+#happiness, and many other variables of interest.To access and analyze the GSS data, one can download the data package from the GSS website. 
+#The data are typically provided in a statistical software format, such as STATA or SPSS, and may require some data cleaning and processing before analysis.
+#For this specific article, the author plans to simulate and clean the data to select the variables that are relevant to the research question. This may involve 
+#dropping irrelevant variables, transforming or recoding variables, and creating new variables from existing ones.Once the data cleaning is complete, the author can
+#start analyzing the selected variables to investigate the research question. This may involve using statistical software or other analytical tools to explore relationships 
+#and patterns in the data.Overall, the GSS dataset is a rich source of social and demographic data that can provide valuable insights into various trends and attitudes over time. 
+# However, careful attention to data cleaning and analysis is necessary to ensure the validity and reliability of the findings.   
+         

### 2023-03-29 scripts/02-data_cleaning.R

@@ -1,0 +1,143 @@
+#### Preamble ####
+# Purpose: The purpose of this code is to clean and preprocess a dataset called "the_raw_data", which contains information about individuals' demographics, 
+#employment status, job satisfaction, and happiness. The code selects relevant variables from the dataset, converts them into factors, and renames them to 
+#more understandable names. It also removes any observations with missing or invalid values and filters the data to only include years between 1972 and 2012 
+#and individuals under the age of 89. Additionally, the code creates a new variable called "age_range" based on the age variable, which categorizes individuals 
+#into different age groups. Finally, the cleaned dataset is saved as a CSV file called "cleaned_data.csv" in the "outputs" folder. The cleaned dataset is now ready 
+# to be used for further analysis and modeling.
+# Author: SHAOHAN CHANG  
+# Data: 14 March 2023 
+# Contact: SHAOHAN.CHANG@utoronto.ca 
+# License: MIT
+# Pre-requisites:
+## 1. Go the website : https://gss.norc.org/get-the-data/stata
+## 2.Scroll down to the "Stata Data" section and click the "Download the GSS Stata data files" link.
+## 3. Select the years you want to download from the list provided. You can select multiple years by holding down the "Ctrl" key on your keyboard while clicking on the years you want.
+## 4. Click the "Download Selected Files" button at the bottom of the page. 
+## 5. On the next page, select the "Stata" file format.
+## 6. Select "ALL" from the dropdown menu next to the green "ALL" button to download all variables.
+## 7. Click the "Create File" button and wait for the file to be generated.
+## 8. Once the file has been created, click the "Download File" button to save the file to your computer.
+# Any other information needed? [...UPDATE THIS...]
+## 1. Make sure to note the location where the downloaded data file is saved on your computer, as you will need to provide the file path when reading the data into R.
+## 2. The GSS data file is likely to be very large, especially if you downloaded the data for multiple years. It may be necessary to filter the data to a specific time period or subset of 
+# variables in order to work with it more efficiently. This can be done using functions like subset() or dplyr::select().
+## 3. Since the downloaded data file is in Stata format, you will need to use a package like "haven" or "foreign" to read the data into R. For example, you can use the haven::read_dta() 
[…]

### 2023-03-29 scripts/04-test_data.R

@@ -1,0 +1,52 @@
+#### Preamble ####
+# Purpose: The purpose of this code is to conduct a series of tests on the data frame to check for the presence of missing (NA) values in various variables. By running these tests, the user can ensure the data is complete and free of missing values before proceeding with further analysis.Test One: The code checks for any missing values across the entire data frame.Test Two: The code examines the 'happy' variable for missing values.Test Three: The code assesses the 'year' variable for missing values.Test Four: The code evaluates the 'sex' variable for missing values.Test Five: The code inspects the 'degree' variable for missing values.For each test, the code prints "Check passed" if there are no missing values, and "Check failed" if missing values are detected. This information helps the user decide on necessary data cleaning steps and maintain data integrity during analysis.
+# Author: SHAOHAN CHANG 
+# Data: 14 March 2023 
+# Contact: SHAOHAN.CHANG@Toronto.ca 
+# License: MIT
+# Pre-requisites: Prior to executing these tests on the test data, it is presumed that the data has already been imported into R and stored as a data frame. Additionally, it is assumed that the necessary packages for performing these tests, such as "dplyr" or "tidyverse", have been installed and loaded in R. It is also crucial to comprehend the research question and objectives, as this knowledge will steer the data analysis and establish the most suitable tests to employ.Moreover, it is advisable to meticulously examine the cookbook or documentation for the dataset, as this will supply vital details about the variables, their definitions, and any coding or missing value conventions utilized in the dataset. By possessing a thorough understanding of these prerequisites, researchers can guarantee that their data analysis is well-founded and precise.
+
+#### Work space setup ####
+library(tidyverse)
+library(janitor)
+library(dplyr)
+
+
+#### Test data ####
+
+
+data <- 
+  readr::read_csv("inputs/data/cleaned_data.csv")
+
+# Test One : Check for NA values in the data frame.
+# Explanation : as the result , there 0 NA value. 
+
+check_result <- ifelse(sum(is.na(data)) == 0, "Check passed", "Check failed")
+print(check_result)
+
+
+# Test Two : Check for NA values in happy. 
+
+# Explanation :  Three are 0 missing values in the happy. 
+
+check_result <- ifelse(sum(is.na(data$happy)) == 0, "Check passed", "Check failed")
+print(check_result)
+
+
+# Test Three : Check for NA values in year.
[…]

### 2023-03-29 scripts/01-download_data.R
Delete scripts directory

@@ -1,12 +1,0 @@
-# Explain how you download the data
-
-#The General Social Survey (GSS) is a nationally representative survey conducted in the United States since 1972 to 2012. 
-# It gathers information on various social and demographic trends and attitudes, including residents' living conditions, working status, 
-#happiness, and many other variables of interest.To access and analyze the GSS data, one can download the data package from the GSS website. 
-#The data are typically provided in a statistical software format, such as STATA or SPSS, and may require some data cleaning and processing before analysis.
-#For this specific article, the author plans to simulate and clean the data to select the variables that are relevant to the research question. This may involve 
-#dropping irrelevant variables, transforming or recoding variables, and creating new variables from existing ones.Once the data cleaning is complete, the author can
-#start analyzing the selected variables to investigate the research question. This may involve using statistical software or other analytical tools to explore relationships 
-#and patterns in the data.Overall, the GSS dataset is a rich source of social and demographic data that can provide valuable insights into various trends and attitudes over time. 
-# However, careful attention to data cleaning and analysis is necessary to ensure the validity and reliability of the findings.   
-         

### 2023-03-29 scripts/02-data_cleaning.R

@@ -1,143 +1,0 @@
-#### Preamble ####
-# Purpose: The purpose of this code is to clean and preprocess a dataset called "the_raw_data", which contains information about individuals' demographics, 
-#employment status, job satisfaction, and happiness. The code selects relevant variables from the dataset, converts them into factors, and renames them to 
-#more understandable names. It also removes any observations with missing or invalid values and filters the data to only include years between 1972 and 2012 
-#and individuals under the age of 89. Additionally, the code creates a new variable called "age_range" based on the age variable, which categorizes individuals 
-#into different age groups. Finally, the cleaned dataset is saved as a CSV file called "cleaned_data.csv" in the "outputs" folder. The cleaned dataset is now ready 
-# to be used for further analysis and modeling.
-# Author: SHAOHAN CHANG  
-# Data: 14 March 2023 
-# Contact: SHAOHAN.CHANG@utoronto.ca 
-# License: MIT
-# Pre-requisites:
-## 1. Go the website : https://gss.norc.org/get-the-data/stata
-## 2.Scroll down to the "Stata Data" section and click the "Download the GSS Stata data files" link.
-## 3. Select the years you want to download from the list provided. You can select multiple years by holding down the "Ctrl" key on your keyboard while clicking on the years you want.
-## 4. Click the "Download Selected Files" button at the bottom of the page. 
-## 5. On the next page, select the "Stata" file format.
-## 6. Select "ALL" from the dropdown menu next to the green "ALL" button to download all variables.
-## 7. Click the "Create File" button and wait for the file to be generated.
-## 8. Once the file has been created, click the "Download File" button to save the file to your computer.
-# Any other information needed? [...UPDATE THIS...]
-## 1. Make sure to note the location where the downloaded data file is saved on your computer, as you will need to provide the file path when reading the data into R.
-## 2. The GSS data file is likely to be very large, especially if you downloaded the data for multiple years. It may be necessary to filter the data to a specific time period or subset of 
-# variables in order to work with it more efficiently. This can be done using functions like subset() or dplyr::select().
-## 3. Since the downloaded data file is in Stata format, you will need to use a package like "haven" or "foreign" to read the data into R. For example, you can use the haven::read_dta() 
[…]

### 2023-03-29 scripts/04-test_data.R

@@ -1,52 +1,0 @@
-#### Preamble ####
-# Purpose: The purpose of this code is to conduct a series of tests on the data frame to check for the presence of missing (NA) values in various variables. By running these tests, the user can ensure the data is complete and free of missing values before proceeding with further analysis.Test One: The code checks for any missing values across the entire data frame.Test Two: The code examines the 'happy' variable for missing values.Test Three: The code assesses the 'year' variable for missing values.Test Four: The code evaluates the 'sex' variable for missing values.Test Five: The code inspects the 'degree' variable for missing values.For each test, the code prints "Check passed" if there are no missing values, and "Check failed" if missing values are detected. This information helps the user decide on necessary data cleaning steps and maintain data integrity during analysis.
-# Author: SHAOHAN CHANG 
-# Data: 14 March 2023 
-# Contact: SHAOHAN.CHANG@Toronto.ca 
-# License: MIT
-# Pre-requisites: Prior to executing these tests on the test data, it is presumed that the data has already been imported into R and stored as a data frame. Additionally, it is assumed that the necessary packages for performing these tests, such as "dplyr" or "tidyverse", have been installed and loaded in R. It is also crucial to comprehend the research question and objectives, as this knowledge will steer the data analysis and establish the most suitable tests to employ.Moreover, it is advisable to meticulously examine the cookbook or documentation for the dataset, as this will supply vital details about the variables, their definitions, and any coding or missing value conventions utilized in the dataset. By possessing a thorough understanding of these prerequisites, researchers can guarantee that their data analysis is well-founded and precise.
-
-#### Work space setup ####
-library(tidyverse)
-library(janitor)
-library(dplyr)
-
-
-#### Test data ####
-
-
-data <- 
-  readr::read_csv("inputs/data/cleaned_data.csv")
-
-# Test One : Check for NA values in the data frame.
-# Explanation : as the result , there 0 NA value. 
-
-check_result <- ifelse(sum(is.na(data)) == 0, "Check passed", "Check failed")
-print(check_result)
-
-
-# Test Two : Check for NA values in happy. 
-
-# Explanation :  Three are 0 missing values in the happy. 
-
-check_result <- ifelse(sum(is.na(data$happy)) == 0, "Check passed", "Check failed")
-print(check_result)
-
-
-# Test Three : Check for NA values in year.
[…]

### 2023-03-29 scripts/00-simulate_data.R
Add files via upload

@@ -1,0 +1,39 @@
+#### Preamble ####
+# Purpose:The code above simulates a dataset called "happiness_and_income" with information on individuals' happiness, income, and other characteristics. 
+#The "set.seed" function sets a specific seed for the random number generator, ensuring that the same random values are generated each time the code is run.
+#The "size_of_population" variable sets the number of individuals in the simulated population.The "tibble" function creates a table with columns for the year of observation, 
+#age, sex, education level ("degree"), job satisfaction ("job_satisfied"), happiness level ("happy"), satisfaction level ("sat"), and age group ("age2").The "sample" function generates 
+#random samples for each of these variables, with the "replace" argument set to TRUE so that each individual can be sampled more than once.The "mutate" function creates a new column for 
+#age group based on the age variable, with individuals grouped into "age 18-39", "age 40-59", or "age 60+" based on their age.Overall, this code is simulating a population of individuals 
+#with varying characteristics, including their level of happiness, income, and education, among other variables. This type of simulation could be used to explore relationships between 
+#these variables and test different hypotheses.
+# Author: SHAOHAN CHANG  
+# Data: 29 March 2023 
+# Contact: SHAOHAN.CHANG@utoronto.ca
+# License: MIT
+# Pre-requisites: You have downloaded the data from the library. To do that:
+## 1. Go the website : https://gss.norc.org/get-the-data/stata
+## 2.Download the all file from 1972 to the 2012 file. 
+## 3. Click the file of download.
+## 4. select the SATA file 
+## 5. Can select all variables by clicking button next to the green colored 'ALL'. Then continue 
+## 6. Create the file, download and save the file. 
+# Any other information needed? 
+## 1. It is important to note the location where the downloaded data file is saved on your computer, as this will be needed when reading the data into R.
+## 2. The downloaded data file is likely to be very large, as it contains survey data from 1972 to 2012. It may be necessary to filter the data to a specific 
+# time period or subset of variables in order to work with it more efficiently.
+## 3. The downloaded data file is likely to be in Stata format, so it will need to be read into R using a package like "haven" or "foreign".
+## 4. It is also important to familiarize oneself with the codebook or documentation for the dataset, which can be found on the GSS website or in the downloaded file. 
+# This will provide information on the variables and their meanings, as well as any codes or missing values used in the dataset.
[…]

### 2023-03-29 scripts/01-download_data.R

@@ -1,0 +1,3 @@
+# Explain how you download the data
+
+The General Social Survey (GSS) is a comprehensive survey conducted in the United States since 1972 to 2012, providing insight into various social and demographic trends and attitudes. Accessing and analyzing the data requires downloading the data package from the GSS website and cleaning and processing the data to select relevant variables for the research question. This may involve dropping irrelevant variables, transforming or recording variables, and creating new variables. Once the data cleaning is complete, the selected variables can be analyzed using statistical software or other analytical tools to explore patterns and relationships. Despite being a valuable source of information, careful attention to data cleaning and analysis is crucial to ensure the validity and reliability of the findings.

### 2023-03-29 scripts/02-data_cleaning.R

@@ -1,0 +1,143 @@
+#### Preamble ####
+# Purpose: The purpose of this code is to clean and preprocess a dataset called "the_raw_data", which contains information about individuals' demographics, 
+#employment status, job satisfaction, and happiness. The code selects relevant variables from the dataset, converts them into factors, and renames them to 
+#more understandable names. It also removes any observations with missing or invalid values and filters the data to only include years between 1972 and 2012 
+#and individuals under the age of 89. Additionally, the code creates a new variable called "age_range" based on the age variable, which categorizes individuals 
+#into different age groups. Finally, the cleaned dataset is saved as a CSV file called "cleaned_data.csv" in the "outputs" folder. The cleaned dataset is now ready 
+# to be used for further analysis and modeling.
+# Author: SHAOHAN CHANG  
+# Data: 14 March 2023 
+# Contact: SHAOHAN.CHANG@utoronto.ca 
+# License: MIT
+# Pre-requisites:
+## 1. Go the website : https://gss.norc.org/get-the-data/stata
+## 2.Scroll down to the "Stata Data" section and click the "Download the GSS Stata data files" link.
+## 3. Select the years you want to download from the list provided. You can select multiple years by holding down the "Ctrl" key on your keyboard while clicking on the years you want.
+## 4. Click the "Download Selected Files" button at the bottom of the page. 
+## 5. On the next page, select the "Stata" file format.
+## 6. Select "ALL" from the drop down menu next to the green "ALL" button to download all variables.
+## 7. Click the "Create File" button and wait for the file to be generated.
+## 8. Once the file has been created, click the "Download File" button to save the file to your computer.
+# Any other information needed? [...UPDATE THIS...]
+## 1. Make sure to note the location where the downloaded data file is saved on your computer, as you will need to provide the file path when reading the data into R.
+## 2. The GSS data file is likely to be very large, especially if you downloaded the data for multiple years. It may be necessary to filter the data to a specific time period or subset of 
+# variables in order to work with it more efficiently. This can be done using functions like subset() or dplyr::select().
+## 3. Since the downloaded data file is in Stata format, you will need to use a package like "haven" or "foreign" to read the data into R. For example, you can use the haven::read_dta() 
[…]

### 2023-03-29 scripts/04-test_data.R

@@ -1,0 +1,52 @@
+#### Preamble ####
+# Purpose: The purpose of this code is to conduct a series of tests on the data frame to check for the presence of missing (NA) values in various variables. By running these tests, the user can ensure the data is complete and free of missing values before proceeding with further analysis.Test One: The code checks for any missing values across the entire data frame.Test Two: The code examines the 'happy' variable for missing values.Test Three: The code assesses the 'year' variable for missing values.Test Four: The code evaluates the 'sex' variable for missing values.Test Five: The code inspects the 'degree' variable for missing values.For each test, the code prints "Check passed" if there are no missing values, and "Check failed" if missing values are detected. This information helps the user decide on necessary data cleaning steps and maintain data integrity during analysis.
+# Author: SHAOHAN CHANG 
+# Data: 29 March 2023 
+# Contact: SHAOHAN.CHANG@Toronto.ca 
+# License: MIT
+# Pre-requisites: Prior to executing these tests on the test data, it is presumed that the data has already been imported into R and stored as a data frame. Additionally, it is assumed that the necessary packages for performing these tests, such as "dplyr" or "tidyverse", have been installed and loaded in R. It is also crucial to comprehend the research question and objectives, as this knowledge will steer the data analysis and establish the most suitable tests to employ.Moreover, it is advisable to meticulously examine the cookbook or documentation for the dataset, as this will supply vital details about the variables, their definitions, and any coding or missing value conventions utilized in the dataset. By possessing a thorough understanding of these prerequisites, researchers can guarantee that their data analysis is well-founded and precise.
+
+#### Work space setup ####
+library(tidyverse)
+library(janitor)
+library(dplyr)
+
+
+#### Test data ####
+
+
+data <- 
+  readr::read_csv("inputs/data/cleaned_data.csv")
+
+# Test One : Check for NA values in the data frame.
+# Explanation : as the result , there 0 NA value. 
+
+check_result <- ifelse(sum(is.na(data)) == 0, "Check passed", "Check failed")
+print(check_result)
+
+
+# Test Two : Check for NA values in happy. 
+
+# Explanation :  Three are 0 missing values in the happy. 
+
+check_result <- ifelse(sum(is.na(data$happy)) == 0, "Check passed", "Check failed")
+print(check_result)
+
+
+# Test Three : Check for NA values in year.
[…]

### 2023-03-30 scripts/00-simulate_data.R
Delete scripts directory

@@ -1,39 +1,0 @@
-#### Preamble ####
-# Purpose:The code above simulates a dataset called "happiness_and_income" with information on individuals' happiness, income, and other characteristics. 
-#The "set.seed" function sets a specific seed for the random number generator, ensuring that the same random values are generated each time the code is run.
-#The "size_of_population" variable sets the number of individuals in the simulated population.The "tibble" function creates a table with columns for the year of observation, 
-#age, sex, education level ("degree"), job satisfaction ("job_satisfied"), happiness level ("happy"), satisfaction level ("sat"), and age group ("age2").The "sample" function generates 
-#random samples for each of these variables, with the "replace" argument set to TRUE so that each individual can be sampled more than once.The "mutate" function creates a new column for 
-#age group based on the age variable, with individuals grouped into "age 18-39", "age 40-59", or "age 60+" based on their age.Overall, this code is simulating a population of individuals 
-#with varying characteristics, including their level of happiness, income, and education, among other variables. This type of simulation could be used to explore relationships between 
-#these variables and test different hypotheses.
-# Author: SHAOHAN CHANG  
-# Data: 29 March 2023 
-# Contact: SHAOHAN.CHANG@utoronto.ca
-# License: MIT
-# Pre-requisites: You have downloaded the data from the library. To do that:
-## 1. Go the website : https://gss.norc.org/get-the-data/stata
-## 2.Download the all file from 1972 to the 2012 file. 
-## 3. Click the file of download.
-## 4. select the SATA file 
-## 5. Can select all variables by clicking button next to the green colored 'ALL'. Then continue 
-## 6. Create the file, download and save the file. 
-# Any other information needed? 
-## 1. It is important to note the location where the downloaded data file is saved on your computer, as this will be needed when reading the data into R.
-## 2. The downloaded data file is likely to be very large, as it contains survey data from 1972 to 2012. It may be necessary to filter the data to a specific 
-# time period or subset of variables in order to work with it more efficiently.
-## 3. The downloaded data file is likely to be in Stata format, so it will need to be read into R using a package like "haven" or "foreign".
-## 4. It is also important to familiarize oneself with the codebook or documentation for the dataset, which can be found on the GSS website or in the downloaded file. 
-# This will provide information on the variables and their meanings, as well as any codes or missing values used in the dataset.
[…]

### 2023-03-30 scripts/01-download_data.R

@@ -1,3 +1,0 @@
-# Explain how you download the data
-
-The General Social Survey (GSS) is a comprehensive survey conducted in the United States since 1972 to 2012, providing insight into various social and demographic trends and attitudes. Accessing and analyzing the data requires downloading the data package from the GSS website and cleaning and processing the data to select relevant variables for the research question. This may involve dropping irrelevant variables, transforming or recording variables, and creating new variables. Once the data cleaning is complete, the selected variables can be analyzed using statistical software or other analytical tools to explore patterns and relationships. Despite being a valuable source of information, careful attention to data cleaning and analysis is crucial to ensure the validity and reliability of the findings.

### 2023-03-30 scripts/02-data_cleaning.R

@@ -1,143 +1,0 @@
-#### Preamble ####
-# Purpose: The purpose of this code is to clean and preprocess a dataset called "the_raw_data", which contains information about individuals' demographics, 
-#employment status, job satisfaction, and happiness. The code selects relevant variables from the dataset, converts them into factors, and renames them to 
-#more understandable names. It also removes any observations with missing or invalid values and filters the data to only include years between 1972 and 2012 
-#and individuals under the age of 89. Additionally, the code creates a new variable called "age_range" based on the age variable, which categorizes individuals 
-#into different age groups. Finally, the cleaned dataset is saved as a CSV file called "cleaned_data.csv" in the "outputs" folder. The cleaned dataset is now ready 
-# to be used for further analysis and modeling.
-# Author: SHAOHAN CHANG  
-# Data: 14 March 2023 
-# Contact: SHAOHAN.CHANG@utoronto.ca 
-# License: MIT
-# Pre-requisites:
-## 1. Go the website : https://gss.norc.org/get-the-data/stata
-## 2.Scroll down to the "Stata Data" section and click the "Download the GSS Stata data files" link.
-## 3. Select the years you want to download from the list provided. You can select multiple years by holding down the "Ctrl" key on your keyboard while clicking on the years you want.
-## 4. Click the "Download Selected Files" button at the bottom of the page. 
-## 5. On the next page, select the "Stata" file format.
-## 6. Select "ALL" from the drop down menu next to the green "ALL" button to download all variables.
-## 7. Click the "Create File" button and wait for the file to be generated.
-## 8. Once the file has been created, click the "Download File" button to save the file to your computer.
-# Any other information needed? [...UPDATE THIS...]
-## 1. Make sure to note the location where the downloaded data file is saved on your computer, as you will need to provide the file path when reading the data into R.
-## 2. The GSS data file is likely to be very large, especially if you downloaded the data for multiple years. It may be necessary to filter the data to a specific time period or subset of 
-# variables in order to work with it more efficiently. This can be done using functions like subset() or dplyr::select().
-## 3. Since the downloaded data file is in Stata format, you will need to use a package like "haven" or "foreign" to read the data into R. For example, you can use the haven::read_dta() 
[…]

### 2023-03-30 scripts/04-test_data.R

@@ -1,52 +1,0 @@
-#### Preamble ####
-# Purpose: The purpose of this code is to conduct a series of tests on the data frame to check for the presence of missing (NA) values in various variables. By running these tests, the user can ensure the data is complete and free of missing values before proceeding with further analysis.Test One: The code checks for any missing values across the entire data frame.Test Two: The code examines the 'happy' variable for missing values.Test Three: The code assesses the 'year' variable for missing values.Test Four: The code evaluates the 'sex' variable for missing values.Test Five: The code inspects the 'degree' variable for missing values.For each test, the code prints "Check passed" if there are no missing values, and "Check failed" if missing values are detected. This information helps the user decide on necessary data cleaning steps and maintain data integrity during analysis.
-# Author: SHAOHAN CHANG 
-# Data: 29 March 2023 
-# Contact: SHAOHAN.CHANG@Toronto.ca 
-# License: MIT
-# Pre-requisites: Prior to executing these tests on the test data, it is presumed that the data has already been imported into R and stored as a data frame. Additionally, it is assumed that the necessary packages for performing these tests, such as "dplyr" or "tidyverse", have been installed and loaded in R. It is also crucial to comprehend the research question and objectives, as this knowledge will steer the data analysis and establish the most suitable tests to employ.Moreover, it is advisable to meticulously examine the cookbook or documentation for the dataset, as this will supply vital details about the variables, their definitions, and any coding or missing value conventions utilized in the dataset. By possessing a thorough understanding of these prerequisites, researchers can guarantee that their data analysis is well-founded and precise.
-
-#### Work space setup ####
-library(tidyverse)
-library(janitor)
-library(dplyr)
-
-
-#### Test data ####
-
-
-data <- 
-  readr::read_csv("inputs/data/cleaned_data.csv")
-
-# Test One : Check for NA values in the data frame.
-# Explanation : as the result , there 0 NA value. 
-
-check_result <- ifelse(sum(is.na(data)) == 0, "Check passed", "Check failed")
-print(check_result)
-
-
-# Test Two : Check for NA values in happy. 
-
-# Explanation :  Three are 0 missing values in the happy. 
-
-check_result <- ifelse(sum(is.na(data$happy)) == 0, "Check passed", "Check failed")
-print(check_result)
-
-
-# Test Three : Check for NA values in year.
[…]

### 2023-03-30 outputs/paper/paper.qmd
Add files via upload

@@
 ---
-title: "Exploring Relationships between Demographic Characteristics, Health, Finances, Living Arrangements, and Happiness: An Analysis of the General Social Survey (GSS) Data from 1972 to 2012"
-subtitle: ""
+title: "Exploring Relationships between Demographic Characteristics, Health, Finances, Living Arrangements, and Happiness"
+subtitle: "An Analysis of the General Social Survey (GSS) Data from 1972 to 2012"
 author: 
@@
 data %>%
-  select(14:16) %>%
+  select(14:15) %>%
   slice(1:5) %>%
@@
 It is a categorical variable with different levels of satisfaction: very satisfied, more or less satisfied, not very satisfied, and not at all satisfied.
--   living_area: This variable indicates the type of living area in which the individual resided at the time the data was collected.
-It is a categorical variable with different levels: large city, small city, suburban, and rural.
 -   happy: This variable indicates the individual's level of happiness or life satisfaction.

### 2023-03-30 scripts/02-data_cleaning.R

@@ -1,0 +1,131 @@
+#### Preamble ####
+# Purpose: The purpose of the final line write_csv(data, "inputs/data/cleaned_data.csv") is to save the 
+#cleaned and transformed data into a CSV file named "cleaned_data.csv" in the directory "inputs/data". 
+#This line is saving the cleaned data as a CSV file so that it can be easily loaded and used in future 
+#analysis or modeling.This is a good practice because it ensures that the cleaned data can be easily accessed
+#and used later on without having to repeat the cleaning and transformation process every time. It also allows 
+#for easier sharing of the cleaned data with others who may need to use it.
+# Author: SHAOHAN CHANG  
+# Data: 14 March 2023 
+# Contact: SHAOHAN.CHANG@utoronto.ca 
+# License: MIT
+# Pre-requisites:
+## 1. Go to the GSS website by entering https://gss.norc.org/get-the-data/stata into your web browser.
+## 2.Scroll down the page until you find the "Stata Data" section, and then click on the "Download the GSS Stata data files" link.
+## 3. Select the years of interest from the list provided, and if you need to download multiple years, hold down the "Ctrl" key while clicking to select each year.
+## 4. Click the "Download Selected Files" button located at the bottom of the page. 
+## 5. On the next page, select the "Stata" file format.
+## 6. To download all variables, choose "ALL" from the drop-down menu next to the green "ALL" button.
+## 7. Click the "Create File" button and wait for the file to be generated. This may take a few moments, depending on the size of the file and your internet connection.
+## 8. Once the file has been created, click the "Download File" button to save it to your computer. Make sure to save the file in a location where you can easily find it later.
+
+# Any other information needed?
+## 1. Take note of the file path where the downloaded data file is saved on your computer, as this information is necessary to read the data into R.
+## 2. Keep in mind that the GSS data file can be quite large, especially if you have downloaded multiple years of data. To work with it more efficiently, consider filtering the data to a specific time period or a subset of variables using functions like subset() or dplyr::select().
+## 3. Because the downloaded data file is in Stata format, you'll need to use a package like "haven" or "foreign" to read the data into R. For example, you can use the haven::read_dta() function.
[…]

### 2023-04-01 outputs/paper/paper.qmd
Add files via upload

@@
 
-# Model
+# Model : Linear Regression
 
@@
 
-The [@tbl-lm], which is based the equation of @eq-model :
+In @eq-model:
+
+-   ${\hat{Y}}$ is predicted value of the dependent variable. This is the outcome we're trying to predict or estimate based on the independent variables.
+-   ${\hat{\beta_0}}$ : The intercept term, which represents the expected value of ${\hat{Y}}$ when all independent variables are equal to 0.
+-   ${\hat{\beta_1}}$ , ${\hat{\beta_2}}$ , ${\hat{\beta_3}}$ , ${\hat{\beta_4}}$ , ${\hat{\beta_5}}$ and ${\hat{\beta_6}}$ are the estimated coefficients for each independent variable.
+These coefficients indicate the average change in the dependent variable ${\hat{Y}}$ associated with a one-unit change in the corresponding independent variable, holding all other variables constant.
+The independent variables are:
+-   $X_{age}$ : Age of the individual.
+-   $X_{degree-score}$ : A measure of the individual's level of education or degree. 
+-   $X_{finance-score}$ : A measure of the individual's financial stability or status.
+-   $X_{health-score}$ : A measure of the individual's overall health.
+-   $X_{divorce-score}$ : A measure of the individual's likelihood of divorce or past divorces.
+-   $X_{babies-number}$ : The number of babies/children the individual has.
+
+The purpose of this multiple linear regression model is to understand the relationship between these independent variables and the dependent variable.
+By fitting the model to a dataset, we can estimate the coefficients and make predictions for new observations.
+we can also use the model to identify which independent variables have the most significant impact on the dependent variable and determine the strength and direction of those relationships.The [@tbl-lm], which is based the equation of @eq-model :
 

### 2023-04-03 scripts/03-test_data.R
Delete scripts directory

@@ -1,58 +1,0 @@
-#### Preamble ####
-# Purpose: The purpose of these tests is to check for missing values (NA values) in different variables of the "cleaned_data.csv" dataset. 
-#These tests ensure that the data is clean and complete, and suitable for further analysis. Test One checks the entire dataset for any NA values, 
-#while Tests Two to Five specifically check for NA values in the "happy", "year", "sex", and "health" variables, respectively. The if else() function
-#is used to print a message indicating whether the check has passed or failed.
-# Author: SHAOHAN CHANG 
-# Data: 29 March 2023 
-# Contact: SHAOHAN.CHANG@Toronto.ca 
-# License: MIT
-# Pre-requisites: The prerequisite for running these tests is that the "cleaned_data.csv" dataset has been cleaned and prepared for analysis. The dataset 
-#should also be in a format that is compatible with the readr::read_csv() function used to read the data into R. Additionally, the R environment must be set
-#up with the necessary packages for performing data analysis, such as readr. Finally, the user should have a basic understanding of R programming and data 
-#analysis techniques, including how to write and run R scripts.
-
-#### Work space setup ####
-library(tidyverse)
-library(janitor)
-library(dplyr)
-
-
-#### Test data ####
-
-
-data <- 
-  readr::read_csv("inputs/data/cleaned_data.csv")
-
-# Test One : Check for NA values in the data frame.
-# Explanation : as the result , there 0 NA value. 
-
-check_result <- ifelse(sum(is.na(data)) == 0, "Check passed", "Check failed")
-print(check_result)
-
-
-# Test Two : Check for NA values in happy. 
-
-# Explanation :  Three are 0 missing values in the happy. 
-
-check_result <- ifelse(sum(is.na(data$happy)) == 0, "Check passed", "Check failed")
-print(check_result)
-
-
-# Test Three : Check for NA values in year.
-# Explanation :There are 0 missing values in the year variable. 
-
-check_result <- ifelse(sum(is.na(data$year)) == 0, "Check passed", "Check failed")
-print(check_result)
-
-# Test Four : Check for NA values in sex. 
-# Explanation :There are 0 missing values in the sex variable.
-
-check_result <- ifelse(sum(is.na(data$sex)) == 0, "Check passed", "Check failed")
-print(check_result)
-
-# Test Five : Check for NA values in health. 
-# Explanation :There are 0 missing values in the health variable.
-
-check_result <- ifelse(sum(is.na(data$degree)) == 0, "Check passed", "Check failed")
-print(check_result)

### 2023-04-03 outputs/paper/paper.qmd
Add files via upload

@@
 date-format: "D MMMM YYYY"
-abstract: "This paper presents an analysis of a subset of the General Social Survey (GSS) data from the year 1972, which includes information on individuals' demographic characteristics, health, finances, living arrangements, and subjective well-being.
-The study aimed to explore various aspects of individuals' lives during the early 1970s in the United States, such as social stratification, gender roles, family dynamics, health disparities, and subjective well-being.The dataset consists of 5 observations and 10 variables, including year, age, sex, babies, divorce, health, finance_satisfied, living_area, and happy.
+abstract: "This paper presents an analysis of a subset of the General Social Survey (GSS) data from the year 1972, which includes information on individuals' demographic characteristics, health, finances and subjective well-being.
+The study aimed to explore various aspects of individuals' lives during the early 1970s in the United States, such as social stratification, gender roles, family dynamics, health disparities, and subjective well-being.The dataset consists of 13 observations and 24947 variables, for example: including year, age, sex, babies, divorce, health, finance satisfied and happy.
 The study used graphical representation to analyze the relationships between different variables in the dataset and individuals' level of happiness.
@@
 One such survey is the General Social Survey (GSS), which has been conducted in the United States since 1972 to 2012.
-This data set is a subset of the GSS data from the year 1972, which includes information on individuals' demographic characteristics, health, finances, living arrangements, and subjective well-being.
+This data set is a subset of the GSS data from the year 1972, which includes information on individuals' demographic characteristics, health, finances and subjective well-being.
 While this is a relatively small data set, it provides a glimpse into the lives of individuals in the United States during a particular period in time.This paper aims to explore various aspects of individuals' lives during the early 1970s in the United States using the GSS data set.
@@
 This data-set contains information on various personal and demographic characteristics of individuals, collected between the years 1972 and 2012.
-The data-set includes variables such as age, sex, number of babies, divorce status, self-reported health status, financial satisfaction, living area, and level of happiness.
+The data-set includes variables such as age, sex, number of babies, divorce status, self-reported health status, financial satisfaction and level of happiness.
 The data-set can be used to study the relationships between these variables and to gain insights into factors that may influence an individual's overall life satisfaction.
@@
 
+### Analyzing the Impact of Family Size on Happiness
+
 ```{r}
@@
 
-### Baby
+### Exploring the Connection Between Childlessness and Happiness
 
@@
 
-### Health
+### The Interplay of Health and Happiness: Evaluating the Link Between Self-Perceived Health and Life Satisfaction
 
@@
 
-### Financial Satisfaction
+### The Financial Satisfaction-Happiness
 
@@
 
-### Divorce
+### Marital Status and Happiness: Comparing the Emotional Well-Being of Married and Divorced Individuals
 
@@
 
-### Degree
+### Education and Emotional Well-Being
 

### 2023-04-03 scripts/03-test_data.R

@@ -1,0 +1,58 @@
+#### Preamble ####
+# Purpose: The purpose of these tests is to check for missing values (NA values) in different variables of the "cleaned_data.csv" dataset. 
+#These tests ensure that the data is clean and complete, and suitable for further analysis. Test One checks the entire dataset for any NA values, 
+#while Tests Two to Five specifically check for NA values in the "happy", "year", "sex", and "health" variables, respectively. The if else() function
+#is used to print a message indicating whether the check has passed or failed.
+# Author: SHAOHAN CHANG 
+# Data: 29 March 2023 
+# Contact: SHAOHAN.CHANG@Toronto.ca 
+# License: MIT
+# Pre-requisites: The prerequisite for running these tests is that the "cleaned_data.csv" dataset has been cleaned and prepared for analysis. The dataset 
+#should also be in a format that is compatible with the readr::read_csv() function used to read the data into R. Additionally, the R environment must be set
+#up with the necessary packages for performing data analysis, such as readr. Finally, the user should have a basic understanding of R programming and data 
+#analysis techniques, including how to write and run R scripts.
+
+#### Work space setup ####
+library(tidyverse)
+library(janitor)
+library(dplyr)
+
+
+#### Test data ####
+
+
+data <- 
+  readr::read_csv("inputs/data/cleaned_data.csv")
+
+# Test One : Check for NA values in the data frame.
+# Explanation : as the result , there 0 NA value. 
+
+check_result <- ifelse(sum(is.na(data)) == 0, "Check passed", "Check failed")
+print(check_result)
+
+
+# Test Two : Check for NA values in happy. 
+
+# Explanation :  Three are 0 missing values in the happy. 
+
+check_result <- ifelse(sum(is.na(data$happy)) == 0, "Check passed", "Check failed")
+print(check_result)
+
+
+# Test Three : Check for NA values in year.
+# Explanation :There are 0 missing values in the year variable. 
+
+check_result <- ifelse(sum(is.na(data$year)) == 0, "Check passed", "Check failed")
+print(check_result)
+
+# Test Four : Check for NA values in sex. 
+# Explanation :There are 0 missing values in the sex variable.
+
+check_result <- ifelse(sum(is.na(data$sex)) == 0, "Check passed", "Check failed")
+print(check_result)
+
+# Test Five : Check for NA values in health. 
+# Explanation :There are 0 missing values in the health variable.
+
+check_result <- ifelse(sum(is.na(data$degree)) == 0, "Check passed", "Check failed")
+print(check_result)

### 2023-04-04 scripts/01-download_data.R
Delete scripts directory

@@ -1,9 +1,0 @@
-# Explain how you download the data
-
-#The General Social Survey (GSS) is a comprehensive survey conducted in the United States since 1972 to 2012, 
-#providing insight into various social and demographic trends and attitudes. Accessing and analyzing the data 
-#requires downloading the data package from the GSS website and cleaning and processing the data to select relevant 
-#variables for the research question. This may involve dropping irrelevant variables, transforming or recording variables, 
-#and creating new variables. Once the data cleaning is complete, the selected variables can be analyzed using statistical software 
-#or other analytically tools to explore patterns and relationships. Despite being a valuable source of information, careful attention #
-#to data cleaning and analysis is crucial to ensure the validity and reliability of the findings.

### 2023-04-04 scripts/02-data_cleaning.R

@@ -1,131 +1,0 @@
-#### Preamble ####
-# Purpose: The purpose of the final line write_csv(data, "inputs/data/cleaned_data.csv") is to save the 
-#cleaned and transformed data into a CSV file named "cleaned_data.csv" in the directory "inputs/data". 
-#This line is saving the cleaned data as a CSV file so that it can be easily loaded and used in future 
-#analysis or modeling.This is a good practice because it ensures that the cleaned data can be easily accessed
-#and used later on without having to repeat the cleaning and transformation process every time. It also allows 
-#for easier sharing of the cleaned data with others who may need to use it.
-# Author: SHAOHAN CHANG  
-# Data: 14 March 2023 
-# Contact: SHAOHAN.CHANG@utoronto.ca 
-# License: MIT
-# Pre-requisites:
-## 1. Go to the GSS website by entering https://gss.norc.org/get-the-data/stata into your web browser.
-## 2.Scroll down the page until you find the "Stata Data" section, and then click on the "Download the GSS Stata data files" link.
-## 3. Select the years of interest from the list provided, and if you need to download multiple years, hold down the "Ctrl" key while clicking to select each year.
-## 4. Click the "Download Selected Files" button located at the bottom of the page. 
-## 5. On the next page, select the "Stata" file format.
-## 6. To download all variables, choose "ALL" from the drop-down menu next to the green "ALL" button.
-## 7. Click the "Create File" button and wait for the file to be generated. This may take a few moments, depending on the size of the file and your internet connection.
-## 8. Once the file has been created, click the "Download File" button to save it to your computer. Make sure to save the file in a location where you can easily find it later.
-
-# Any other information needed?
-## 1. Take note of the file path where the downloaded data file is saved on your computer, as this information is necessary to read the data into R.
-## 2. Keep in mind that the GSS data file can be quite large, especially if you have downloaded multiple years of data. To work with it more efficiently, consider filtering the data to a specific time period or a subset of variables using functions like subset() or dplyr::select().
-## 3. Because the downloaded data file is in Stata format, you'll need to use a package like "haven" or "foreign" to read the data into R. For example, you can use the haven::read_dta() function.
[…]

### 2023-04-04 outputs/paper/paper.qmd
Add files via upload

@@
 ---
-title: "Exploring Relationships between Demographic Characteristics, Health, Finances, Living Arrangements, and Happiness"
-subtitle: "An Analysis of the General Social Survey (GSS) Data from 1972 to 2012"
+title: "Examining the Multifaceted Impact of Family Size on Happiness, Health, Gender Dynamics, and Financial Well-being"
+subtitle: ""
 author: 
   - SHAOHAN CHANG
-thanks: "Code and data are available at: https://github.com/lucas11333/Factor_of_Wellbeing"
+thanks: "Code and data are available at: https://github.com/lucas11333/Of_Wellbeing"
 date: "`r Sys.time()`"
 date-format: "D MMMM YYYY"
-abstract: "This paper presents an analysis of a subset of the General Social Survey (GSS) data from the year 1972, which includes information on individuals' demographic characteristics, health, finances and subjective well-being.
-The study aimed to explore various aspects of individuals' lives during the early 1970s in the United States, such as social stratification, gender roles, family dynamics, health disparities, and subjective well-being.The dataset consists of 13 observations and 24947 variables, for example: including year, age, sex, babies, divorce, health, finance satisfied and happy.
-The study used graphical representation to analyze the relationships between different variables in the dataset and individuals' level of happiness.
-The results of the analysis suggest that there is a positive relationship between people's satisfaction with their current financial situation, their self-rated health, and their level of happiness in life.
-Additionally, being divorced may have a slight impact on one's level of happiness in life, with a small proportion of individuals feeling not too happy.
-Moreover, the study found that people's level of education is positively associated with their level of happiness in life, as people's education level increases, their level of happiness also gradually increases.Overall, this study provides valuable insights into various aspects of individuals' lives during the early 1970s in the United States.
-The findings can be useful for researchers and students interested in exploring topics such as social stratification, gender roles, family dynamics, health disparities, and subjective well-being.
-The study highlights the importance of considering different factors that can influence individuals' level of happiness and well-being, such as their financial situation, health status, and level of education.
-Further research could investigate more recent data from the GSS to examine changes in these relationships over time."
+abstract: "This study analyzed the relationship between family size, measured by the number of children, and various aspects of family life, such as happiness, health, and financial satisfaction.
+The findings suggest that happiness levels are highest among childless individuals, while families with one child report the best health status.
+Additionally, higher financial satisfaction is associated with fewer children in a family.
+These insights matter as they provide a better understanding of the factors influencing family size and the potential consequences of family planning decisions on overall wellbeing."
 format: pdf
@@
 
-Surveys are a common method for collecting data on individuals' attitudes, behaviors, and experiences in social science research.
-One such survey is the General Social Survey (GSS), which has been conducted in the United States since 1972 to 2012.
-This data set is a subset of the GSS data from the year 1972, which includes information on individuals' demographic characteristics, health, finances and subjective well-being.
-While this is a relatively small data set, it provides a glimpse into the lives of individuals in the United States during a particular period in time.This paper aims to explore various aspects of individuals' lives during the early 1970s in the United States using the GSS data set.
-The variables in this data set are diverse and reflect a range of aspects of individuals' lives.
-For instance, the variables on babies and divorce provide information on individuals' family structures, while the variables on health and finance satisfaction offer insights into their well-being and financial stability [@b].
-The data set also includes variables on individuals' living arrangements and their subjective well-being, providing a glimpse into their social context and overall happiness.
+The impact of the number of children in a family on various aspects of family life has been a topic of interest for researchers and policymakers alike [@a].
+Family size and structure play a crucial role in shaping the lives of individuals and communities.
+Understanding the connections between the number of children and factors such as happiness, health, sex distribution, and financial satisfaction can help inform decisions and policies aimed at promoting family well being [@b].
+This paper seeks to explore these relationships and shed light on the complex interplay between family size and various aspects of family life.
 
-The paper presents a comprehensive analysis of the relationships between different variables in the data set and individuals' level of happiness.
-The analysis includes a graphical representation of the relationship between the number of children and happiness in the family, individuals' self-rated health and their self-rated level of happiness, people's satisfaction with their financial situation and their happiness, the level of happiness in life for individuals in two different states: divorced or married, and the relationship between people's level of education and their level of happiness in life.The results of the analysis suggest that there is a positive relationship between people's satisfaction with their current financial situation, their self-rated health, and their level of happiness in life [@a].
-The analysis also indicates that being divorced may have a slight impact on one's level of happiness in life, with a small proportion of individuals feeling "not too happy." Additionally, as people's education level increases, their level of happiness also gradually increases.
+The paper examines the relationship between the number of children (0, 1, 2, 3, 4) in a family and different variables such as happiness, health, sex distribution, and financial satisfaction using multiple data sources.
+Previous research on this topic has often focused on specific aspects of family life or specific sub populations, leaving a gap in the understanding of the broader relationships between family size and different variables.
+This study aims to fill this gap by providing a comprehensive analysis of the relationship between the number of children in a family and various aspects of family life.
 
-Overall, this paper provides valuable insights into various aspects of individuals' lives during the early 1970s in the United States.
-The findings can be useful for researchers and students interested in exploring topics such as social stratification, gender roles, family dynamics, health disparities, and subjective well-being.
+Through the analysis of several charts and tables, this study uncovers patterns and trends in the data that suggest connections between the number of children in a family and the variables of interest.
+For example, the data reveals that families with better health tend to have a higher likelihood of having one or more children, while families with lower financial satisfaction tend to have more children [@c].
+However, the relationships identified in this study may not be linear, and it is important to consider the potential influence of other factors on the number of children in a family.
+
+The structure of the paper is as follows: first, we present the data and methodology used in the study, followed by a detailed analysis of the relationships between the number of children in a family and the variables of interest.
+Next, we discuss the implications of the findings and their relevance to broader discussions on family well being and policy.
+Finally, we conclude with a summary of the main findings and suggestions for future research in this area.
 
@@
 
-## Data {#sec-data}
+## Data
 
@@
 
-This data-set contains information on various personal and demographic characteristics of individuals, collected between the years 1972 and 2012.
+In @tbl-var contains information on various personal and demographic characteristics of individuals, collected between the years 1972 and 2012.
 The data-set includes variables such as age, sex, number of babies, divorce status, self-reported health status, financial satisfaction and level of happiness.
@@
 ```{r}
-#| eval: true
+#| message: false
+#| echo: false
 #| warning: false
-#| echo: false
+#| label: tbl-var
+#| tbl-cap: Report Data (First 5 rows)
 data %>%
-  select(1:8) %>%
+  select(1:6) %>%
   slice(1:5) %>%
-  kable(caption = "Table of Happy by Various Variables") %>%
+  kable() %>%
   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
@@
 ```{r}
-#| eval: true
+#| echo: false
 #| warning: false
-#| echo: false
-#| label: table-one
-#| table-cap: Report Data (First 5 rows)
-
 data %>%
-  select(9:13) %>%
-  slice(1:5) %>%
-  kable() %>%
-  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
-```
-
-```{r}
-#| eval: true
-#| warning: false
-#| echo: false
-data %>%
-  select(14:15) %>%
+  select(6:10) %>%
   slice(1:5) %>%
@@
 -   year: This variable indicates the year in which the data was collected. In this data-set, all the observations are from the year 1972 to 2012.
--   age: This variable indicates the age of the individual at the time the data was collected. It is a continuous variable measured in years.
 -   sex: This variable indicates the biological sex of the individual. It is a categorical variable with two levels: male and female.
@@
 It is a categorical variable with different levels, depending on the number of babies: 0, 1, 2, 3, 4, or 5+.
--   divorce: This variable indicates whether or not the individual had ever been divorced at the time the data was collected. It is a categorical variable with two levels: yes and no.
 -   health: This variable indicates the self-reported health status of the individual at the time the data was collected.
@@
 It is a categorical variable with different levels of happiness: very happy, pretty happy, not too happy, and not at all happy.
--   divorce_score: This variable is a binary representation of the divorce status of an individual in the dataset.
-The value '0' denotes that the individual is not divorced, while the value '1' indicates that they are divorced.
 -   happy_score: The happy_score variable is an ordinal variable representing the self-reported happiness levels of the individuals in the dataset.
 It ranges from 0 to 3, with 0 representing "not too happy," 1 representing "happy," 2 representing "very happy," and 3 reserved for any unclassified or missing responses.
--   degree_score: This ordinal variable represents the educational attainment of the individuals in the dataset.
-It ranges from 1 to 5, where 1 signifies "less than high school," 2 denotes "high school," 3 represents "associate/junior college," 4 refers to "bachelor's," and 5 indicates "graduate" level education.
-The value 6 is reserved for any unclassified or missing responses.
 -   health_score: The health_score variable is an ordinal variable indicating the self-reported health status of the individuals in the dataset.
@@
 
-In [@fig-one], this chart shows the number of people who are very happy, not too happy, and happy.
-Overall, the data indicates that the largest number of people are happy, with approximately 15,000 individuals falling into this category.
-On the other hand, the smallest number of people are not too happy, with significantly fewer individuals in this category compared to the other two variables.
-In summary, the data suggests that the number of unhappy individuals is a relatively small group.
-
-### Analyzing the Impact of Family Size on Happiness
-
-```{r}
-#| label: fig-one
-#| fig-cap: Couning of Happiness
-#| echo: false
-#| warning: false
-
-ggplot(data, aes(x = happy, fill = happy)) +
-  geom_bar() +
-  scale_fill_manual(values = c("#FFC107", "#FF5722", "#4CAF50", "#2196F3")) +
-  labs(fill = "Happiness level")+
-  coord_flip()
-
-```
-
 ### Exploring the Connection Between Childlessness and Happiness
 
-In [@fig-two], through the graph showing the relationship between the number of children and happiness in the family, it is obvious that when people have no children, the largest number of 'very happy', 'pretty happy', and 'not too happy' are shown.
+In [@fig-one],which analysis of this data is to calculate the number of children with 0, 1, 2, 3, 4.through the graph showing the relationship between the number of children and happiness in the family, it is obvious that when people have no children, the largest number of 'very happy', 'pretty happy', and 'not too happy' are shown.
 Although The preliminary judgment is that the number of people who are happy without children is the largest.
@@
 ```{r}
-#| label: fig-two
+#| label: fig-one
 #| fig-cap: Relationship between Number of Babies and Happiness
@@
 #| warning: false
-
 data %>%
-  filter(babies != "unknown") %>% 
   group_by(babies, happy) %>%
@@
   mutate(prop = n / sum(n)) %>%
-  ggplot(aes(x = factor(babies), y = prop, group = happy, color = happy)) +
-  geom_line(size = 1.5) +
-  stat_smooth(geom = "ribbon", alpha = 0.2) +
+  ggplot(aes(x = factor(babies), y = prop, fill = happy)) +
+  geom_bar(stat = "identity", position = "dodge") +
   scale_x_discrete(name = "Number of Babies", expand = c(0.1, 0.1)) +
   scale_y_continuous(labels = scales::percent_format(), name = "Percentage", expand = c(0.05, 0)) +
-  scale_color_discrete(name = "Happiness") +
+  scale_fill_discrete(name = "Happiness") +
+  theme_minimal() +
+  theme(plot.title = element_text(size = 16, face = "bold", margin = margin(b = 10)),
+        plot.subtitle = element_text(size = 14, margin = margin(b = 20)),
+        axis.title = element_text(size = 12, face = "bold"),
+        axis.text = element_text(size = 10),
+        legend.title = element_text(size = 12, face = "bold"),
+        legend.text = element_text(size = 10),
+        legend.position = "bottom")
+
+```
+
+In [@fig-two],which presented in the table indicates that the sex distribution varies depending on the number of babies in the family.
+A higher percentage of females compared to males is consistently observed across all groups.
+The lowest difference in sex distribution is found among families with no babies, where the female-to-male ratio is relatively closer.
+As the number of babies in a family increases, the percentage of females also increases, with the highest difference observed in families with one and four babies.
+In these groups, the sex distribution is more skewed towards females.
+
+```{r}
+#| label: fig-two
+#| fig-cap: Relationship between Number of Babies and Gender
+#| echo: false
+#| warning: false
+data %>%
+  group_by(babies, sex) %>%
+  summarize(n = n()) %>%
+  mutate(prop = n / sum(n)) %>%
+  ggplot(aes(x = factor(babies), y = prop, fill = sex)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  scale_x_discrete(name = "Number of Babies", expand = c(0.1, 0.1)) +
+  scale_y_continuous(labels = scales::percent_format(), name = "Percentage", expand = c(0.05, 0)) +
+  scale_fill_discrete(name = "Sex") +
   theme_minimal() +
@@
 
-### The Interplay of Health and Happiness: Evaluating the Link Between Self-Perceived Health and Life Satisfaction
+### The Relationship Between Number of Children and Self-Rated Health Status
 
-In [@fig-four], which represents the relationship between participants' self-rated health and their self-rated level of happiness.
-The chart shows that the proportion of participants who rated themselves as "very happy" was the highest among those who rated their health as "excellent".
-On the other hand, the proportion of participants who rated themselves as "not too happy" was the lowest among those who rated their health as "poor".From the overall trend, it can be inferred that the higher the participants' self-rated health, the higher their self-rated level of satisfaction with life.
+In [@fig-four], the analysis of the chart, it can be observed that when individuals have one child, there is a significantly higher proportion of participants who rate their health as 'good' or 'excellent' compared to other categories.
+In contrast, for participants who do not have any children, the proportion of those who rate their health as 'poor' is the highest, but no clear conclusion can be drawn from this finding.
+For individuals with three children, the feedback on their health status is evenly distributed among 'good', 'fair', and 'excellent', with a very small proportion of participants reporting 'poor' health.
+Overall, having one child is associated with the highest proportion of participants reporting 'excellent' health status.
 
@@
 #| label: fig-four
-#| fig-cap: Relationship between Health and Happiness
+#| fig-cap: Number of Children and Self-Rated Health Status
 #| echo: false
 #| warning: false
-ggplot(data, aes(x = health, fill = happy)) +
+
+ggplot(data, aes(x = health, fill = factor(babies))) +
   geom_bar(position = "fill") +
   scale_y_continuous(labels = scales::percent) +
-  labs(x = "Health", y = "Percentage of Happy Cases") +
+  labs(x = "Health", y = "Percentage of Cases by Number of Babies", fill = "Number of Babies") +
   theme_minimal() +
@@
 
-In [@fig-five], which spanning from 1970 to 2010, illustrates the relationship between participants' self-reported happiness levels and their health states.
-It is evident that when participants rated their health as 'poor', the proportion of those who identified as 'very happy' was notably lower compared to other health states.
-On the other hand, when participants reported their health as 'excellent' or 'good', the number of 'very happy' responses regarding their life satisfaction increased significantly.
-In summary, this chart suggests a positive correlation between people's health and their happiness in life.
+In [@fig-five], which present the dot plot, which represent the each number of babies in different condition of health, which explores the relationship between health and the number of babies in the family.
+The data is organized into four health categories - 'excellent', 'fair', 'good', and 'poor' - and five categories based on the number of babies, ranging from 0 to 4.The data reveals a pattern suggesting a connection between health status and the number of babies in a family.
+Families with 'excellent' health have a more balanced distribution of babies, with a higher proportion of families having one or two babies compared to those with poorer health.
+This trend indicates that better health is associated with a higher likelihood of having one or more babies.As the number of babies increases, the percentages for all four health categories tend to decrease.
+This pattern is most noticeable in the 'poor' health category, where the decline in percentages is more pronounced as the number of babies increases.In summary, the data suggests a relationship between health and the number of babies in a family.
+Better health is generally associated with a higher likelihood of having one or more babies, while poorer health tends to correlate with a lower likelihood.
+However, it is essential to consider that the relationship may not be linear and that other factors could also influence the number of babies in a family.
 
@@
 #| label: fig-five
-#| fig-cap: Relationship between Health and "Very Happy" With Year
+#| fig-cap: Relationship between Health and Number of Babies With Year
 #| echo: false
 #| warning: false
-ggplot(data[data$happy == "very happy", ], aes(x = year, y = health)) +
+
+ggplot(data[data$happy == "very happy", ], aes(x = year, y = factor(babies))) +
   geom_point(position = position_jitter(width = 0.2, height = 0.1), size = 2, color = "#4daf4a") +
   facet_wrap(~health, ncol = 5, scales = "free_y") +
-  labs(x = "Year", y = "Self-rated Health") +
+  labs(x = "Year", y = "Number of Babies") +
   theme_bw() +
@@
 
-### The Financial Satisfaction-Happiness
+### The Association Between Family Size and Financial Satisfaction
 
-In [@fig-six], the graph depicts the relationship between people's satisfaction with their financial situation and their happiness.It is clear that when people are not very satisfied with their current finances, the proportion of unhappy people in their lives is the highest.
-On the other hand, when people are very satisfied with their finances, the proportion of happy people in their lives is the highest, and the proportion of unhappy people is also the lowest.
-Therefore, it can be concluded that there is a positive relationship between people's satisfaction with their current financial situation and their level of happiness in life.
+In [@fig-six], which appears that the number of babies in a family is related to the level of financial satisfaction.
+In general, families with lower financial satisfaction, regardless of the category, tend to have a higher number of babies.
+This trend is observed across all three financial satisfaction levels.It is interesting to note that the majority of families in all financial satisfaction levels have 0 babies.
+However, the percentage of families with 0 babies is notably higher in the 'pretty well satisfied' category compared to the 'more or less satisfied' and 'not satisfied at all' categories.As the number of babies increases, the percentages for all three financial satisfaction categories tend to decrease.
+This pattern is more pronounced in the 'pretty well satisfied' category, where the decline in percentages is steeper as the number of babies increases.In summary, the data suggests a connection between financial satisfaction and the number of babies in a family.
+Families with higher financial satisfaction generally have fewer babies, while those with lower financial satisfaction have more babies.
+It is essential to consider that this relationship may not be linear, and other factors could also influence the number of babies in a family.
 
@@
 #| warning: false
-#| 
-ggplot(data, aes(x = finance_satified, fill = happy)) +
+ggplot(data, aes(x = finance_satified, fill = factor(babies))) +
   geom_bar(position = "fill") +
   scale_y_continuous(labels = scales::percent) +
-  labs(x = "Rate of Finance Satified ",
-       y = "Percentage of Happy Cases") +
-  theme_minimal() +
-  coord_flip()
-```
-
-### Marital Status and Happiness: Comparing the Emotional Well-Being of Married and Divorced Individuals
-
-In [@fig-seven], the graph represents the level of happiness in life for individuals in two different states: divorced or married.
-The graph shows that the levels of happiness in both marital states are almost similar.
-However, the proportion of people who feel "not too happy" in their lives is slightly higher among the divorced group than among the married group.
-In conclusion, being divorced may have a slight impact on one's level of happiness in life, with a small proportion of individuals feeling "not too happy."
-
-```{r}
-#| label: fig-seven
-#| fig-cap: Relationship between Happiness and Divorce
-#| echo: false
-#| warning: false
-ggplot(data, aes(x = divorce, fill = happy)) +
-  geom_bar(position = "fill") +
-  scale_y_continuous(labels = scales::percent) +
-  labs(x = "Divorce",
-       y = "Percentage of Happy Cases") +
-  theme_minimal() +
-  coord_flip()
-
-```
-
-In [@fig-eight], which based on the analysis of the charts, it appears that for the years 1972, 1975, 1982, 1990, 1996, 2002, and 2010, individuals who reported being divorced also reported a higher percentage of happy responses.
-On the other hand, for the years 1976, 1980, 1984, 1987, 1989, and 2006, individuals who reported being married reported a higher percentage of happy responses.
-Additionally, the percentage of individuals who reported "not too happy" was significantly higher for individuals who reported being divorced than for those who reported being married in the years 1973, 1984, 1987, 1990, 1991, 1993, 2008, and 2012.
-
-```{r fig.width= 8,fig.height= 4}
-#| label: fig-eight 
-#| fig-cap: Relationship between Divorce and Happiness by Year
-#| echo: false
-#| warning: false
-data %>%
-  filter(divorce != "unknown") %>%
-  group_by(year, divorce, happy) %>%
-  summarize(n = n()) %>%
-  mutate(prop = n / sum(n)) %>%
-  ggplot(aes(x = factor(divorce), y = prop, group = happy, color = happy)) +
-  geom_line(size = 1.5) +
-  stat_smooth(geom = "ribbon", alpha = 0.2) +
-  facet_wrap(~ year, nrow = 2) +
-  scale_x_discrete(name = "Divorce", expand = c(0.1, 0.1)) +
-  scale_y_continuous(labels = scales::percent_format(), name = "Percentage", expand = c(0.05, 0)) +
-  scale_color_discrete(name = "Happiness") +
-  theme_minimal() +
-  theme(plot.title = element_text(size = 16, face = "bold", margin = margin(b = 10)),
-        plot.subtitle = element_text(size = 14, margin = margin(b = 20)),
-        axis.title = element_text(size = 12, face = "bold"),
-        axis.text = element_text(size = 10),
-        legend.title = element_text(size = 12, face = "bold"),
-        legend.text = element_text(size = 10),
-        legend.position = "bottom")
-
-```
-
-### Education and Emotional Well-Being
-
-In [@fig-nine], which shows that there is a certain relationship between people's level of education and their level of happiness in life.
-From the graph, it can be observed that the proportion of people who feel "not too happy" is the highest among those with education levels lower than high school.
-However, the proportion of unhappy individuals is the lowest among those with bachelor's and graduate degrees, suggesting that as people's education level increases, their level of happiness also gradually increases.
-
-```{r}
-#| label: fig-nine
-#| fig-cap: Relationship between Happiness and Degree
-#| echo: false
-#| warning: false
-ggplot(data, aes(x = degree, fill = happy)) +
-  geom_bar(position = "fill") +
-  scale_y_continuous(labels = scales::percent) +
-  labs(x = "Degree",
-       y = "Percentage of Happy Cases") +
+  labs(x = "Rate of Finance Satisfaction",
+       y = "Percentage of Cases by Number of Babies",
+       fill = "Number of Babies") +
   theme_minimal() +
@@
 $$
-\hat{Y}=\hat{\beta_0}+\hat{\beta_1}X_{age}+\hat{\beta_2}X_{degree-score}+\hat{\beta_3}X_{finance-score}+\hat{\beta_4}X_{health-score} + \hat{\beta_5}X_{divorce-score} + 
+\hat{Y}=\hat{\beta_0}+\hat{\beta_1}X_{finance-score}+\hat{\beta_2}X_{health-score} + \hat{\beta_3}X_{happy} + 
 \hat{\beta_6}X_{babies-number} 
@@
 #| tbl-cap: Linear Model and its Summary Statistics
-model <- lm(data$happy_score ~ age +  degree_score + finance_score + health_score + divorce_score + babies_number, data=data)
+model <- lm(data$babies ~  finance_score + health_score + happy, data=data)
 
@@
   list(
-    "Well-Being" = model
+    "Babies" = model
   ),
@@
 
-In @eq-model:
+The @tbl-lm is built based on the @eq-model:
 
@@
 -   ${\hat{\beta_0}}$ : The intercept term, which represents the expected value of ${\hat{Y}}$ when all independent variables are equal to 0.
--   ${\hat{\beta_1}}$ , ${\hat{\beta_2}}$ , ${\hat{\beta_3}}$ , ${\hat{\beta_4}}$ , ${\hat{\beta_5}}$ and ${\hat{\beta_6}}$ are the estimated coefficients for each independent variable.
+-   ${\hat{\beta_1}}$ , ${\hat{\beta_2}}$ , ${\hat{\beta_3}}$ are the estimated coefficients for each independent variable.
 These coefficients indicate the average change in the dependent variable ${\hat{Y}}$ associated with a one-unit change in the corresponding independent variable, holding all other variables constant.
@@
 
-The purpose of this multiple linear regression model is to understand the relationship between these independent variables and the dependent variable.
-By fitting the model to a dataset, we can estimate the coefficients and make predictions for new observations.
-we can also use the model to identify which independent variables have the most significant impact on the dependent variable and determine the strength and direction of those relationships.The [@tbl-lm], which is based the equation of @eq-model :
-
--   Overall model significance: The F-statistic (314.461) indicates that the overall model is statistically significant, suggesting that the predictors included in the model collectively explain a meaningful portion of the variance in well-being.
--   Model fit: The R-squared (0.070) and adjusted R-squared (0.070) values are relatively low, indicating that only 7% of the variation in well-being is explained by the predictors in the model.
-This suggests that there may be other factors influencing well-being that have not been included in the model.
--   Age as a predictor: The coefficient for age (0.00) and its confidence interval (\[0.00, 0.00\]) suggest that age does not have a statistically significant effect on well-being in this model.
--   Degree score as a predictor: The positive coefficient for degree_score (0.02) and its confidence interval (\[0.01, 0.03\]) indicate that higher degree scores are associated with higher well-being.
-This suggests a positive relationship between educational achievement and well-being.
--   Finance score as a predictor: The negative coefficient for finance_score (−0.09) and its confidence interval (\[−0.11, −0.08\]) demonstrate that higher finance scores are associated with lower well-being.
-This indicates a negative relationship between financial stress and well-being.
--   Health score as a predictor: The positive coefficient for health_score (0.32) and its confidence interval (\[0.30, 0.34\]) show that higher health scores are associated with higher well-being.
-This suggests a strong positive relationship between health and well-being.
--   Divorce score as a predictor: The coefficient for divorce_score (−0.02) and its confidence interval (\[−0.05, 0.01\]) indicate that the effect of divorce_score on well-being is not statistically significant.
-This suggests that the relationship between divorce and well-being is inconclusive in this model.
--   Number of babies as a predictor: The negative coefficient for babies_number (−0.03) and its confidence interval (\[−0.05, −0.01\]) demonstrate that having more babies is associated with lower well-being.
-This indicates a negative relationship between the number of children and well-being.
-
-In conclusion of this result, the model shows that degree_score, finance_score, health_score, and babies_number are statistically significant predictors of well-being, while age and divorce_score are not.
-However, the low R-squared value suggests that there are likely other factors affecting well-being that have not been included in the model.
+The given multiple linear regression analysis aimed to predict an unspecified dependent variable based on several independent variables, including babies (intercept), finance score, health score, and two levels of happiness (not too happy and very happy).
+The model's overall explanatory power is quite low, with an R² of 0.009, indicating that it only accounts for 0.9% of the variation in the dependent variable.The finance and health scores both have positive relationships with the dependent variable, with coefficients of 0.03 and 0.06, respectively.
+The confidence intervals for these variables do not include zero, suggesting that these relationships are statistically significant.
+However, the coefficients for the happiness levels (not too happy and very happy) are small and have confidence intervals that include zero, which indicates that they might not be significantly related to the dependent variable.
 
@@
 
-## Table of Relationship between Number of Children and Happiness in the Family.
+## Table of Relationship between Number of Children and Gender.
 
-In the table two, which appears to be presenting data on the happiness levels of babies, as rated by some measure or criteria, at different ages from 0 to 4 years old.
-The three categories of happiness levels are "not too happy," "happy," and "very happy." Looking at the data for 4-year-old, we can see that 48.15% of them were rated as "not too happy," 14.81% as "very happy," and the remaining 37.04% as simply "happy." This suggests that the majority of 4-year-old were not rated as particularly happy, with less than half of them falling into the happy or very happy categories.
+In the Table 3 ,which presented in the table indicate that the sex distribution varies depending on the number of babies in the family.Across all groups, there is a consistent pattern of a higher percentage of females compared to males.
+The lowest difference in sex distribution is observed among families with no babies, where the female-to-male ratio is relatively closer (54.53% female vs.
+45.47% male).
+As the number of babies in a family increases, the percentage of females also increases, with the highest difference observed in families with 1 and 4 babies.
+In these groups, the sex distribution is more skewed towards females, with 60.92% and 60.98% female representation, respectively.
 
 ```{r}
-#| eval: true
+#| message: false
+#| echo: false
 #| warning: false
+
+sex_table <- data %>% 
+  group_by(babies, sex) %>% 
+  summarize(response = n(), variance = var(as.numeric(sex))) %>%
+  mutate(percent = round(response/sum(response)*100, 2)) %>%
+  select(babies, sex, percent) %>%
+  spread(sex, percent)
+
+kable(sex_table, caption = "Relationship between Number of Children and Gender") %>%
+  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
+
+```
+
+## Distribution of Happiness Levels Across Families with Different Numbers of Babies
+
+In the Table 4, which suggests that families with 4 babies have the highest proportion of "happy" individuals at 63.41%.
+In contrast, families with 3 babies have the highest proportion of "not too happy" individuals at 16.57% and the lowest proportion of "happy" individuals at 50.30%.
+Families with 0, 1, and 2 babies have relatively similar distributions of happiness levels.
+It is worth noting that families with 3 babies have the highest proportion of "very happy" individuals at 33.14%, followed closely by families with 2 babies at 32.95%.
+Families with 4 babies have the lowest proportion of "very happy" individuals at 24.39%.
+
+```{r}
+#| message: false
 #| echo: false
-#| label: table-two
-#| table-cap: Table of Happy by Various Variables
+#| warning: false    
 happy_table <- data %>% 
-  filter(babies != "unknown") %>%
   group_by(babies, happy) %>% 
@@
 
-kable(happy_table, caption = "Table of Happy by Various Variables") %>%
+kable(happy_table, caption = "Happiness Levels Across Families with number of Babies") %>%
   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
@@
 
-## Table of Health and Happiness in the Family
+## Distribution of Self-Rated Health Status Across Families with Different Numbers of Babies
 
-In table three, which appears to be presenting data on the relationship between the health and happiness levels of families, based on some measure or criteria.
-The three categories of happiness levels are "not too happy," "happy," and "very happy," while the four categories of health are "excellent," "fair," "good," and "poor." Looking at the data, we can see that families who rated their health as "excellent" had the highest proportion of respondents who reported being "very happy," at 53.70%, and the lowest proportion of those who were "not too happy," at only 4.94%.
-In contrast, families who rated their health as "fair" had the highest proportion of respondents who were "not too happy," at 15.92%, and the lowest proportion of those who were "very happy," at only 25.81%.
+In Table 5, which appears suggests that individuals without any babies tend to have higher percentages in all health categories, especially in the "poor" health category (93.52%).
+As the number of babies in a family increases, the proportion of individuals in the "excellent," "fair," and "good" health categories generally decreases.
+The "poor" health category also follows this trend, but the decrease is less pronounced.
+Individuals with 1 or 2 babies have relatively similar health status distributions, with slightly higher percentages in the "excellent" and "good" health categories compared to the "fair" and "poor" health categories.
+Individuals with 3 or 4 babies have the lowest percentages across all health categories.
 
 ```{r}
-#| eval: true
+#| message: false
+#| echo: false
 #| warning: false    
-#| echo: false
-#| label: table-three
-#| table-cap: Table of Health and Happiness in the Family
 health_happy_table <- data %>%
-  group_by(health, happy) %>%
-  summarize(response = n(), variance = var(as.numeric(happy))) %>%
+  group_by(health, babies) %>%
+  summarize(response = n(), variance = var(as.numeric(babies))) %>%
   mutate(percent = round(response / sum(response) * 100, 2)) %>%
-  select(health, happy, percent) %>%
-  spread(happy, percent)
+  select(health, babies, percent) %>%
+  spread(babies, percent)
 
-kable(health_happy_table, caption = "Table of Health and Happiness in the Family") %>%
+kable(health_happy_table, caption = "Health Status with number of Babies") %>%
   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
@@
 
-## Table of Financial Satisfaction and Happiness in the Family
+## Distribution of Financial Satisfaction Across Families with Different Numbers of Babies
 
-In table four, which appears that the table is presenting data on the relationship between financial satisfaction and happiness levels in families, based on some measure or criteria.
-The three categories of happiness levels are "not too happy," "happy," and "very happy," while the three categories of financial satisfaction are "more or less satisfied," "not satisfied at all," and "pretty well satisfied." Looking at the data, we can see that families who reported being "pretty well satisfied" with their finances had the highest proportion of respondents who were "very happy," at 52.0%, and the lowest proportion of those who were "not too happy," at only 5.24%.
-On the other hand, families who reported being "not satisfied at all" with their finances had the highest proportion of respondents who were "not too happy," at 20.92%, and the lowest proportion of those who were "very happy," at only 22.5%.
+In Table 6, which appears suggests that families with 0 babies have the highest percentages of financial satisfaction across all categories.
+As the number of babies in a family increases, the proportion of families in each financial satisfaction category generally decreases.
+Families with 4 babies have the lowest percentages in all financial satisfaction categories.Notably, the "pretty well satisfied" category shows the steepest decline in percentages as the number of babies increases.Families with 0 babies in this category have the highest percentage of financial satisfaction at 85.47%, while families with 4 babies have the lowest percentage at 0.05%.
 
 ```{r}
-#| eval: true
+#| message: false
+#| echo: false
 #| warning: false    
-#| echo: false
-#| label: table-four
-#| table-cap: Table of Financial Satisfaction and Happiness in the Family
+finance_happy_table <- data %>%
+  group_by(finance_satified, babies) %>%
+  summarize(response = n(), variance = var(as.numeric(babies))) %>%
+  mutate(percent = round(response / sum(response) * 100, 2)) %>%
+  select(finance_satified, babies, percent) %>%
+  spread(babies, percent)
 
-finance_happy_table <- data %>%
-  group_by(finance_satified, happy) %>%
-  summarize(response = n(), variance = var(as.numeric(happy))) %>%
-  mutate(percent = round(response / sum(response) * 100, 2)) %>%
-  select(finance_satified, happy, percent) %>%
-  spread(happy, percent)
-
-kable(finance_happy_table, caption = "Table of Financial Satisfaction and Happiness in the Family") %>%
-  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
-
-```
-
-In table five, which appears to be presenting data on the relationship between divorce and happiness levels in families, based on some measure or criteria.
-The three categories of happiness levels are "not too happy," "happy," and "very happy," while the two categories of divorce are "no" and "yes." Looking at the data, we can see that there are only small differences in the proportions of families who reported being "happy" or "not too happy" depending on whether or not they had experienced divorce.
-Specifically, families who reported "no" to divorce had a slightly higher proportion of respondents who were "very happy," at 38.61%, compared to those who reported "yes" to divorce, at 36.24%.
-However, families who reported "yes" to divorce had a slightly higher proportion of respondents who were "not too happy," at 11.53%, compared to those who reported "no" to divorce, at 9.29%.
-
-```{r}
-#| eval: true
-#| warning: false
-#| echo: false
-#| label: table-five
-#| table-cap: Table of Divorce and Happiness in the Family
-divorce_happy_table <- data %>%
-  group_by(divorce, happy) %>%
-  summarize(response = n(), variance = var(as.numeric(happy))) %>%
-  mutate(percent = round(response / sum(response) * 100, 2)) %>%
-  select(divorce, happy, percent) %>%
-  spread(happy, percent)
-
-kable(divorce_happy_table, caption = "Table of Divorce and Happiness in the Family") %>%
-  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
-
-```
-
-In table six, which appears to be presenting data on the relationship between educational attainment and happiness levels in families, based on some measure or criteria.
-The three categories of happiness levels are "not too happy," "happy," and "very happy," while the categories of educational attainment are "associate/junior college," "bachelor's," "graduate," "high school," and "less than high school." Looking at the data, we can see that families with different levels of educational attainment generally reported similar levels of happiness.
-The proportions of respondents who reported being "very happy" were similar across all levels of educational attainment, ranging from 41.24% for those with an associate/junior college degree to 44.28% for those with a graduate degree.
-The proportions of respondents who reported being "not too happy" were also similar across all levels of educational attainment, ranging from 5.26% for those with a graduate degree to 14.96% for those with less than a high school education.
-
-```{r}
-#| eval: true
-#| warning: false
-#| echo: false
-#| label: table-six
-#| table-cap: Table of Degree and Happiness in the Family
-degree_happy_table <- data %>%
-  group_by(degree, happy) %>%
-  summarize(response = n(), variance = var(as.numeric(happy))) %>%
-  mutate(percent = round(response / sum(response) * 100, 2)) %>%
-  select(degree, happy, percent) %>%
-  spread(happy, percent)
-
-kable(degree_happy_table, caption = "Table of Degree and Happiness in the Family") %>%
+kable(finance_happy_table, caption = "Table of Financial Satisfaction and Number of babies") %>%
   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
@@
 
-The analysis of the General Social Survey data-set from 1972 provides insights into various aspects of individuals' lives in the United States during that time period.
-The results suggest that several variables, such as financial satisfaction, self-reported health status, and level of education, have a positive relationship with individuals' level of happiness.Regarding family dynamics, the analysis indicates that individuals with no children reported the highest levels of happiness, although the data set's limitations require further exploration of the proportion of individuals with different numbers of children.
-Being divorced may have a slight impact on one's level of happiness in life, with a small proportion of individuals feeling "not too happy" compared to married individuals.
+In conclusion, the analysis of the data presented in [@fig-one] through [@fig-six] reveals several key findings related to the number of children in a family and its association with happiness, health, and financial satisfaction.
+Overall, families with no children report the highest levels of happiness, but this result could be influenced by the larger sample size of childless families.
+The sex distribution data indicates a higher percentage of females in families with more children, with the most significant differences observed in families with one and four children.
 
-Furthermore, the analysis suggests that individuals' self-rated health status has a positive relationship with their self-rated level of happiness.
-The higher the participants' self-rated health, the higher their self-rated level of satisfaction with life.
-Similarly, there is a positive relationship between people's satisfaction with their current financial situation and their level of happiness in life.
-The higher people's satisfaction with their finances, the higher their level of happiness.The analysis suggests that there is a certain relationship between people's level of education and their level of happiness in life.
-The proportion of people who feel "not too happy" is the highest among those with education levels lower than high school.
-However, the proportion of unhappy individuals is the lowest among those with bachelor's and graduate degrees, suggesting that as people's education level increases, their level of happiness also gradually increases.
+The analysis of health status shows that having one child is associated with the highest proportion of participants reporting 'excellent' health.
+The relationship between health and the number of children suggests that better health is generally associated with a higher likelihood of having one or more children, while poorer health correlates with a lower likelihood.Financial satisfaction also appears to be connected to the number of children in a family, with families with higher financial satisfaction generally having fewer children, while those with lower financial satisfaction have more children.
+This relationship may not be linear, and other factors could influence the number of children in a family.
 
-Overall, these findings provide valuable insights into the factors that may influence individuals' overall life satisfaction during the early 1970s in the United States.
-The results can be useful for researchers and students interested in exploring topics such as social stratification, gender roles, family dynamics, health disparities, and subjective well-being.
+It is important to acknowledge the limitations of this analysis, such as the potential influence of various confounding factors and the possibility of non-linear relationships between variables.
+Furthermore, the data may not be representative of all families or cultural contexts, so the findings should be interpreted with caution.
+Nevertheless, this study provides valuable insights into the complex relationships between family size and factors such as happiness, health, and financial satisfaction.
+Future research could explore these relationships in greater depth, considering additional variables, longitudinal data, and diverse populations to provide a more comprehensive understanding of the factors influencing family size and well-being.
 
@@
 The study's findings on the positive relationship between financial satisfaction, health, and happiness underscore the importance of financial stability and access to healthcare for overall well-being.
-These findings have important implications for policymakers and practitioners working to improve individuals' quality of life [@c] .
+These findings have important implications for policymakers and practitioners working to improve individuals' quality of life[@d].
 For example, policies aimed at increasing access to affordable healthcare and financial assistance programs can help individuals improve their financial stability and access to essential services, ultimately contributing to overall well-being.
 
-The study's results also suggest that education is an important factor in individuals' overall well-being and happiness.
+The study's results also suggest that education is an important factor in individuals' overall well-being and happiness[@e].
 As people's education level increases, their level of happiness also gradually increases.
-This highlights the need for policies and programs that support educational attainment, particularly for disadvantaged populations [@d].
-Such programs can include initiatives to improve access to education and financial aid for those who may face barriers to education.
+This highlights the need for policies and programs that support educational attainment, particularly for disadvantaged populations.
+Such programs can include initiatives to improve access to education and financial aid for those who may face barriers to education [@f].
 
@@
 
-## Impact of divorce on individuals' happiness
-
-Divorce is a significant life event that can have profound effects on an individual's overall well-being and happiness.
-The findings of this study suggest that individuals who have experienced divorce may have lower levels of happiness than those who are married or have never been married.
-This could be due to a range of factors, including the loss of social support and economic stability that often accompanies divorce [@o].
-
-One possible explanation for the association between divorce and happiness is the impact of social support.
-Marriage provides a source of emotional support, and individuals who divorce may experience a loss of this support network.
-Furthermore, divorce can result in the breakdown of extended family relationships, reducing the availability of social support.
-This loss of social support could contribute to lower levels of happiness and well-being.
-Economic factors may also play a role in the relationship between divorce and happiness [@e].
-Divorce can result in significant financial upheaval, particularly for individuals who were financially dependent on their partner.
-This financial instability could contribute to lower levels of happiness and well-being, as financial stress can be a significant source of anxiety and depression.
-
-Further research could explore the reasons behind the association between divorce and happiness.
-Qualitative studies could be conducted to explore the experiences of individuals who have gone through divorce and how this event has affected their well-being.
-Longitudinal studies could also be conducted to examine changes in individuals' happiness levels before and after a divorce[@f].
-
-Overall, the findings of this study highlight the importance of considering the impact of divorce on individuals' well-being and happiness.
-Policies and interventions aimed at supporting individuals going through divorce, such as access to counseling and financial support, could help to mitigate the negative effects of this life event and improve individuals' overall well-being.
-
 ## The importance of historical context in understanding well-being
@@
 The historical context of the early 1970s in the United States is essential in understanding individuals' well-being during that period.
-Societal norms, values, and attitudes during this time were different from those of today, and these differences could have influenced individuals' well-being.
+Societal norms, values, and attitudes during this time were different from those of today, and these differences could have influenced individuals' well-being [@g].
 These social movements may have influenced individuals' attitudes towards social stratification, gender roles, and family dynamics, which, in turn, could have affected their well-being.
 
-Understanding the historical context is also essential in developing interventions that can address the unique challenges faced by individuals during a particular period in time [@g].
+Understanding the historical context is also essential in developing interventions that can address the unique challenges faced by individuals during a particular period in time [@h].
 For example, the economic conditions during the early 1970s, such as high inflation and high unemployment rates, could have affected individuals' financial stability and, ultimately, their well-being.
@@
 
-Furthermore, the study's findings can be compared to more recent data to examine changes in the relationships between different factors and well-being over time [@h].
+Furthermore, the study's findings can be compared to more recent data to examine changes in the relationships between different factors and well-being over time[@i].
 For example, the impact of divorce on well-being may have changed over time, as societal attitudes towards divorce have shifted.
@@
 
-## Impact of Financial Stability on Happiness
+## Relationship between Family Size, Happiness, Health, and Gender Distribution
 
-As the analysis of the GSS dataset shows, there is a positive correlation between individuals' satisfaction with their financial situation and overall well-being, an important finding.
-This correlation underscores the importance of U.S.
-financial stability in determining a person's happiness in the early 1970s.
-In this discussion, we will further explore the impact of these factors on individual well-being during that time.
+The analysis of the data presented in [@fig-one] and [@fig-five] suggests a relationship between the number of children in a family and the overall happiness and health status of individuals.
+Families with no children seem to have the highest proportion of 'very happy', 'pretty happy', and 'not too happy' responses, although this could be influenced by the larger amount of data collected for childless individuals.
+Furthermore, families with 'excellent' health tend to have a more balanced distribution of children, with a higher likelihood of having one or more children compared to families with poorer health.
 
-In the early 1970s, the United States was going through a period of economic turmoil.
-One of the most important factors is the rapid rise in inflation.
-The country faces a phenomenon known as "stagflation," which is characterized by a stagnant economy, high inflation, and high unemployment.
-This unusual economic situation is largely attributable to the 1973 oil crisis, which caused a spike in oil prices and disrupted the global economy [@i].
-The rise in inflation during this period has a direct impact on individuals' financial satisfaction.
-As the cost of goods and services increases, people find it a challenge to maintain their previous standard of living [@j].
-This is further exacerbated by high unemployment, as many people struggle to find stable employment.Analysis of the GSS dataset highlights the importance of financial stability in determining individual well-being, emphasizing the need for effective economic policies to ensure the financial security and well-being of populations.
+In addition to the relationship between family size and happiness, as well as family size and health, the analysis of data in [@fig-two] also indicates a connection between family size and gender distribution.
+The data suggests that the sex distribution varies depending on the number of babies in the family, with a higher percentage of females compared to males observed across all groups.
+As the number of babies in a family increases, the percentage of females also increases, with the highest difference observed in families with one and four babies.
+In these groups, the sex distribution is more skewed towards females.
+This finding suggests that the presence and number of babies in a family may also influence the gender composition of the family.
 
-## The Role of Education in Happiness
+The data from [@fig-three] and [@fig-four] further supports the relationship between family size, happiness, and health.
+The analysis of the number of children had each year from 1972 to 2012 in relation to the level of happiness shows fluctuations in the proportion of individuals who reported feeling "not too happy" and "happy" over the years.
+This finding highlights the potential influence of sociocultural and economic factors on happiness and family size over time.
 
-The study found that as an individual's education level increased, their level of happiness also gradually increased.
-This finding prompts a discussion on the role of education in determining one's overall happiness and well-being during the early 1970s.
-It would be interesting to explore the potential reasons behind this correlation, such as the opportunities for personal development, improved employment prospects, and social mobility that education provides[@k].
-Moreover, examining the accessibility and quality of education during that period could offer further insights into the impact of education on happiness.
-By understanding the role of education in shaping individuals' happiness, researchers and policymakers can better appreciate the significance of investing in education and ensuring equal access to quality education for all.One possible explanation is that education provides individuals with the tools and resources they need to achieve personal goals and fulfill their potential[@l].
-Education can help individuals develop a sense of purpose, autonomy, and mastery, which are important factors in promoting happiness and well-being.
-In addition, education can provide individuals with the skills and knowledge needed to pursue meaningful and fulfilling careers, which can also contribute to their overall sense of well-being.
+Additionally, the data from [@fig-four] reveals that having one child is associated with the highest proportion of participants reporting 'excellent' health status.
+This finding might suggest that having a smaller family size could be related to better health outcomes for individuals.
+However, it is crucial to consider other factors that could potentially influence the health status of individuals, such as access to healthcare, lifestyle choices, and overall well-being.
 
-Moreover, education can provide opportunities for social mobility, which can enhance individuals' sense of self-worth and life satisfaction.
-Education can help individuals acquire the social and cultural capital necessary to succeed in their professional and personal lives, which can lead to increased opportunities and social status [@m].
-This, in turn, can contribute to individuals' overall sense of happiness and well-being.However, it is important to note that not all forms of education may have the same impact on individuals' happiness and well-being.
-The accessibility and quality of education are crucial factors that can influence the extent to which education promotes happiness and well-being.
-For example, individuals who have access to high-quality education may experience greater benefits in terms of personal development, employment prospects, and social mobility than those who do not have access to such education [@n].
+In summary, the relationship between family size and happiness, health, and gender distribution is complex and multifaceted.
+While the data suggests certain trends and connections, it is important to recognize that other factors may also play a role in determining happiness, health, and gender distribution in families with varying numbers of children.
+Further research and analysis are needed to better understand these relationships and to identify potential contributing factors.
 
-Therefore, policymakers and educators must work to ensure that all individuals have equal access to high-quality education.
-Investing in education can not only promote individuals' personal and professional growth but also contribute to the overall well-being and happiness of society as a whole.
-By understanding the role of education in shaping individuals' happiness, we can work towards building a more just and equitable society.
+## Impact of Family Size on Financial Satisfaction
+
+The data from [@fig-six] reveals a connection between financial satisfaction and the number of children in a family.
+In general, families with higher financial satisfaction tend to have fewer children, while those with lower financial satisfaction have more children.
+This trend is observed across all three financial satisfaction levels, with the majority of families in all financial satisfaction levels having 0 babies.
+As the number of children increases, the percentages for all three financial satisfaction categories tend to decrease, suggesting that family size may play a role in financial satisfaction.
+However, it is important to note that this relationship may not be linear and that other factors could also influence the number of children in a family and their financial satisfaction.
 
@@
 
--   The data-set used in the study is small, consisting of only 5 observations and 10 variables, which may limit the generalization of the findings.
--   The study only examines data from the year 1972, which may not be representative of individuals' lives in the United States today or even in the 1970s as a whole.
--   The study only uses graphical representation to analyze the relationships between variables, which may not provide a comprehensive understanding of the complex relationships between variables.
--   The study only examines a limited set of variables and does not consider other factors that could impact individuals' level of happiness and well-being, such as social support, employment status, and cultural factors.
+-   Sample representation: The data used in this analysis may not be representative of all families or cultural contexts, which could limit the generalization of the findings.
+Further research with more diverse samples is needed to ensure the results are applicable across different populations.
+-   Confounding factors: The analysis does not account for potential confounding factors that might influence the relationships between the number of children, happiness, health, and financial satisfaction.
+Factors such as age, education, income, and cultural background could play a role in the observed patterns and should be considered in future research.
+-   Cross-sectional data: The data used in this analysis is cross-sectional, which makes it challenging to establish causal relationships between variables.
+Longitudinal data would allow for a more in-depth understanding of how the variables change over time and their potential causal relationships.
+-   Non-linear relationships: The relationships between the variables in this study may not be linear, and other forms of relationships could exist.
+The analysis could be extended by exploring different types of relationships between variables, such as quadratic or cubic functions.
 
@@
 
--   Further research could expand the data-set to include more observations and variables, which could provide a more comprehensive understanding of individuals' lives during the early 1970s in the United States.
--   Future studies could examine more recent data from the GSS to investigate changes in the relationships between variables over time.
--   Future studies could use more advanced statistical methods to analyze the relationships between variables, such as regression analysis, to provide a more robust understanding of the relationships between variables.
--   Future studies could consider other factors that may impact individuals' level of happiness and well-being, such as social support, employment status, and cultural factors.
+-   Diversify the sample: Conduct further research with more diverse samples, including participants from different cultural backgrounds, age groups, and socioeconomic statuses, to better understand the relationships between the number of children, happiness, health, and financial satisfaction across various populations.
+-   Consider potential confounding factors: Future research should consider potential confounding factors that might influence the relationships between variables.
+By controlling for these factors, the analysis would provide a clearer understanding of the true relationships between the number of children and happiness, health, and financial satisfaction.
+-   Longitudinal data analysis: Collect and analyze longitudinal data to establish causal relationships between variables and observe how these relationships change over time.
+This approach would provide a more comprehensive understanding of the factors influencing family size and well-being.
+-   Explore non-linear relationships: Expand the analysis to consider non-linear relationships between the variables in the study.
+By exploring different types of relationships, the research could provide a more nuanced understanding of how the number of children, happiness, health, and financial satisfaction are interconnected.
+-   Investigate additional variables: Consider other variables that might influence family size and well-being, such as parenting styles, social support networks, and access to childcare.
+Incorporating these additional variables in the analysis could provide a more holistic understanding of the factors that contribute to family well-being.
 
@@
 
-### 5. Have you ever been divorced?
-
-a.  Yes
-b.  No
-
-### 6. What is your current living area?
-
-a.  Large city
-b.  Small city
-c.  Suburban
-d.  Rural
-
-### 7. What is your age? (Please enter a number)
-
-### 8. What is your biological sex?
+### 5. What is your biological sex?
 
@@
 
-### 9. What is the highest level of education you have completed?
-
-a.  Less than high school
-b.  High school or equivalent
-c.  Some college or associate degree
-d.  Bachelor's degree
-e.  Graduate or professional degree
-
-### 10. How would you rate your overall level of well-being?
+### 6 How would you rate your overall level of well-being?
 

### 2023-04-04 scripts/02-data_cleaning.R

@@ -1,0 +1,118 @@
+#### Preamble ####
+# Purpose: The purpose of the final line write_csv(data, "inputs/data/cleaned_data.csv") is to save the 
+#cleaned and transformed data into a CSV file named "cleaned_data.csv" in the directory "inputs/data". 
+#This line is saving the cleaned data as a CSV file so that it can be easily loaded and used in future 
+#analysis or modeling.This is a good practice because it ensures that the cleaned data can be easily accessed
+#and used later on without having to repeat the cleaning and transformation process every time. It also allows 
+#for easier sharing of the cleaned data with others who may need to use it.
+# Author: SHAOHAN CHANG  
+# Data: 14 March 2023 
+# Contact: SHAOHAN.CHANG@utoronto.ca 
+# License: MIT
+# Pre-requisites:
+## 1. Go to the GSS website by entering https://gss.norc.org/get-the-data/stata into your web browser.
+## 2.Scroll down the page until you find the "Stata Data" section, and then click on the "Download the GSS Stata data files" link.
+## 3. Select the years of interest from the list provided, and if you need to download multiple years, hold down the "Ctrl" key while clicking to select each year.
+## 4. Click the "Download Selected Files" button located at the bottom of the page. 
+## 5. On the next page, select the "Stata" file format.
+## 6. To download all variables, choose "ALL" from the drop-down menu next to the green "ALL" button.
+## 7. Click the "Create File" button and wait for the file to be generated. This may take a few moments, depending on the size of the file and your internet connection.
+## 8. Once the file has been created, click the "Download File" button to save it to your computer. Make sure to save the file in a location where you can easily find it later.
+
+# Any other information needed?
+## 1. Take note of the file path where the downloaded data file is saved on your computer, as this information is necessary to read the data into R.
+## 2. Keep in mind that the GSS data file can be quite large, especially if you have downloaded multiple years of data. To work with it more efficiently, consider filtering the data to a specific time period or a subset of variables using functions like subset() or dplyr::select().
+## 3. Because the downloaded data file is in Stata format, you'll need to use a package like "haven" or "foreign" to read the data into R. For example, you can use the haven::read_dta() function.
[…]

### 2023-04-05 outputs/paper/paper.qmd
Add files via upload

@@
 title: "Examining the Multifaceted Impact of Family Size on Happiness, Health, Gender Dynamics, and Financial Well-being"
-subtitle: ""
+subtitle: "A Cross-Sectional Cumulative Analysis of U.S. Microdata from 1972-2012"
 author: 
@@
 date-format: "D MMMM YYYY"
-abstract: "This study analyzed the relationship between family size, measured by the number of children, and various aspects of family life, such as happiness, health, and financial satisfaction.
+abstract: "This study explores the multifaceted impact of family size on happiness, health, gender dynamics, and financial well-being by analyzing cross-sectional cumulative microdata from the United States between 1972 and 2012.
+This study analyzed the relationship between family size, measured by the number of children, and various aspects of family life, such as happiness, health, and financial satisfaction.
 The findings suggest that happiness levels are highest among childless individuals, while families with one child report the best health status.
@@
 
-The impact of the number of children in a family on various aspects of family life has been a topic of interest for researchers and policymakers alike [@a].
+This research investigates the diverse effects of family size on various aspects such as happiness, health, gender roles, and financial stability.
+The study employs cross-sectional cumulative microdata from the United States spanning from 1972 to 2012.The impact of the number of children in a family on various aspects of family life has been a topic of interest for researchers and policymakers alike [@a].
 Family size and structure play a crucial role in shaping the lives of individuals and communities.
@@
 In @tbl-var contains information on various personal and demographic characteristics of individuals, collected between the years 1972 and 2012.
-The data-set includes variables such as age, sex, number of babies, divorce status, self-reported health status, financial satisfaction and level of happiness.
-The data-set can be used to study the relationships between these variables and to gain insights into factors that may influence an individual's overall life satisfaction.
+The data-set comprises of 10 variables, namely age, sex, number of babies, divorce status, self-reported health status, financial satisfaction, level of happiness, and additional variables.
+The data-set contains 38,960 rows, providing ample opportunities to analyze the relationships between these variables and gain valuable insights into the factors that could potentially impact an individual's overall life satisfaction.
 
@@
 
-In [@fig-one],which analysis of this data is to calculate the number of children with 0, 1, 2, 3, 4.through the graph showing the relationship between the number of children and happiness in the family, it is obvious that when people have no children, the largest number of 'very happy', 'pretty happy', and 'not too happy' are shown.
-Although The preliminary judgment is that the number of people who are happy without children is the largest.
-But among the data, the data collected without children is the most.
-In order to ensure the accuracy of the data, it is necessary to further analyze the proportion of the number of children in the family for the next part of the analysis.
+In [@fig-one],which analysis explores the relationship between the number of children in a family and happiness levels, categorized as 'very happy,' 'pretty happy,' and 'not too happy.' Although childless families show the highest numbers in each happiness category, the data collected for such families is more abundant, necessitating an analysis of happiness proportions within each family size.
+The findings reveal no linear correlation between the number of children and overall family happiness, with happiness varying across family sizes without a consistent pattern.
+The non-uniform distribution of happiness categories among families with different numbers of children implies that factors beyond the number of children also contribute to happiness levels.
+In conclusion, the data shows variations in happiness levels among families of different sizes but does not establish a definitive correlation between the number of children and overall family happiness.
+Further research is needed to better understand the complex factors influencing happiness within families.
 
@@
 
-In [@fig-four], the analysis of the chart, it can be observed that when individuals have one child, there is a significantly higher proportion of participants who rate their health as 'good' or 'excellent' compared to other categories.
+In [@fig-four], which observed that when individuals have one child, there is a significantly higher proportion of participants who rate their health as 'good' or 'excellent' compared to other categories.
 In contrast, for participants who do not have any children, the proportion of those who rate their health as 'poor' is the highest, but no clear conclusion can be drawn from this finding.
@@
 $$
-\hat{Y}=\hat{\beta_0}+\hat{\beta_1}X_{finance-score}+\hat{\beta_2}X_{health-score} + \hat{\beta_3}X_{happy} + 
+\hat{Y}=\hat{\beta_0} + \hat{\beta_1}X_{finance-score} + \hat{\beta_2}X_{health-score} + \hat{\beta_3}X_{happy} + 
 \hat{\beta_6}X_{babies-number} 
@@
 
--   ${\hat{Y}}$ is predicted value of the dependent variable. This is the outcome we're trying to predict or estimate based on the independent variables.
--   ${\hat{\beta_0}}$ : The intercept term, which represents the expected value of ${\hat{Y}}$ when all independent variables are equal to 0.
--   ${\hat{\beta_1}}$ , ${\hat{\beta_2}}$ , ${\hat{\beta_3}}$ are the estimated coefficients for each independent variable.
-These coefficients indicate the average change in the dependent variable ${\hat{Y}}$ associated with a one-unit change in the corresponding independent variable, holding all other variables constant.
+-   $\hat{Y}$ is predicted value of the dependent variable. This is the outcome we're trying to predict or estimate based on the independent variables.
+-   $\hat{\beta_0}$ : The intercept term, which represents the expected value of $\hat{Y}$ when all independent variables are equal to 0.
+-   $\hat{\beta_1}$ , $\hat{\beta_2}$ , $\hat{\beta_3}$ are the estimated coefficients for each independent variable.
+These coefficients indicate the average change in the dependent variable $\hat{Y}$ associated with a one-unit change in the corresponding independent variable, holding all other variables constant.
 The independent variables are:
@@
 
-In the Table 3 ,which presented in the table indicate that the sex distribution varies depending on the number of babies in the family.Across all groups, there is a consistent pattern of a higher percentage of females compared to males.
-The lowest difference in sex distribution is observed among families with no babies, where the female-to-male ratio is relatively closer (54.53% female vs.
-45.47% male).
+In the @tbl-sex, which presented in the table indicate that the sex distribution varies depending on the number of babies in the family.Across all groups, there is a consistent pattern of a higher percentage of females compared to males.
+The lowest difference in sex distribution is observed among families with no babies, where the female-to-male ratio is relatively closer 54.53% female vs.
+45.47% male.
 As the number of babies in a family increases, the percentage of females also increases, with the highest difference observed in families with 1 and 4 babies.
@@
 ```{r}
-#| message: false
+#| label: tbl-sex
+#| tbl-cap: Relationship between Number of Children and Gender
 #| echo: false
 #| warning: false
-
 sex_table <- data %>% 
@@
 
-kable(sex_table, caption = "Relationship between Number of Children and Gender") %>%
+kable(sex_table  ) %>%
   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
@@
 
-In the Table 4, which suggests that families with 4 babies have the highest proportion of "happy" individuals at 63.41%.
+In the @tbl-happ, which suggests that families with 4 babies have the highest proportion of "happy" individuals at 63.41%.
 In contrast, families with 3 babies have the highest proportion of "not too happy" individuals at 16.57% and the lowest proportion of "happy" individuals at 50.30%.
@@
 ```{r}
+#| label: tbl-happ
+#| tbl-cap: Happiness Levels Across Families with number of Babies
 #| message: false
@@
 
-kable(happy_table, caption = "Happiness Levels Across Families with number of Babies") %>%
+kable(happy_table) %>%
   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
@@
 
-In Table 5, which appears suggests that individuals without any babies tend to have higher percentages in all health categories, especially in the "poor" health category (93.52%).
+In @tbl-heal, which appears suggests that individuals without any babies tend to have higher percentages in all health categories, especially in the "poor" health category (93.52%).
 As the number of babies in a family increases, the proportion of individuals in the "excellent," "fair," and "good" health categories generally decreases.
@@
 ```{r}
+#| label: tbl-heal
+#| tbl-cap: Health Status with number of Babies
 #| message: false
@@
 
-kable(health_happy_table, caption = "Health Status with number of Babies") %>%
+kable(health_happy_table) %>%
   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
@@
 
-In Table 6, which appears suggests that families with 0 babies have the highest percentages of financial satisfaction across all categories.
+In @tbl-fin, which appears suggests that families with 0 babies have the highest percentages of financial satisfaction across all categories.
 As the number of babies in a family increases, the proportion of families in each financial satisfaction category generally decreases.
@@
 ```{r}
+#| label: tbl-fin
+#| tbl-cap: Table of Financial Satisfaction and Number of babies
 #| message: false
@@
 
-kable(finance_happy_table, caption = "Table of Financial Satisfaction and Number of babies") %>%
+kable(finance_happy_table) %>%
   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
@@
 # Discussion
+
+## Role of gender distribution in family size and well-being
+
+The observation that families with more children have a higher percentage of females, particularly in families with one and four children, highlights the importance of examining the impact of gender distribution within families.
+In many societies, traditional gender roles dictate that women assume primary responsibilities for children, which could lead to a disproportionate burden on women in larger families.
+This unequal distribution of responsibilities might impact women's well-being, including their mental and physical health, career opportunities, and financial stability [@j].
+Moreover, the unequal distribution of resources within families due to gender biases could exacerbate these disparities, further impacting the well-being of women in larger families [@k].
+Additionally, societal expectations and norms surrounding gender roles may influence the decision-making process of couples when considering family size.
+For instance, cultural pressure to have more children or adhere to specific gender roles within a family might contribute to stress, relationship strain, and decreased well-being among family members [@l].
+
+To gain a more comprehensive understanding of the role of gender in family well-being, future research should examine how gender roles and expectations evolve as family size changes, as well as how these dynamics impact overall happiness, health, and financial satisfaction.
+This research could help inform policies and interventions that promote gender equity within families, ensuring that the well-being of all family members is considered and supported, regardless of family size.
 
@@
 For example, the economic conditions during the early 1970s, such as high inflation and high unemployment rates, could have affected individuals' financial stability and, ultimately, their well-being.
-Interventions that address these economic challenges may have had a significant impact on individuals' well-being during this period.
-
-Furthermore, the study's findings can be compared to more recent data to examine changes in the relationships between different factors and well-being over time[@i].
-For example, the impact of divorce on well-being may have changed over time, as societal attitudes towards divorce have shifted.
-Comparing the study's findings to more recent data can provide insights into how societal changes have influenced individuals' well-being over time.Overall, the historical context is essential in understanding individuals' well-being during a particular period in time.
-The study's focus on the early 1970s in the United States provides valuable insights into the factors that influenced individuals' well-being during that period.
-These findings can be used to develop interventions that address the unique challenges faced by individuals during a particular historical context, as well as to compare changes in the relationships between different factors and well-being over time.
+Interventions that address these economic challenges may have had a significant impact on individuals' well-being during this period[@i].
 
@@
 The analysis of the number of children had each year from 1972 to 2012 in relation to the level of happiness shows fluctuations in the proportion of individuals who reported feeling "not too happy" and "happy" over the years.
-This finding highlights the potential influence of sociocultural and economic factors on happiness and family size over time.
+This finding highlights the potential influence of horticultural and economic factors on happiness and family size over time.
 

### 2023-04-05 scripts/01-download_data.R

@@ -1,0 +1,9 @@
+# Explain how you download the data
+
+#The General Social Survey (GSS) is a comprehensive survey conducted in the United States since 1972 to 2012, 
+#providing insight into various social and demographic trends and attitudes. Accessing and analyzing the data 
+#requires downloading the data package from the GSS website and cleaning and processing the data to select relevant 
+#variables for the research question. This may involve dropping irrelevant variables, transforming or recording variables, 
+#and creating new variables. Once the data cleaning is complete, the selected variables can be analyzed using statistical software 
+#or other analytically tools to explore patterns and relationships. Despite being a valuable source of information, careful attention #
+#to data cleaning and analysis is crucial to ensure the validity and reliability of the findings.

### 2023-04-05 scripts/02-data_cleaning.R
Delete scripts directory

@@ -1,118 +1,0 @@
-#### Preamble ####
-# Purpose: The purpose of the final line write_csv(data, "inputs/data/cleaned_data.csv") is to save the 
-#cleaned and transformed data into a CSV file named "cleaned_data.csv" in the directory "inputs/data". 
-#This line is saving the cleaned data as a CSV file so that it can be easily loaded and used in future 
-#analysis or modeling.This is a good practice because it ensures that the cleaned data can be easily accessed
-#and used later on without having to repeat the cleaning and transformation process every time. It also allows 
-#for easier sharing of the cleaned data with others who may need to use it.
-# Author: SHAOHAN CHANG  
-# Data: 14 March 2023 
-# Contact: SHAOHAN.CHANG@utoronto.ca 
-# License: MIT
-# Pre-requisites:
-## 1. Go to the GSS website by entering https://gss.norc.org/get-the-data/stata into your web browser.
-## 2.Scroll down the page until you find the "Stata Data" section, and then click on the "Download the GSS Stata data files" link.
-## 3. Select the years of interest from the list provided, and if you need to download multiple years, hold down the "Ctrl" key while clicking to select each year.
-## 4. Click the "Download Selected Files" button located at the bottom of the page. 
-## 5. On the next page, select the "Stata" file format.
-## 6. To download all variables, choose "ALL" from the drop-down menu next to the green "ALL" button.
-## 7. Click the "Create File" button and wait for the file to be generated. This may take a few moments, depending on the size of the file and your internet connection.
-## 8. Once the file has been created, click the "Download File" button to save it to your computer. Make sure to save the file in a location where you can easily find it later.
-
-# Any other information needed?
-## 1. Take note of the file path where the downloaded data file is saved on your computer, as this information is necessary to read the data into R.
-## 2. Keep in mind that the GSS data file can be quite large, especially if you have downloaded multiple years of data. To work with it more efficiently, consider filtering the data to a specific time period or a subset of variables using functions like subset() or dplyr::select().
-## 3. Because the downloaded data file is in Stata format, you'll need to use a package like "haven" or "foreign" to read the data into R. For example, you can use the haven::read_dta() function.
[…]

### 2023-04-05 outputs/paper/paper.qmd
Add files via upload

@@
 This research investigates the diverse effects of family size on various aspects such as happiness, health, gender roles, and financial stability.
-The study employs cross-sectional cumulative microdata from the United States spanning from 1972 to 2012.The impact of the number of children in a family on various aspects of family life has been a topic of interest for researchers and policymakers alike [@a].
+The study employs cross-sectional cumulative micro data from the United States spanning from 1972 to 2012.The impact of the number of children in a family on various aspects of family life has been a topic of interest for researchers and policymakers alike [@a].
 Family size and structure play a crucial role in shaping the lives of individuals and communities.
@@
 data %>%
-  select(6:10) %>%
+  select(7:10) %>%
   slice(1:5) %>%

### 2023-04-05 scripts/02-data_cleaning.R
Delete scripts directory

@@ -1,115 +1,0 @@
-#### Preamble ####
-# Purpose: The purpose of the final line write_csv(data, "inputs/data/cleaned_data.csv") is to save the 
-#cleaned and transformed data into a CSV file named "cleaned_data.csv" in the directory "inputs/data". 
-#This line is saving the cleaned data as a CSV file so that it can be easily loaded and used in future 
-#analysis or modeling.This is a good practice because it ensures that the cleaned data can be easily accessed
-#and used later on without having to repeat the cleaning and transformation process every time. It also allows 
-#for easier sharing of the cleaned data with others who may need to use it.
-# Author: SHAOHAN CHANG  
-# Date: 14 March 2023 
-# Contact: SHAOHAN.CHANG@utoronto.ca 
-# License: MIT
-# Pre-requisites:
-## 1. Go to the GSS website by entering https://gss.norc.org/get-the-data/stata into your web browser.
-## 2.Scroll down the page until you find the "Stata Data" section, and then click on the "Download the GSS Stata data files" link.
-## 3. Select the years of interest from the list provided, and if you need to download multiple years, hold down the "Ctrl" key while clicking to select each year.
-## 4. Click the "Download Selected Files" button located at the bottom of the page. 
-## 5. On the next page, select the "Stata" file format.
-## 6. To download all variables, choose "ALL" from the drop-down menu next to the green "ALL" button.
-## 7. Click the "Create File" button and wait for the file to be generated. This may take a few moments, depending on the size of the file and your internet connection.
-## 8. Once the file has been created, click the "Download File" button to save it to your computer. Make sure to save the file in a location where you can easily find it later.
-
-# Any other information needed?
-## 1. Take note of the file path where the downloaded data file is saved on your computer, as this information is necessary to read the data into R.
-## 2. Keep in mind that the GSS data file can be quite large, especially if you have downloaded multiple years of data. To work with it more efficiently, consider filtering the data to a specific time period or a subset of variables using functions like subset() or dplyr::select().
-## 3. Because the downloaded data file is in Stata format, you'll need to use a package like "haven" or "foreign" to read the data into R. For example, you can use the haven::read_dta() function.
[…]

### 2023-04-05 scripts/01-download_data.R
Add files via upload

@@ -1,0 +1,32 @@
+
+#### Preamble ####
+# Purpose:The General Social Survey (GSS) is a comprehensive survey conducted in the United States since 1972 to 2012, 
+#providing insight into various social and demographic trends and attitudes. Accessing and analyzing the data 
+#requires downloading the data package from the GSS website and cleaning and processing the data to select relevant 
+#variables for the research question. This may involve dropping irrelevant variables, transforming or recording variables, 
+#and creating new variables. Once the data cleaning is complete, the selected variables can be analyzed using statistical software 
+#or other analytically tools to explore patterns and relationships. Despite being a valuable source of information, careful attention #
+#to data cleaning and analysis is crucial to ensure the validity and reliability of the findings.
+# Author: shaohan chang
+# Date: 4 April 2023
+# Contact: shaohan.chang@utoronto.ca
+# License: MIT
+# Pre-requisites: Download all the packages under the Work space section
+# Any other information needed? None
+
+
+#### Work space setup ####
+library(haven)
+library(tidyverse)
+
+#### Download data ####
+raw_data <- read_dta("inputs/data/gss7221_r3b.dta")
+
+raw_data <-
+  labelled::to_factor(raw_data)
+
+
+#### Save data ####
+# [...UPDATE THIS...]
+# change the_raw_data to whatever name you assigned when you downloaded it.
+write_csv(raw_data, "inputs/data/raw_data.csv") 

### 2023-04-05 scripts/02-data_cleaning.R

@@ -1,0 +1,115 @@
+#### Preamble ####
+# Purpose: The purpose of the final line write_csv(data, "inputs/data/cleaned_data.csv") is to save the 
+#cleaned and transformed data into a CSV file named "cleaned_data.csv" in the directory "inputs/data". 
+#This line is saving the cleaned data as a CSV file so that it can be easily loaded and used in future 
+#analysis or modeling.This is a good practice because it ensures that the cleaned data can be easily accessed
+#and used later on without having to repeat the cleaning and transformation process every time. It also allows 
+#for easier sharing of the cleaned data with others who may need to use it.
+# Author: SHAOHAN CHANG  
+# Date: 14 March 2023 
+# Contact: SHAOHAN.CHANG@utoronto.ca 
+# License: MIT
+# Pre-requisites:
+## 1. Go to the GSS website by entering https://gss.norc.org/get-the-data/stata into your web browser.
+## 2.Scroll down the page until you find the "Stata Data" section, and then click on the "Download the GSS Stata data files" link.
+## 3. Select the years of interest from the list provided, and if you need to download multiple years, hold down the "Ctrl" key while clicking to select each year.
+## 4. Click the "Download Selected Files" button located at the bottom of the page. 
+## 5. On the next page, select the "Stata" file format.
+## 6. To download all variables, choose "ALL" from the drop-down menu next to the green "ALL" button.
+## 7. Click the "Create File" button and wait for the file to be generated. This may take a few moments, depending on the size of the file and your internet connection.
+## 8. Once the file has been created, click the "Download File" button to save it to your computer. Make sure to save the file in a location where you can easily find it later.
+
+# Any other information needed?
+## 1. Take note of the file path where the downloaded data file is saved on your computer, as this information is necessary to read the data into R.
+## 2. Keep in mind that the GSS data file can be quite large, especially if you have downloaded multiple years of data. To work with it more efficiently, consider filtering the data to a specific time period or a subset of variables using functions like subset() or dplyr::select().
+## 3. Because the downloaded data file is in Stata format, you'll need to use a package like "haven" or "foreign" to read the data into R. For example, you can use the haven::read_dta() function.
[…]

### 2023-04-05 scripts/00-simulate_data.R
Delete scripts directory

@@ -1,40 +1,0 @@
-#### Preamble ####
-# Purpose: generate a simulated dataset with 100 observations, where each observation contains information 
-#about an individual's demographics, well-being, and satisfaction levels. The purpose of this simulated dataset 
-#is to explore relationships and trends among the variables, which can be useful for research, analysis, or practice
-#in understanding factors that may affect people's lives.
-# Author: shaohan chang
-# Date: 4 April 2023
-# Contact: shaohan.chang@utoronto.ca
-# License: MIT
-# Pre-requisites: Download package of tidyverse 
-# Any other information needed? None
-
-library(tidyverse)
-
-#### Simulate data ####
-set.seed(123) # set seed for reproducibility
-
-# generate 100 observations
-n <- 100
-
-# generate year variable (1972 to 2021)
-year <- sample(1972:2021, n, replace = TRUE)
-
-# generate sex variable
-sex <- sample(c("female", "male"), n, replace = TRUE)
-
-# generate babies variable (0 to 5)
-babies <- sample(0:5, n, replace = TRUE)
-
-# generate health variable
-health <- sample(c("excellent", "good", "fair", "poor"), n, replace = TRUE)
-
-# generate finance_satisfaction variable
-finance_satisfaction <- sample(c("not satisfied at all", "more or less satisfied", "pretty well satisfied"), n, replace = TRUE)
-
-# generate happiness variable
-happiness <- sample(c("not too happy", "happy", "very happy"), n, replace = TRUE)
-
-# create a data frame with the generated variables
-simulated_data <- data.frame(year, sex, babies, health, finance_satisfaction, happiness)

### 2023-04-05 scripts/01-download_data.R

@@ -1,32 +1,0 @@
-
-#### Preamble ####
-# Purpose:The General Social Survey (GSS) is a comprehensive survey conducted in the United States since 1972 to 2012, 
-#providing insight into various social and demographic trends and attitudes. Accessing and analyzing the data 
-#requires downloading the data package from the GSS website and cleaning and processing the data to select relevant 
-#variables for the research question. This may involve dropping irrelevant variables, transforming or recording variables, 
-#and creating new variables. Once the data cleaning is complete, the selected variables can be analyzed using statistical software 
-#or other analytically tools to explore patterns and relationships. Despite being a valuable source of information, careful attention #
-#to data cleaning and analysis is crucial to ensure the validity and reliability of the findings.
-# Author: shaohan chang
-# Date: 4 April 2023
-# Contact: shaohan.chang@utoronto.ca
-# License: MIT
-# Pre-requisites: Download all the packages under the Work space section
-# Any other information needed? None
-
-
-#### Work space setup ####
-library(haven)
-library(tidyverse)
-
-#### Download data ####
-raw_data <- read_dta("inputs/data/gss7221_r3b.dta")
-
-raw_data <-
-  labelled::to_factor(raw_data)
-
-
-#### Save data ####
-# [...UPDATE THIS...]
-# change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(raw_data, "inputs/data/raw_data.csv") 

### 2023-04-05 scripts/03-test_data.R
Add files via upload

@@ -1,0 +1,58 @@
+#### Preamble ####
+# Purpose: The purpose of these tests is to check for missing values (NA values) in different variables of the "cleaned_data.csv" dataset. 
+#These tests ensure that the data is clean and complete, and suitable for further analysis. Test One checks the entire dataset for any NA values, 
+#while Tests Two to Five specifically check for NA values in the "happy", "year", "sex", and "health" variables, respectively. The if else() function
+#is used to print a message indicating whether the check has passed or failed.
+# Author: SHAOHAN CHANG 
+# Date: 29 March 2023 
+# Contact: SHAOHAN.CHANG@Toronto.ca 
+# License: MIT
+# Pre-requisites: The prerequisite for running these tests is that the "cleaned_data.csv" dataset has been cleaned and prepared for analysis. The dataset 
+#should also be in a format that is compatible with the readr::read_csv() function used to read the data into R. Additionally, the R environment must be set
+#up with the necessary packages for performing data analysis, such as readr. Finally, the user should have a basic understanding of R programming and data 
+#analysis techniques, including how to write and run R scripts.
+
+#### Work space setup ####
+library(tidyverse)
+library(janitor)
+library(dplyr)
+
+
+#### Test data ####
+
+
+data <- 
+  readr::read_csv("inputs/data/cleaned_data.csv")
+
+# Test One : Check for NA values in the data frame.
+# Explanation : as the result , there 0 NA value. 
+
+check_result <- ifelse(sum(is.na(data)) == 0, "Check passed", "Check failed")
+print(check_result)
+
+
+# Test Two : Check for NA values in happy. 
+
+# Explanation :  Three are 0 missing values in the happy. 
+
+check_result <- ifelse(sum(is.na(data$happy)) == 0, "Check passed", "Check failed")
+print(check_result)
+
+
+# Test Three : Check for NA values in year.
+# Explanation :There are 0 missing values in the year variable. 
+
+check_result <- ifelse(sum(is.na(data$year)) == 0, "Check passed", "Check failed")
+print(check_result)
+
+# Test Four : Check for NA values in sex. 
+# Explanation :There are 0 missing values in the sex variable.
+
+check_result <- ifelse(sum(is.na(data$sex)) == 0, "Check passed", "Check failed")
+print(check_result)
+
+# Test Five : Check for NA values in health. 
+# Explanation :There are 0 missing values in the health variable.
+
+check_result <- ifelse(sum(is.na(data$degree)) == 0, "Check passed", "Check failed")
+print(check_result)

### 2023-04-06 outputs/paper/paper.qmd
Add files via upload

@@
 This research investigates the diverse effects of family size on various aspects such as happiness, health, gender roles, and financial stability.
-The study employs cross-sectional cumulative micro data from the United States spanning from 1972 to 2012.The impact of the number of children in a family on various aspects of family life has been a topic of interest for researchers and policymakers alike [@a].
+The impact of the number of children in a family on various aspects of family life has been a topic of interest for researchers and policymakers alike [@a].
 Family size and structure play a crucial role in shaping the lives of individuals and communities.
-Understanding the connections between the number of children and factors such as happiness, health, sex distribution, and financial satisfaction can help inform decisions and policies aimed at promoting family well being [@b].
-This paper seeks to explore these relationships and shed light on the complex interplay between family size and various aspects of family life.
+Understanding the connections between the number of children and factors such as happiness, health, sex distribution, and financial satisfaction can help inform decisions and policies aimed at promoting family well-being [@b].
 
-The paper examines the relationship between the number of children (0, 1, 2, 3, 4) in a family and different variables such as happiness, health, sex distribution, and financial satisfaction using multiple data sources.
+In this context, the objective of this study is to explore the complex interplay between family size and various aspects of family life.
+The study employs cross-sectional cumulative micro data from the United States spanning from 1972 to 2012.
+The paper aims to fill a gap in the existing literature by providing a comprehensive analysis of the relationship between the number of children in a family (0, 1, 2, 3, 4) and different variables such as happiness, health, sex distribution, and financial satisfaction, using multiple data sources.
 Previous research on this topic has often focused on specific aspects of family life or specific sub populations, leaving a gap in the understanding of the broader relationships between family size and different variables.
-This study aims to fill this gap by providing a comprehensive analysis of the relationship between the number of children in a family and various aspects of family life.
 
-Through the analysis of several charts and tables, this study uncovers patterns and trends in the data that suggest connections between the number of children in a family and the variables of interest.
+The methodology of the study includes the analysis of several charts and tables to uncover patterns and trends in the data, suggesting connections between the number of children in a family and the variables of interest.
 For example, the data reveals that families with better health tend to have a higher likelihood of having one or more children, while families with lower financial satisfaction tend to have more children [@c].
@@
 The structure of the paper is as follows: first, we present the data and methodology used in the study, followed by a detailed analysis of the relationships between the number of children in a family and the variables of interest.
-Next, we discuss the implications of the findings and their relevance to broader discussions on family well being and policy.
+Next, we discuss the implications of the findings and their relevance to broader discussions on family well-being and policy.
 Finally, we conclude with a summary of the main findings and suggestions for future research in this area.
 
-## Methodology
+# Methodology
 
-This study will combine data sources, including surveys and academic literature.
-The collected data will be analyzed to determine the trends and changes in public attitudes towards sexual morality over time (1972 to 2012).
-The study will also examine differences in attitudes between men and women, as well as work attitudes, and the relationship between education levels and happiness in daily life.
+The data used for this study was obtained from cross-sectional cumulative micro data from the United States, spanning from 1972 to 2012.
+Multiple data sources were utilized to ensure a comprehensive and representative sample of the US population.
+These data sources include the General Social Survey (GSS), such as happiness, health, gender roles, and financial stability.The sample for this study consists of families with different numbers of children (0, 1, 2, 3, 4).
+The final sample size was determined by considering the availability of data and the need for a balanced representation of different family sizes.
+The sample includes families from diverse socioeconomic backgrounds, ethnicities, and geographic locations in the United States, ensuring a comprehensive representation of the population.
 
@@
 
-After cleaning the data and selecting the main variables, the following table shows the first five rows of data and their corresponding parameters.The following data section provides a more detailed explanation of the selected variables for the data.
+The following table shows the first five rows of data and their corresponding parameters.The following data section provides a more detailed explanation of the selected variables for the data.
 
@@
 
+In this study, missing values (NA) have not been removed.
+The rationale behind this decision is that eliminating missing values from every column would lead to a significant reduction in the data set's size, compromising its representatives.
+Instead, R is employed to automatically filter out missing values, ensuring data integrity.
+
 ### Exploring the Connection Between Childlessness and Happiness
@@
 In regards to the variable "not too happy," the proportion of individuals who reported feeling unhappy was relatively high in 1974, 1985, 1993, 2004, 2006, and 2008.
-On the other hand, in regards to the variable "happy," the percentage of individuals reporting feeling happy was relatively high in 1973, 1977, 1994, 2006, and 2012.
+On the other hand, in regards to the variable "happy," the percentage of individuals reporting feeling happy was relatively high in 1973, 1977, 1994, 2006, and 2012.From the overall data, it can be seen that when people have 1 or 2 children, the most common self-rated health statuses are excellent, fair, and good.
 
@@
 
-data %>%
-  filter(babies != "unknown") %>%
-  group_by(year, babies, happy) %>%
-  summarize(n = n()) %>%
-  mutate(prop = n / sum(n)) %>%
-  ggplot(aes(x = factor(babies), y = prop, group = happy, color = happy)) +
-  geom_line(size = 1.5) +
-  stat_smooth(geom = "ribbon", alpha = 0.2) +
-  facet_wrap(~ year) +
-  scale_x_discrete(name = "Number of Babies", expand = c(0.1, 0.1)) +
-  scale_y_continuous(labels = scales::percent_format(), name = "Percentage", expand = c(0.05, 0)) +
-  scale_color_discrete(name = "Happiness") +
-  theme_minimal() +
-  theme(plot.title = element_text(size = 14, face = "bold", margin = margin(b = 10)),
-        plot.subtitle = element_text(size = 14, margin = margin(b = 20)),
-        axis.title = element_text(size = 12, face = "bold"),
-        axis.text = element_text(size = 10),
-        legend.title = element_text(size = 12, face = "bold"),
-        legend.text = element_text(size = 10),
-        legend.position = "bottom")
+ggplot(data[data$happy == "very happy", ], aes(x = year, y = factor(babies))) +
+  geom_point(position = position_jitter(width = 0.2, height = 0.1), size = 2, color = "#4daf4a") +
+  facet_wrap(~health, ncol = 5, scales = "free_y") +
+  labs(x = "Year", y = "Number of Babies") +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
+        panel.grid.major.x = element_line(color = "grey", size = 0.1),
+        strip.text = element_text(size = 10),
+        panel.spacing = unit(0.2, "lines"))
 
@@
 
-# summary
+# Results
+
+In conclusion, the analysis of the data presented in [@fig-one] through [@fig-six] reveals several key findings related to the number of children in a family and its association with happiness, health, and financial satisfaction.
+Overall, families with no children report the highest levels of happiness, but this result could be influenced by the larger sample size of childless families.
+The sex distribution data indicates a higher percentage of females in families with more children, with the most significant differences observed in families with one and four children.
+
+The analysis of health status shows that having one child is associated with the highest proportion of participants reporting 'excellent' health.
+The relationship between health and the number of children suggests that better health is generally associated with a higher likelihood of having one or more children, while poorer health correlates with a lower likelihood.Financial satisfaction also appears to be connected to the number of children in a family, with families with higher financial satisfaction generally having fewer children, while those with lower financial satisfaction have more children.
+This relationship may not be linear, and other factors could influence the number of children in a family.
+
+It is important to acknowledge the limitations of this analysis, such as the potential influence of various confounding factors and the possibility of non-linear relationships between variables.
+Furthermore, the data may not be representative of all families or cultural contexts, so the findings should be interpreted with caution.
+Nevertheless, this study provides valuable insights into the complex relationships between family size and factors such as happiness, health, and financial satisfaction.
+Future research could explore these relationships in greater depth, considering additional variables, longitudinal data, and diverse populations to provide a more comprehensive understanding of the factors influencing family size and well-being.
 
@@
 ```
-
-# Results
-
-In conclusion, the analysis of the data presented in [@fig-one] through [@fig-six] reveals several key findings related to the number of children in a family and its association with happiness, health, and financial satisfaction.
-Overall, families with no children report the highest levels of happiness, but this result could be influenced by the larger sample size of childless families.
-The sex distribution data indicates a higher percentage of females in families with more children, with the most significant differences observed in families with one and four children.
-
-The analysis of health status shows that having one child is associated with the highest proportion of participants reporting 'excellent' health.
-The relationship between health and the number of children suggests that better health is generally associated with a higher likelihood of having one or more children, while poorer health correlates with a lower likelihood.Financial satisfaction also appears to be connected to the number of children in a family, with families with higher financial satisfaction generally having fewer children, while those with lower financial satisfaction have more children.
-This relationship may not be linear, and other factors could influence the number of children in a family.
-
-It is important to acknowledge the limitations of this analysis, such as the potential influence of various confounding factors and the possibility of non-linear relationships between variables.
-Furthermore, the data may not be representative of all families or cultural contexts, so the findings should be interpreted with caution.
-Nevertheless, this study provides valuable insights into the complex relationships between family size and factors such as happiness, health, and financial satisfaction.
-Future research could explore these relationships in greater depth, considering additional variables, longitudinal data, and diverse populations to provide a more comprehensive understanding of the factors influencing family size and well-being.
 

### 2023-04-06 outputs/paper/paper.tex
Add files via upload

@@
 \usepackage{xcolor}
+\usepackage{siunitx}
+
+  \newcolumntype{d}{S[
+    input-open-uncertainty=,
+    input-close-uncertainty=,
+    parse-numbers = false,
+    table-align-text-pre=false,
+    table-align-text-post=false
+  ]}
+
 \KOMAoption{captions}{tableheading}
@@
 \hypersetup{
-  pdftitle={Exploring Relationships between Demographic Characteristics, Health, Finances, Living Arrangements, and Happiness: An Analysis of the General Social Survey (GSS) Data from 1972 to 2012},
+  pdftitle={Examining the Multifaceted Impact of Family Size on Happiness, Health, Gender Dynamics, and Financial Well-being},
   pdfauthor={SHAOHAN CHANG},
@@
 
-\title{Exploring Relationships between Demographic Characteristics,
-Health, Finances, Living Arrangements, and Happiness: An Analysis of the
-General Social Survey (GSS) Data from 1972 to 2012\thanks{Code and data
-are available at: https://github.com/lucas11333/Factor\_of\_Wellbeing}}
+\title{Examining the Multifaceted Impact of Family Size on Happiness,
+Health, Gender Dynamics, and Financial Well-being\thanks{Code and data
+are available at: https://github.com/lucas11333/Of\_Wellbeing}}
+\usepackage{etoolbox}
+\makeatletter
+\providecommand{\subtitle}[1]{% add subtitle to \maketitle
+  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
+}
+\makeatother
+\subtitle{A Cross-Sectional Cumulative Analysis of U.S. Microdata from
+1972-2012}
 \author{SHAOHAN CHANG}
-\date{28 March 2023}
+\date{6 April 2023}
 
@@
 \begin{abstract}
-This paper presents an analysis of a subset of the General Social Survey
-(GSS) data from the year 1972, which includes information on
-individuals' demographic characteristics, health, finances, living
-arrangements, and subjective well-being. The study aimed to explore
-various aspects of individuals' lives during the early 1970s in the
-United States, such as social stratification, gender roles, family
-dynamics, health disparities, and subjective well-being.The dataset
-consists of 5 observations and 10 variables, including year, age, sex,
-babies, divorce, health, finance\_satisfied, living\_area, and happy.
-The study used graphical representation to analyze the relationships
-between different variables in the dataset and individuals' level of
-happiness. The results of the analysis suggest that there is a positive
-relationship between people's satisfaction with their current financial
-situation, their self-rated health, and their level of happiness in
-life. Additionally, being divorced may have a slight impact on one's
-level of happiness in life, with a small proportion of individuals
-feeling not too happy. Moreover, the study found that people's level of
-education is positively associated with their level of happiness in
-life, as people's education level increases, their level of happiness
-also gradually increases.Overall, this study provides valuable insights
-into various aspects of individuals' lives during the early 1970s in the
-United States. The findings can be useful for researchers and students
-interested in exploring topics such as social stratification, gender
-roles, family dynamics, health disparities, and subjective well-being.
-The study highlights the importance of considering different factors
-that can influence individuals' level of happiness and well-being, such
-as their financial situation, health status, and level of education.
-Further research could investigate more recent data from the GSS to
-examine changes in these relationships over time.
+This study explores the multifaceted impact of family size on happiness,
+health, gender dynamics, and financial well-being by analyzing
+cross-sectional cumulative microdata from the United States between 1972
+and 2012. This study analyzed the relationship between family size,
+measured by the number of children, and various aspects of family life,
+such as happiness, health, and financial satisfaction. The findings
+suggest that happiness levels are highest among childless individuals,
+while families with one child report the best health status.
+Additionally, higher financial satisfaction is associated with fewer
+children in a family. These insights matter as they provide a better
+understanding of the factors influencing family size and the potential
+consequences of family planning decisions on overall wellbeing.
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, breakable, borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced, interior hidden, boxrule=0pt]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, breakable, frame hidden, boxrule=0pt, sharp corners]}{\end{tcolorbox}}\fi
 
@@
 
-Surveys are a common method for collecting data on individuals'
-attitudes, behaviors, and experiences in social science research. One
-such survey is the General Social Survey (GSS), which has been conducted
-in the United States since 1972 to 2012. This data set is a subset of
-the GSS data from the year 1972, which includes information on
-individuals' demographic characteristics, health, finances, living
-arrangements, and subjective well-being. While this is a relatively
-small data set, it provides a glimpse into the lives of individuals in
-the United States during a particular period in time.This paper aims to
-explore various aspects of individuals' lives during the early 1970s in
-the United States using the GSS data set. The variables in this data set
-are diverse and reflect a range of aspects of individuals' lives. For
-instance, the variables on babies and divorce provide information on
-individuals' family structures, while the variables on health and
-finance satisfaction offer insights into their well-being and financial
-stability (Vlaev 2014). The data set also includes variables on
-individuals' living arrangements and their subjective well-being,
-providing a glimpse into their social context and overall happiness.
-
-The paper presents a comprehensive analysis of the relationships between
-different variables in the data set and individuals' level of happiness.
-The analysis includes a graphical representation of the relationship
-between the number of children and happiness in the family, individuals'
-self-rated health and their self-rated level of happiness, people's
-satisfaction with their financial situation and their happiness, the
-level of happiness in life for individuals in two different states:
-divorced or married, and the relationship between people's level of
-education and their level of happiness in life.The results of the
-analysis suggest that there is a positive relationship between people's
-satisfaction with their current financial situation, their self-rated
-health, and their level of happiness in life (RSiahpush 2008). The
-analysis also indicates that being divorced may have a slight impact on
-one's level of happiness in life, with a small proportion of individuals
-feeling ``not too happy.'' Additionally, as people's education level
-increases, their level of happiness also gradually increases.
-
-Overall, this paper provides valuable insights into various aspects of
-individuals' lives during the early 1970s in the United States. The
-findings can be useful for researchers and students interested in
-exploring topics such as social stratification, gender roles, family
-dynamics, health disparities, and subjective well-being.
+This research investigates the diverse effects of family size on various
+aspects such as happiness, health, gender roles, and financial
+stability. The impact of the number of children in a family on various
+aspects of family life has been a topic of interest for researchers and
+policymakers alike (Brown 2010). Family size and structure play a
+crucial role in shaping the lives of individuals and communities.
+Understanding the connections between the number of children and factors
+such as happiness, health, sex distribution, and financial satisfaction
+can help inform decisions and policies aimed at promoting family
+well-being (Cheng 2011).
+
+In this context, the objective of this study is to explore the complex
+interplay between family size and various aspects of family life. The
+study employs cross-sectional cumulative micro data from the United
+States spanning from 1972 to 2012. The paper aims to fill a gap in the
+existing literature by providing a comprehensive analysis of the
+relationship between the number of children in a family (0, 1, 2, 3, 4)
+and different variables such as happiness, health, sex distribution, and
+financial satisfaction, using multiple data sources. Previous research
+on this topic has often focused on specific aspects of family life or
+specific sub populations, leaving a gap in the understanding of the
+broader relationships between family size and different variables.
+
+The methodology of the study includes the analysis of several charts and
+tables to uncover patterns and trends in the data, suggesting
+connections between the number of children in a family and the variables
+of interest. For example, the data reveals that families with better
+health tend to have a higher likelihood of having one or more children,
+while families with lower financial satisfaction tend to have more
+children (Waite 1995). However, the relationships identified in this
+study may not be linear, and it is important to consider the potential
+influence of other factors on the number of children in a family.
+
+The structure of the paper is as follows: first, we present the data and
+methodology used in the study, followed by a detailed analysis of the
+relationships between the number of children in a family and the
+variables of interest. Next, we discuss the implications of the findings
+and their relevance to broader discussions on family well-being and
+policy. Finally, we conclude with a summary of the main findings and
+suggestions for future research in this area.
 
 \hypertarget{methodology}{%
-\subsection{Methodology}\label{methodology}}
-
-This study will combine data sources, including surveys and academic
-literature. The collected data will be analyzed to determine the trends
-and changes in public attitudes towards sexual morality over time (1972
-to 2012). The study will also examine differences in attitudes between
-men and women, as well as work attitudes, and the relationship between
-education levels and happiness in daily life.
+\section{Methodology}\label{methodology}}
+
+The data used for this study was obtained from cross-sectional
+cumulative micro data from the United States, spanning from 1972 to
+2012. Multiple data sources were utilized to ensure a comprehensive and
+representative sample of the US population. These data sources include
+the General Social Survey (GSS), such as happiness, health, gender
+roles, and financial stability.The sample for this study consists of
+families with different numbers of children (0, 1, 2, 3, 4). The final
+sample size was determined by considering the availability of data and
+the need for a balanced representation of different family sizes. The
+sample includes families from diverse socioeconomic backgrounds,
+ethnicities, and geographic locations in the United States, ensuring a
+comprehensive representation of the population.
 
@@
 here (Müller 2020), haven (Wickham, Miller, and Smith 2022), ggplot
-(Wickham 2016) , kableExtra (Zhu 2021) to assist in data analysis, and
-the data from General Social Survey ({``GSS General Social Survey''}
-2023).
-
-\hypertarget{sec-data}{%
-\subsection{Data}\label{sec-data}}
-
-After cleaning the data and selecting the main variables, the following
-table shows the first five rows of data and their corresponding
-parameters.The following data section provides a more detailed
-explanation of the selected variables for the data.
-
-This data-set contains information on various personal and demographic
-characteristics of individuals, collected between the years 1972 and
-2012. The data-set includes variables such as age, sex, number of
-babies, divorce status, self-reported health status, financial
-satisfaction, living area, and level of happiness. The data-set can be
-used to study the relationships between these variables and to gain
-insights into factors that may influence an individual's overall life
+(Wickham 2016) , kableExtra (Zhu 2021) , model summary (Arel-Bundock
+2022) to assist in data analysis, and the data from General Social
+Survey ({``GSS General Social Survey''} 2023).
+
+\hypertarget{data}{%
+\subsection{Data}\label{data}}
+
+The following table shows the first five rows of data and their
+corresponding parameters.The following data section provides a more
+detailed explanation of the selected variables for the data.
+
+In Table~\ref{tbl-var} contains information on various personal and
+demographic characteristics of individuals, collected between the years
+1972 and 2012. The data-set comprises of 10 variables, namely age, sex,
+number of babies, divorce status, self-reported health status, financial
+satisfaction, level of happiness, and additional variables. The data-set
+contains 38,960 rows, providing ample opportunities to analyze the
+relationships between these variables and gain valuable insights into
+the factors that could potentially impact an individual's overall life
 satisfaction.
 
+\hypertarget{tbl-var}{}
 \begin{table}
-
-\caption{Table of Happy by Various Variables}
+\caption{\label{tbl-var}Report Data (First 5 rows) }\tabularnewline
+
 \centering
-\begin{tabular}[t]{r|l|l|l|l|l|l|l}
-\hline
-year & age & sex & babies & divorce & health & finance\_satified & living\_area\\
-\hline
-1972 & 70 & male & 0 & no & fair & more or less satisfied & large city\\
-\hline
-1972 & 48 & female & 0 & no & excellent & pretty well satisfied & large city\\
-\hline
-1972 & 27 & female & 0 & no & good & not satisfied at all & large city\\
-\hline
-1972 & 61 & female & 0 & no & good & pretty well satisfied & unknown\\
-\hline
-1972 & 30 & female & 2 & no & fair & not satisfied at all & unknown\\
+\begin{tabular}{r|l|r|l|l|l}
+\hline
+year & sex & babies & health & finance\_satified & happy\\
+\hline
+1972 & male & 2 & fair & pretty well satisfied & very happy\\
+\hline
+1972 & female & 1 & good & not satisfied at all & very happy\\
+\hline
+1972 & female & 1 & excellent & not satisfied at all & very happy\\
+\hline
+1972 & male & 1 & good & pretty well satisfied & very happy\\
+\hline
+1972 & male & 2 & excellent & more or less satisfied & not too happy\\
 \hline
@@
 \centering
-\begin{tabular}{l|l}
-\hline
-happy & degree\\
-\hline
-not too happy & less than high school\\
-\hline
-happy & high school\\
-\hline
-not too happy & bachelor's\\
-\hline
-happy & high school\\
-\hline
-happy & high school\\
+\begin{tabular}{r|r|r|r}
+\hline
+happy\_score & health\_score & finance\_score & babies\_number\\
+\hline
+3 & 2 & 3 & 2\\
+\hline
+3 & 3 & 4 & 1\\
+\hline
+3 & 4 & 4 & 1\\
+\hline
+3 & 3 & 3 & 1\\
+\hline
+0 & 4 & 2 & 2\\
 \hline
@@
   1972 to 2012.
-\item
-  age: This variable indicates the age of the individual at the time the
-  data was collected. It is a continuous variable measured in years.
 \item
@@
   4, or 5+.
-\item
-  divorce: This variable indicates whether or not the individual had
-  ever been divorced at the time the data was collected. It is a
-  categorical variable with two levels: yes and no.
 \item
@@
 \item
-  living\_area: This variable indicates the type of living area in which
-  the individual resided at the time the data was collected. It is a
-  categorical variable with different levels: large city, small city,
-  suburban, and rural.
-\item
   happy: This variable indicates the individual's level of happiness or
@@
   happy.
+\item
+  happy\_score: The happy\_score variable is an ordinal variable
+  representing the self-reported happiness levels of the individuals in
+  the dataset. It ranges from 0 to 3, with 0 representing ``not too
+  happy,'' 1 representing ``happy,'' 2 representing ``very happy,'' and
+  3 reserved for any unclassified or missing responses.
+\item
+  health\_score: The health\_score variable is an ordinal variable
+  indicating the self-reported health status of the individuals in the
+  dataset. It ranges from 1 to 4, with 1 denoting ``poor'' health, 2
+  signifying ``fair'' health, 3 representing ``good'' health, and 4
+  referring to ``excellent'' health. The value 5 is reserved for any
+  unclassified or missing responses.
+\item
+  finance\_score: This ordinal variable represents the financial
+  satisfaction level of the individuals in the dataset. It ranges from 1
+  to 3, with 1 indicating ``Not at all satisfied,'' 2 denoting ``more or
+  less satisfied,'' and 3 signifying ``pretty well satisfied.'' The
+  value 4 is reserved for any unclassified or missing responses.
+\item
+  babies\_number: The babies\_number variable is an ordinal variable
+  denoting the number of babies an individual in the dataset has. It
+  ranges from 0 to 4, where 0 represents ``0'' babies, 1 denotes ``1''
+  baby, 2 signifies ``2'' babies, 3 indicates ``3'' babies, and 4 refers
+  to ``4'' babies. The value 5 is reserved for any unclassified or
+  missing responses.
 \end{itemize}
 
-In Figure~\ref{fig-one}, this chart shows the number of people who are
-very happy, not too happy, and happy. Overall, the data indicates that
-the largest number of people are happy, with approximately 15,000
-individuals falling into this category. On the other hand, the smallest
-number of people are not too happy, with significantly fewer individuals
-in this category compared to the other two variables. In summary, the
-data suggests that the number of unhappy individuals is a relatively
-small group.
+In this study, missing values (NA) have not been removed. The rationale
+behind this decision is that eliminating missing values from every
+column would lead to a significant reduction in the data set's size,
+compromising its representatives. Instead, R is employed to
+automatically filter out missing values, ensuring data integrity.
+
+\hypertarget{exploring-the-connection-between-childlessness-and-happiness}{%
+\subsubsection{Exploring the Connection Between Childlessness and
+Happiness}\label{exploring-the-connection-between-childlessness-and-happiness}}
+
+In Figure~\ref{fig-one},which analysis explores the relationship between
+the number of children in a family and happiness levels, categorized as
+`very happy,' `pretty happy,' and `not too happy.' Although childless
+families show the highest numbers in each happiness category, the data
+collected for such families is more abundant, necessitating an analysis
+of happiness proportions within each family size. The findings reveal no
+linear correlation between the number of children and overall family
+happiness, with happiness varying across family sizes without a
+consistent pattern. The non-uniform distribution of happiness categories
+among families with different numbers of children implies that factors
+beyond the number of children also contribute to happiness levels. In
+conclusion, the data shows variations in happiness levels among families
+of different sizes but does not establish a definitive correlation
+between the number of children and overall family happiness. Further
+research is needed to better understand the complex factors influencing
+happiness within families.
 
@@
 
-\caption{\label{fig-one}Couning of Happiness}
+\caption{\label{fig-one}Relationship between Number of Babies and
+Happiness}
 
@@
 
-\hypertarget{baby}{%
-\subsubsection{Baby}\label{baby}}
-
-In Figure~\ref{fig-two}, through the graph showing the relationship
-between the number of children and happiness in the family, it is
-obvious that when people have no children, the largest number of `very
-happy', `pretty happy', and `not too happy' are shown. Although The
-preliminary judgment is that the number of people who are happy without
-children is the largest. But among the data, the data collected without
-children is the most. In order to ensure the accuracy of the data, it is
-necessary to further analyze the proportion of the number of children in
-the family for the next part of the analysis.
+In Figure~\ref{fig-two},which presented in the table indicates that the
+sex distribution varies depending on the number of babies in the family.
+A higher percentage of females compared to males is consistently
+observed across all groups. The lowest difference in sex distribution is
+found among families with no babies, where the female-to-male ratio is
+relatively closer. As the number of babies in a family increases, the
+percentage of females also increases, with the highest difference
+observed in families with one and four babies. In these groups, the sex
+distribution is more skewed towards females.
 
@@
 \caption{\label{fig-two}Relationship between Number of Babies and
-Happiness}
+Gender}
 
@@
 individuals reporting feeling happy was relatively high in 1973, 1977,
-1994, 2006, and 2012.
+1994, 2006, and 2012.From the overall data, it can be seen that when
+people have 1 or 2 children, the most common self-rated health statuses
+are excellent, fair, and good.
 
@@
 
-\hypertarget{health}{%
-\subsubsection{Health}\label{health}}
-
-In Figure~\ref{fig-four}, which represents the relationship between
-participants' self-rated health and their self-rated level of happiness.
-The chart shows that the proportion of participants who rated themselves
-as ``very happy'' was the highest among those who rated their health as
-``excellent''. On the other hand, the proportion of participants who
-rated themselves as ``not too happy'' was the lowest among those who
-rated their health as ``poor''.From the overall trend, it can be
-inferred that the higher the participants' self-rated health, the higher
-their self-rated level of satisfaction with life.
+\hypertarget{the-relationship-between-number-of-children-and-self-rated-health-status}{%
+\subsubsection{The Relationship Between Number of Children and
+Self-Rated Health
+Status}\label{the-relationship-between-number-of-children-and-self-rated-health-status}}
+
+In Figure~\ref{fig-four}, which observed that when individuals have one
+child, there is a significantly higher proportion of participants who
+rate their health as `good' or `excellent' compared to other categories.
+In contrast, for participants who do not have any children, the
+proportion of those who rate their health as `poor' is the highest, but
+no clear conclusion can be drawn from this finding. For individuals with
+three children, the feedback on their health status is evenly
+distributed among `good', `fair', and `excellent', with a very small
+proportion of participants reporting `poor' health. Overall, having one
+child is associated with the highest proportion of participants
+reporting `excellent' health status.
 
@@
 
-\caption{\label{fig-four}Relationship between Health and Happiness}
+\caption{\label{fig-four}Number of Children and Self-Rated Health
+Status}
 
@@
 
-In Figure~\ref{fig-five}, which spanning from 1970 to 2010, illustrates
-the relationship between participants' self-reported happiness levels
-and their health states. It is evident that when participants rated
-their health as `poor', the proportion of those who identified as `very
-happy' was notably lower compared to other health states. On the other
-hand, when participants reported their health as `excellent' or `good',
-the number of `very happy' responses regarding their life satisfaction
-increased significantly. In summary, this chart suggests a positive
-correlation between people's health and their happiness in life.
+In Figure~\ref{fig-five}, which present the dot plot, which represent
+the each number of babies in different condition of health, which
+explores the relationship between health and the number of babies in the
+family. The data is organized into four health categories - `excellent',
+`fair', `good', and `poor' - and five categories based on the number of
+babies, ranging from 0 to 4.The data reveals a pattern suggesting a
+connection between health status and the number of babies in a family.
+Families with `excellent' health have a more balanced distribution of
+babies, with a higher proportion of families having one or two babies
+compared to those with poorer health. This trend indicates that better
+health is associated with a higher likelihood of having one or more
+babies.As the number of babies increases, the percentages for all four
+health categories tend to decrease. This pattern is most noticeable in
+the `poor' health category, where the decline in percentages is more
+pronounced as the number of babies increases.In summary, the data
+suggests a relationship between health and the number of babies in a
+family. Better health is generally associated with a higher likelihood
+of having one or more babies, while poorer health tends to correlate
+with a lower likelihood. However, it is essential to consider that the
+relationship may not be linear and that other factors could also
+influence the number of babies in a family.
 
@@
 
-\caption{\label{fig-five}Relationship between Health and ``Very Happy''
-With Year}
+\caption{\label{fig-five}Relationship between Health and Number of
+Babies With Year}
 
@@
 
-\hypertarget{financial-satisfaction}{%
-\subsubsection{Financial Satisfaction}\label{financial-satisfaction}}
-
-In Figure~\ref{fig-six}, the graph depicts the relationship between
-people's satisfaction with their financial situation and their
-happiness.It is clear that when people are not very satisfied with their
-current finances, the proportion of unhappy people in their lives is the
-highest. On the other hand, when people are very satisfied with their
-finances, the proportion of happy people in their lives is the highest,
-and the proportion of unhappy people is also the lowest. Therefore, it
-can be concluded that there is a positive relationship between people's
-satisfaction with their current financial situation and their level of
-happiness in life.
+\hypertarget{the-association-between-family-size-and-financial-satisfaction}{%
+\subsubsection{The Association Between Family Size and Financial
+Satisfaction}\label{the-association-between-family-size-and-financial-satisfaction}}
+
+In Figure~\ref{fig-six}, which appears that the number of babies in a
+family is related to the level of financial satisfaction. In general,
+families with lower financial satisfaction, regardless of the category,
+tend to have a higher number of babies. This trend is observed across
+all three financial satisfaction levels.It is interesting to note that
+the majority of families in all financial satisfaction levels have 0
+babies. However, the percentage of families with 0 babies is notably
+higher in the `pretty well satisfied' category compared to the `more or
+less satisfied' and `not satisfied at all' categories.As the number of
+babies increases, the percentages for all three financial satisfaction
+categories tend to decrease. This pattern is more pronounced in the
+`pretty well satisfied' category, where the decline in percentages is
+steeper as the number of babies increases.In summary, the data suggests
+a connection between financial satisfaction and the number of babies in
+a family. Families with higher financial satisfaction generally have
+fewer babies, while those with lower financial satisfaction have more
+babies. It is essential to consider that this relationship may not be
+linear, and other factors could also influence the number of babies in a
+family.
 
@@
 
-\hypertarget{divorce}{%
-\subsubsection{Divorce}\label{divorce}}
-
-In Figure~\ref{fig-seven}, the graph represents the level of happiness
-in life for individuals in two different states: divorced or married.
-The graph shows that the levels of happiness in both marital states are
-almost similar. However, the proportion of people who feel ``not too
-happy'' in their lives is slightly higher among the divorced group than
-among the married group. In conclusion, being divorced may have a slight
-impact on one's level of happiness in life, with a small proportion of
-individuals feeling ``not too happy.''
-
-\begin{figure}
-
-{\centering \includegraphics{paper_files/figure-pdf/fig-seven-1.pdf}
-
-}
-
-\caption{\label{fig-seven}Relationship between Happiness and Divorce}
-
-\end{figure}
-
-In Figure~\ref{fig-eight}, which based on the analysis of the charts, it
-appears that for the years 1972, 1975, 1982, 1990, 1996, 2002, and 2010,
-individuals who reported being divorced also reported a higher
-percentage of happy responses. On the other hand, for the years 1976,
-1980, 1984, 1987, 1989, and 2006, individuals who reported being married
-reported a higher percentage of happy responses. Additionally, the
-percentage of individuals who reported ``not too happy'' was
-significantly higher for individuals who reported being divorced than
-for those who reported being married in the years 1973, 1984, 1987,
-1990, 1991, 1993, 2008, and 2012.
-
-\begin{figure}
-
-{\centering \includegraphics{paper_files/figure-pdf/fig-eight-1.pdf}
-
-}
-
-\caption{\label{fig-eight}Relationship between Divorce and Happiness by
-Year}
-
-\end{figure}
-
-\hypertarget{degree}{%
-\subsubsection{Degree}\label{degree}}
-
-In Figure~\ref{fig-nine}, which shows that there is a certain
-relationship between people's level of education and their level of
-happiness in life. From the graph, it can be observed that the
-proportion of people who feel ``not too happy'' is the highest among
-those with education levels lower than high school. However, the
-proportion of unhappy individuals is the lowest among those with
-bachelor's and graduate degrees, suggesting that as people's education
-level increases, their level of happiness also gradually increases.
-
-\begin{figure}
-
-{\centering \includegraphics{paper_files/figure-pdf/fig-nine-1.pdf}
-
-}
-
-\caption{\label{fig-nine}Relationship between Happiness and Degree}
-
-\end{figure}
-
-\hypertarget{model}{%
-\section{Model}\label{model}}
-
-\begin{verbatim}
-
-Call:
-lm(formula = happy_score ~ age + degree + finance_satified + 
-    health + divorce, data = data)
-
-Coefficients:
-                          (Intercept)                                    age  
-                             4.951478                              -0.002144  
-                     degreebachelor's                         degreegraduate  
-                             0.028053                               0.026886  
-                    degreehigh school            degreeless than high school  
-                            -0.005915                              -0.106730  
- finance_satifiednot satisfied at all  finance_satifiedpretty well satisfied  
-                            -0.471882                               0.087194  
-                           healthfair                             healthgood  
-                            -0.315050                              -0.063929  
-                           healthpoor                             divorceyes  
-                            -0.747780                              -0.018373  
-\end{verbatim}
-
-\hypertarget{summary}{%
-\section{summary}\label{summary}}
-
-\hypertarget{table-of-relationship-between-number-of-children-and-happiness-in-the-family.}{%
-\subsection{Table of Relationship between Number of Children and
-Happiness in the
-Family.}\label{table-of-relationship-between-number-of-children-and-happiness-in-the-family.}}
-
-In the table two, which appears to be presenting data on the happiness
-levels of babies, as rated by some measure or criteria, at different
-ages from 0 to 4 years old. The three categories of happiness levels are
-``not too happy,'' ``happy,'' and ``very happy.'' Looking at the data
-for 4-year-old, we can see that 48.15\% of them were rated as ``not too
-happy,'' 14.81\% as ``very happy,'' and the remaining 37.04\% as simply
-``happy.'' This suggests that the majority of 4-year-old were not rated
-as particularly happy, with less than half of them falling into the
-happy or very happy categories.
-
+\hypertarget{model-linear-regression}{%
+\section{Model : Linear Regression}\label{model-linear-regression}}
+
+\begin{equation}\protect\hypertarget{eq-model}{}{
+\hat{Y}=\hat{\beta_0} + \hat{\beta_1}X_{finance-score} + \hat{\beta_2}X_{health-score} + \hat{\beta_3}X_{happy} + 
+\hat{\beta_6}X_{babies-number} 
+}\label{eq-model}\end{equation}
+
+\hypertarget{tbl-lm}{}
 \begin{table}
-
-\caption{Table of Happy by Various Variables}
+\caption{\label{tbl-lm}Linear Model and its Summary Statistics }\tabularnewline
+
 \centering
-\begin{tabular}[t]{l|r|r|r}
-\hline
-babies & happy & not too happy & very happy\\
-\hline
-0 & 51.37 & 10.04 & 38.59\\
-\hline
-1 & 55.13 & 8.96 & 35.91\\
-\hline
-2 & 54.97 & 7.46 & 37.57\\
-\hline
-3 & 52.36 & 10.63 & 37.01\\
-\hline
-4 & 48.15 & 14.81 & 37.04\\
-\hline
+\begin{tabular}[t]{lc}
+\toprule
+  & Babies\\
+\midrule
+(Intercept) & \num{1.24}\\
+ & {}[\num{1.10}, \num{1.37}]\\
+finance\_score & \num{0.03}\\
+ & {}[\num{0.01}, \num{0.06}]\\
+health\_score & \num{0.02}\\
+ & {}[\num{-0.01}, \num{0.05}]\\
+happyvery happy & \num{0.01}\\
+ & {}[\num{-0.05}, \num{0.06}]\\
+\midrule
+Num.Obs. & \num{3047}\\
+R2 & \num{0.002}\\
+R2 Adj. & \num{0.001}\\
+AIC & \num{5686.7}\\
+BIC & \num{5716.8}\\
+Log.Lik. & \num{-2838.336}\\
+F & \num{2.129}\\
+RMSE & \num{0.61}\\
+\bottomrule
 \end{tabular}
@@
 
-\hypertarget{table-of-health-and-happiness-in-the-family}{%
-\subsection{Table of Health and Happiness in the
-Family}\label{table-of-health-and-happiness-in-the-family}}
-
-In table three, which appears to be presenting data on the relationship
-between the health and happiness levels of families, based on some
-measure or criteria. The three categories of happiness levels are ``not
-too happy,'' ``happy,'' and ``very happy,'' while the four categories of
-health are ``excellent,'' ``fair,'' ``good,'' and ``poor.'' Looking at
-the data, we can see that families who rated their health as
-``excellent'' had the highest proportion of respondents who reported
-being ``very happy,'' at 53.70\%, and the lowest proportion of those who
-were ``not too happy,'' at only 4.94\%. In contrast, families who rated
-their health as ``fair'' had the highest proportion of respondents who
-were ``not too happy,'' at 15.92\%, and the lowest proportion of those
-who were ``very happy,'' at only 25.81\%.
-
+The Table~\ref{tbl-lm} is built based on the Equation~\ref{eq-model}:
+
+\begin{itemize}
+\tightlist
+\item
+  \(\hat{Y}\) is predicted value of the dependent variable. This is the
+  outcome we're trying to predict or estimate based on the independent
+  variables.
+\item
+  \(\hat{\beta_0}\) : The intercept term, which represents the expected
+  value of \(\hat{Y}\) when all independent variables are equal to 0.
+\item
+  \(\hat{\beta_1}\) , \(\hat{\beta_2}\) , \(\hat{\beta_3}\) are the
+  estimated coefficients for each independent variable. These
+  coefficients indicate the average change in the dependent variable
+  \(\hat{Y}\) associated with a one-unit change in the corresponding
+  independent variable, holding all other variables constant. The
+  independent variables are:
+\item
+  \(X_{age}\) : Age of the individual.
+\item
+  \(X_{degree-score}\) : A measure of the individual's level of
+  education or degree.
+\item
+  \(X_{finance-score}\) : A measure of the individual's financial
+  stability or status.
+\item
+  \(X_{health-score}\) : A measure of the individual's overall health.
+\item
+  \(X_{divorce-score}\) : A measure of the individual's likelihood of
+  divorce or past divorces.
+\item
+  \(X_{babies-number}\) : The number of babies/children the individual
+  has.
+\end{itemize}
+
+The given multiple linear regression analysis aimed to predict an
+unspecified dependent variable based on several independent variables,
+including babies (intercept), finance score, health score, and two
+levels of happiness (not too happy and very happy). The model's overall
+explanatory power is quite low, with an R² of 0.009, indicating that it
+only accounts for 0.9\% of the variation in the dependent variable.The
+finance and health scores both have positive relationships with the
+dependent variable, with coefficients of 0.03 and 0.06, respectively.
+The confidence intervals for these variables do not include zero,
+suggesting that these relationships are statistically significant.
+However, the coefficients for the happiness levels (not too happy and
+very happy) are small and have confidence intervals that include zero,
+which indicates that they might not be significantly related to the
+dependent variable.
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+In conclusion, the analysis of the data presented in
+Figure~\ref{fig-one} through Figure~\ref{fig-six} reveals several key
+findings related to the number of children in a family and its
+association with happiness, health, and financial satisfaction. Overall,
+families with no children report the highest levels of happiness, but
+this result could be influenced by the larger sample size of childless
+families. The sex distribution data indicates a higher percentage of
+females in families with more children, with the most significant
+differences observed in families with one and four children.
+
+The analysis of health status shows that having one child is associated
+with the highest proportion of participants reporting `excellent'
+health. The relationship between health and the number of children
+suggests that better health is generally associated with a higher
+likelihood of having one or more children, while poorer health
+correlates with a lower likelihood.Financial satisfaction also appears
+to be connected to the number of children in a family, with families
+with higher financial satisfaction generally having fewer children,
+while those with lower financial satisfaction have more children. This
+relationship may not be linear, and other factors could influence the
+number of children in a family.
+
+It is important to acknowledge the limitations of this analysis, such as
+the potential influence of various confounding factors and the
+possibility of non-linear relationships between variables. Furthermore,
+the data may not be representative of all families or cultural contexts,
+so the findings should be interpreted with caution. Nevertheless, this
+study provides valuable insights into the complex relationships between
+family size and factors such as happiness, health, and financial
+satisfaction. Future research could explore these relationships in
+greater depth, considering additional variables, longitudinal data, and
+diverse populations to provide a more comprehensive understanding of the
+factors influencing family size and well-being.
+
+\hypertarget{table-of-relationship-between-number-of-children-and-gender.}{%
+\subsection{Table of Relationship between Number of Children and
+Gender.}\label{table-of-relationship-between-number-of-children-and-gender.}}
+
+In the Table~\ref{tbl-sex}, which presented in the table indicate that
+the sex distribution varies depending on the number of babies in the
+family.Across all groups, there is a consistent pattern of a higher
+percentage of females compared to males. The lowest difference in sex
+distribution is observed among families with no babies, where the
+female-to-male ratio is relatively closer 54.53\% female vs.~45.47\%
+male. As the number of babies in a family increases, the percentage of
+females also increases, with the highest difference observed in families
+with 1 and 4 babies. In these groups, the sex distribution is more
+skewed towards females, with 60.92\% and 60.98\% female representation,
+respectively.
+
+\hypertarget{tbl-sex}{}
 \begin{table}
-
-\caption{Table of Health and Happiness in the Family}
+\caption{\label{tbl-sex}Relationship between Number of Children and Gender }\tabularnewline
+
 \centering
-\begin{tabular}[t]{l|r|r|r}
-\hline
-health & happy & not too happy & very happy\\
-\hline
-excellent & 41.37 & 4.94 & 53.70\\
-\hline
-fair & 58.27 & 15.92 & 25.81\\
-\hline
-good & 57.14 & 7.76 & 35.10\\
-\hline
-poor & 50.14 & 29.09 & 20.77\\
+\begin{tabular}{r|r|r}
+\hline
+babies & female & male\\
+\hline
+1 & 61.70 & 38.30\\
+\hline
+2 & 61.82 & 38.18\\
+\hline
+3 & 62.50 & 37.50\\
+\hline
+4 & 40.00 & 60.00\\
 \hline
@@
 
-\hypertarget{table-of-financial-satisfaction-and-happiness-in-the-family}{%
-\subsection{Table of Financial Satisfaction and Happiness in the
-Family}\label{table-of-financial-satisfaction-and-happiness-in-the-family}}
-
-In table four, which appears that the table is presenting data on the
-relationship between financial satisfaction and happiness levels in
-families, based on some measure or criteria. The three categories of
-happiness levels are ``not too happy,'' ``happy,'' and ``very happy,''
-while the three categories of financial satisfaction are ``more or less
-satisfied,'' ``not satisfied at all,'' and ``pretty well satisfied.''
-Looking at the data, we can see that families who reported being
-``pretty well satisfied'' with their finances had the highest proportion
-of respondents who were ``very happy,'' at 52.0\%, and the lowest
-proportion of those who were ``not too happy,'' at only 5.24\%. On the
-other hand, families who reported being ``not satisfied at all'' with
-their finances had the highest proportion of respondents who were ``not
-too happy,'' at 20.92\%, and the lowest proportion of those who were
-``very happy,'' at only 22.5\%.
-
+\hypertarget{distribution-of-happiness-levels-across-families-with-different-numbers-of-babies}{%
+\subsection{Distribution of Happiness Levels Across Families with
+Different Numbers of
+Babies}\label{distribution-of-happiness-levels-across-families-with-different-numbers-of-babies}}
+
+In the Table~\ref{tbl-happ}, which suggests that families with 4 babies
+have the highest proportion of ``happy'' individuals at 63.41\%. In
+contrast, families with 3 babies have the highest proportion of ``not
+too happy'' individuals at 16.57\% and the lowest proportion of
+``happy'' individuals at 50.30\%. Families with 0, 1, and 2 babies have
+relatively similar distributions of happiness levels. It is worth noting
+that families with 3 babies have the highest proportion of ``very
+happy'' individuals at 33.14\%, followed closely by families with 2
+babies at 32.95\%. Families with 4 babies have the lowest proportion of
+``very happy'' individuals at 24.39\%.
+
+\hypertarget{tbl-happ}{}
 \begin{table}
-
-\caption{Table of Financial Satisfaction and Happiness in the Family}
+\caption{\label{tbl-happ}Happiness Levels Across Families with number of Babies }\tabularnewline
+
 \centering
-\begin{tabular}[t]{l|r|r|r}
-\hline
-finance\_satified & happy & not too happy & very happy\\
-\hline
-more or less satisfied & 56.76 & 7.74 & 35.5\\
-\hline
-not satisfied at all & 56.59 & 20.92 & 22.5\\
-\hline
-pretty well satisfied & 42.75 & 5.24 & 52.0\\
+\begin{tabular}{r|r|r}
+\hline
+babies & not too happy & very happy\\
+\hline
+1 & 28.95 & 71.05\\
+\hline
+2 & 26.23 & 73.77\\
+\hline
+3 & 33.33 & 66.67\\
+\hline
+4 & 33.33 & 66.67\\
 \hline
@@
 
-In table five, which appears to be presenting data on the relationship
-between divorce and happiness levels in families, based on some measure
-or criteria. The three categories of happiness levels are ``not too
-happy,'' ``happy,'' and ``very happy,'' while the two categories of
-divorce are ``no'' and ``yes.'' Looking at the data, we can see that
-there are only small differences in the proportions of families who
-reported being ``happy'' or ``not too happy'' depending on whether or
-not they had experienced divorce. Specifically, families who reported
-``no'' to divorce had a slightly higher proportion of respondents who
-were ``very happy,'' at 38.61\%, compared to those who reported ``yes''
-to divorce, at 36.24\%. However, families who reported ``yes'' to
-divorce had a slightly higher proportion of respondents who were ``not
-too happy,'' at 11.53\%, compared to those who reported ``no'' to
-divorce, at 9.29\%.
-
+\hypertarget{distribution-of-self-rated-health-status-across-families-with-different-numbers-of-babies}{%
+\subsection{Distribution of Self-Rated Health Status Across Families
+with Different Numbers of
+Babies}\label{distribution-of-self-rated-health-status-across-families-with-different-numbers-of-babies}}
+
+In Table~\ref{tbl-heal}, which appears suggests that individuals without
+any babies tend to have higher percentages in all health categories,
+especially in the ``poor'' health category (93.52\%). As the number of
+babies in a family increases, the proportion of individuals in the
+``excellent,'' ``fair,'' and ``good'' health categories generally
+decreases. The ``poor'' health category also follows this trend, but the
+decrease is less pronounced. Individuals with 1 or 2 babies have
+relatively similar health status distributions, with slightly higher
+percentages in the ``excellent'' and ``good'' health categories compared
+to the ``fair'' and ``poor'' health categories. Individuals with 3 or 4
+babies have the lowest percentages across all health categories.
+
+\hypertarget{tbl-heal}{}
 \begin{table}
-
-\caption{Table of Divorce and Happiness in the Family}
+\caption{\label{tbl-heal}Health Status with number of Babies }\tabularnewline
+
 \centering
-\begin{tabular}[t]{l|r|r|r}
-\hline
-divorce & happy & not too happy & very happy\\
-\hline
-no & 52.10 & 9.29 & 38.61\\
-\hline
-yes & 52.23 & 11.53 & 36.24\\
+\begin{tabular}{l|r|r|r|r}
+\hline
+health & 1 & 2 & 3 & 4\\
+\hline
+excellent & 65.70 & 28.62 & 5.01 & 0.67\\
+\hline
+fair & 68.82 & 21.94 & 8.31 & 0.92\\
+\hline
+good & 68.25 & 26.43 & 5.15 & 0.17\\
+\hline
+poor & 73.97 & 21.92 & 4.11 & NA\\
 \hline
@@
 
-In table six, which appears to be presenting data on the relationship
-between educational attainment and happiness levels in families, based
-on some measure or criteria. The three categories of happiness levels
-are ``not too happy,'' ``happy,'' and ``very happy,'' while the
-categories of educational attainment are ``associate/junior college,''
-``bachelor's,'' ``graduate,'' ``high school,'' and ``less than high
-school.'' Looking at the data, we can see that families with different
-levels of educational attainment generally reported similar levels of
-happiness. The proportions of respondents who reported being ``very
-happy'' were similar across all levels of educational attainment,
-ranging from 41.24\% for those with an associate/junior college degree
-to 44.28\% for those with a graduate degree. The proportions of
-respondents who reported being ``not too happy'' were also similar
-across all levels of educational attainment, ranging from 5.26\% for
-those with a graduate degree to 14.96\% for those with less than a high
-school education.
-
+\hypertarget{distribution-of-financial-satisfaction-across-families-with-different-numbers-of-babies}{%
+\subsection{Distribution of Financial Satisfaction Across Families with
+Different Numbers of
+Babies}\label{distribution-of-financial-satisfaction-across-families-with-different-numbers-of-babies}}
+
+In Table~\ref{tbl-fin}, which appears suggests that families with 0
+babies have the highest percentages of financial satisfaction across all
+categories. As the number of babies in a family increases, the
+proportion of families in each financial satisfaction category generally
+decreases. Families with 4 babies have the lowest percentages in all
+financial satisfaction categories.Notably, the ``pretty well satisfied''
+category shows the steepest decline in percentages as the number of
+babies increases.Families with 0 babies in this category have the
+highest percentage of financial satisfaction at 85.47\%, while families
+with 4 babies have the lowest percentage at 0.05\%.
+
+\hypertarget{tbl-fin}{}
 \begin{table}
-
-\caption{Table of Degree and Happiness in the Family}
+\caption{\label{tbl-fin}Table of Financial Satisfaction and Number of babies }\tabularnewline
+
 \centering
-\begin{tabular}[t]{l|r|r|r}
-\hline
-degree & happy & not too happy & very happy\\
-\hline
-associate/junior college & 50.85 & 7.91 & 41.24\\
-\hline
-bachelor's & 50.66 & 5.63 & 43.71\\
-\hline
-graduate & 50.47 & 5.26 & 44.28\\
-\hline
-high school & 53.48 & 8.86 & 37.66\\
-\hline
-less than high school & 50.90 & 14.96 & 34.13\\
+\begin{tabular}{l|r|r|r|r}
+\hline
+finance\_satified & 1 & 2 & 3 & 4\\
+\hline
+more or less satisfied & 69.20 & 25.15 & 5.12 & 0.53\\
+\hline
+not satisfied at all & 64.89 & 28.15 & 6.30 & 0.65\\
+\hline
+pretty well satisfied & 67.08 & 27.41 & 5.26 & 0.25\\
 \hline
@@
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-The analysis of the General Social Survey data-set from 1972 provides
-insights into various aspects of individuals' lives in the United States
-during that time period. The results suggest that several variables,
-such as financial satisfaction, self-reported health status, and level
-of education, have a positive relationship with individuals' level of
-happiness.Regarding family dynamics, the analysis indicates that
-individuals with no children reported the highest levels of happiness,
-although the data set's limitations require further exploration of the
-proportion of individuals with different numbers of children. Being
-divorced may have a slight impact on one's level of happiness in life,
-with a small proportion of individuals feeling ``not too happy''
-compared to married individuals.
-
-Furthermore, the analysis suggests that individuals' self-rated health
-status has a positive relationship with their self-rated level of
-happiness. The higher the participants' self-rated health, the higher
-their self-rated level of satisfaction with life. Similarly, there is a
-positive relationship between people's satisfaction with their current
-financial situation and their level of happiness in life. The higher
-people's satisfaction with their finances, the higher their level of
-happiness.The analysis suggests that there is a certain relationship
-between people's level of education and their level of happiness in
-life. The proportion of people who feel ``not too happy'' is the highest
-among those with education levels lower than high school. However, the
-proportion of unhappy individuals is the lowest among those with
-bachelor's and graduate degrees, suggesting that as people's education
-level increases, their level of happiness also gradually increases.
-
-Overall, these findings provide valuable insights into the factors that
-may influence individuals' overall life satisfaction during the early
-1970s in the United States. The results can be useful for researchers
-and students interested in exploring topics such as social
-stratification, gender roles, family dynamics, health disparities, and
-subjective well-being.
-
 \hypertarget{discussion}{%
 \section{Discussion}\label{discussion}}
+
+\hypertarget{role-of-gender-distribution-in-family-size-and-well-being}{%
+\subsection{Role of gender distribution in family size and
+well-being}\label{role-of-gender-distribution-in-family-size-and-well-being}}
+
+The observation that families with more children have a higher
+percentage of females, particularly in families with one and four
+children, highlights the importance of examining the impact of gender
+distribution within families. In many societies, traditional gender
+roles dictate that women assume primary responsibilities for children,
+which could lead to a disproportionate burden on women in larger
+families. This unequal distribution of responsibilities might impact
+women's well-being, including their mental and physical health, career
+opportunities, and financial stability (Perrin 2015). Moreover, the
+unequal distribution of resources within families due to gender biases
+could exacerbate these disparities, further impacting the well-being of
+women in larger families (White 2000). Additionally, societal
+expectations and norms surrounding gender roles may influence the
+decision-making process of couples when considering family size. For
+instance, cultural pressure to have more children or adhere to specific
+gender roles within a family might contribute to stress, relationship
+strain, and decreased well-being among family members (Montgomery 2017).
+
+To gain a more comprehensive understanding of the role of gender in
+family well-being, future research should examine how gender roles and
+expectations evolve as family size changes, as well as how these
+dynamics impact overall happiness, health, and financial satisfaction.
+This research could help inform policies and interventions that promote
+gender equity within families, ensuring that the well-being of all
+family members is considered and supported, regardless of family size.
 
@@
 These findings have important implications for policymakers and
-practitioners working to improve individuals' quality of life (Ory 1994)
-. For example, policies aimed at increasing access to affordable
+practitioners working to improve individuals' quality of life(Ory 1994).
+For example, policies aimed at increasing access to affordable
 healthcare and financial assistance programs can help individuals
@@
 The study's results also suggest that education is an important factor
-in individuals' overall well-being and happiness. As people's education
-level increases, their level of happiness also gradually increases. This
-highlights the need for policies and programs that support educational
-attainment, particularly for disadvantaged populations (Rothstein 1994).
-Such programs can include initiatives to improve access to education and
-financial aid for those who may face barriers to education.
+in individuals' overall well-being and happiness(Watkins 2003). As
+people's education level increases, their level of happiness also
+gradually increases. This highlights the need for policies and programs
+that support educational attainment, particularly for disadvantaged
+populations. Such programs can include initiatives to improve access to
+education and financial aid for those who may face barriers to education
+(Sherry 2001).
 
@@
 
-\hypertarget{impact-of-divorce-on-individuals-happiness}{%
-\subsection{Impact of divorce on individuals'
-happiness}\label{impact-of-divorce-on-individuals-happiness}}
-
-Divorce is a significant life event that can have profound effects on an
-individual's overall well-being and happiness. The findings of this
-study suggest that individuals who have experienced divorce may have
-lower levels of happiness than those who are married or have never been
-married. This could be due to a range of factors, including the loss of
-social support and economic stability that often accompanies divorce
-(Headey 1989).
-
-One possible explanation for the association between divorce and
-happiness is the impact of social support. Marriage provides a source of
-emotional support, and individuals who divorce may experience a loss of
-this support network. Furthermore, divorce can result in the breakdown
-of extended family relationships, reducing the availability of social
-support. This loss of social support could contribute to lower levels of
-happiness and well-being. Economic factors may also play a role in the
-relationship between divorce and happiness (Çakar 2020). Divorce can
-result in significant financial upheaval, particularly for individuals
-who were financially dependent on their partner. This financial
-instability could contribute to lower levels of happiness and
-well-being, as financial stress can be a significant source of anxiety
-and depression.
-
-Further research could explore the reasons behind the association
-between divorce and happiness. Qualitative studies could be conducted to
-explore the experiences of individuals who have gone through divorce and
-how this event has affected their well-being. Longitudinal studies could
-also be conducted to examine changes in individuals' happiness levels
-before and after a divorce(Lucas 2003).
-
-Overall, the findings of this study highlight the importance of
-considering the impact of divorce on individuals' well-being and
-happiness. Policies and interventions aimed at supporting individuals
-going through divorce, such as access to counseling and financial
-support, could help to mitigate the negative effects of this life event
-and improve individuals' overall well-being.
-
 \hypertarget{the-importance-of-historical-context-in-understanding-well-being}{%
@@
 from those of today, and these differences could have influenced
-individuals' well-being. These social movements may have influenced
-individuals' attitudes towards social stratification, gender roles, and
-family dynamics, which, in turn, could have affected their well-being.
+individuals' well-being (Stewart 1989). These social movements may have
+influenced individuals' attitudes towards social stratification, gender
+roles, and family dynamics, which, in turn, could have affected their
+well-being.
 
@@
 that address these economic challenges may have had a significant impact
-on individuals' well-being during this period.
-
-Furthermore, the study's findings can be compared to more recent data to
-examine changes in the relationships between different factors and
-well-being over time (CBrunstein 1993). For example, the impact of
-divorce on well-being may have changed over time, as societal attitudes
-towards divorce have shifted. Comparing the study's findings to more
-recent data can provide insights into how societal changes have
-influenced individuals' well-being over time.Overall, the historical
-context is essential in understanding individuals' well-being during a
-particular period in time. The study's focus on the early 1970s in the
-United States provides valuable insights into the factors that
-influenced individuals' well-being during that period. These findings
-can be used to develop interventions that address the unique challenges
-faced by individuals during a particular historical context, as well as
-to compare changes in the relationships between different factors and
-well-being over time.
-
-\hypertarget{impact-of-financial-stability-on-happiness}{%
-\subsection{Impact of Financial Stability on
-Happiness}\label{impact-of-financial-stability-on-happiness}}
-
-As the analysis of the GSS dataset shows, there is a positive
-correlation between individuals' satisfaction with their financial
-situation and overall well-being, an important finding. This correlation
-underscores the importance of U.S. financial stability in determining a
-person's happiness in the early 1970s. In this discussion, we will
-further explore the impact of these factors on individual well-being
-during that time.
-
-In the early 1970s, the United States was going through a period of
-economic turmoil. One of the most important factors is the rapid rise in
-inflation. The country faces a phenomenon known as ``stagflation,''
-which is characterized by a stagnant economy, high inflation, and high
-unemployment. This unusual economic situation is largely attributable to
-the 1973 oil crisis, which caused a spike in oil prices and disrupted
-the global economy (Barsky 2001). The rise in inflation during this
-period has a direct impact on individuals' financial satisfaction. As
-the cost of goods and services increases, people find it a challenge to
-maintain their previous standard of living (Diener 2009). This is
-further exacerbated by high unemployment, as many people struggle to
-find stable employment.Analysis of the GSS dataset highlights the
-importance of financial stability in determining individual well-being,
-emphasizing the need for effective economic policies to ensure the
-financial security and well-being of populations.
-
-\hypertarget{the-role-of-education-in-happiness}{%
-\subsection{The Role of Education in
-Happiness}\label{the-role-of-education-in-happiness}}
-
-The study found that as an individual's education level increased, their
-level of happiness also gradually increased. This finding prompts a
-discussion on the role of education in determining one's overall
-happiness and well-being during the early 1970s. It would be interesting
-to explore the potential reasons behind this correlation, such as the
-opportunities for personal development, improved employment prospects,
-and social mobility that education provides(Warr 1992). Moreover,
-examining the accessibility and quality of education during that period
-could offer further insights into the impact of education on happiness.
-By understanding the role of education in shaping individuals'
-happiness, researchers and policymakers can better appreciate the
-significance of investing in education and ensuring equal access to
-quality education for all.One possible explanation is that education
-provides individuals with the tools and resources they need to achieve
-personal goals and fulfill their potential(Jenkins 2009). Education can
-help individuals develop a sense of purpose, autonomy, and mastery,
-which are important factors in promoting happiness and well-being. In
-addition, education can provide individuals with the skills and
-knowledge needed to pursue meaningful and fulfilling careers, which can
-also contribute to their overall sense of well-being.
-
-Moreover, education can provide opportunities for social mobility, which
-can enhance individuals' sense of self-worth and life satisfaction.
-Education can help individuals acquire the social and cultural capital
-necessary to succeed in their professional and personal lives, which can
-lead to increased opportunities and social status (Keller 1964). This,
-in turn, can contribute to individuals' overall sense of happiness and
-well-being.However, it is important to note that not all forms of
-education may have the same impact on individuals' happiness and
-well-being. The accessibility and quality of education are crucial
-factors that can influence the extent to which education promotes
-happiness and well-being. For example, individuals who have access to
-high-quality education may experience greater benefits in terms of
-personal development, employment prospects, and social mobility than
-those who do not have access to such education (Margolis 2014).
-
-Therefore, policymakers and educators must work to ensure that all
-individuals have equal access to high-quality education. Investing in
-education can not only promote individuals' personal and professional
-growth but also contribute to the overall well-being and happiness of
-society as a whole. By understanding the role of education in shaping
-individuals' happiness, we can work towards building a more just and
-equitable society.
+on individuals' well-being during this period(Brunstein 1993).
+
+\hypertarget{relationship-between-family-size-happiness-health-and-gender-distribution}{%
+\subsection{Relationship between Family Size, Happiness, Health, and
+Gender
+Distribution}\label{relationship-between-family-size-happiness-health-and-gender-distribution}}
+
+The analysis of the data presented in Figure~\ref{fig-one} and
+Figure~\ref{fig-five} suggests a relationship between the number of
+children in a family and the overall happiness and health status of
+individuals. Families with no children seem to have the highest
+proportion of `very happy', `pretty happy', and `not too happy'
+responses, although this could be influenced by the larger amount of
+data collected for childless individuals. Furthermore, families with
+`excellent' health tend to have a more balanced distribution of
+children, with a higher likelihood of having one or more children
+compared to families with poorer health.
+
+In addition to the relationship between family size and happiness, as
+well as family size and health, the analysis of data in
+Figure~\ref{fig-two} also indicates a connection between family size and
+gender distribution. The data suggests that the sex distribution varies
+depending on the number of babies in the family, with a higher
+percentage of females compared to males observed across all groups. As
+the number of babies in a family increases, the percentage of females
+also increases, with the highest difference observed in families with
+one and four babies. In these groups, the sex distribution is more
+skewed towards females. This finding suggests that the presence and
+number of babies in a family may also influence the gender composition
+of the family.
+
+The data from Figure~\ref{fig-three} and Figure~\ref{fig-four} further
+supports the relationship between family size, happiness, and health.
+The analysis of the number of children had each year from 1972 to 2012
+in relation to the level of happiness shows fluctuations in the
+proportion of individuals who reported feeling ``not too happy'' and
+``happy'' over the years. This finding highlights the potential
+influence of horticultural and economic factors on happiness and family
+size over time.
+
+Additionally, the data from Figure~\ref{fig-four} reveals that having
+one child is associated with the highest proportion of participants
+reporting `excellent' health status. This finding might suggest that
+having a smaller family size could be related to better health outcomes
+for individuals. However, it is crucial to consider other factors that
+could potentially influence the health status of individuals, such as
+access to healthcare, lifestyle choices, and overall well-being.
+
+In summary, the relationship between family size and happiness, health,
+and gender distribution is complex and multifaceted. While the data
+suggests certain trends and connections, it is important to recognize
+that other factors may also play a role in determining happiness,
+health, and gender distribution in families with varying numbers of
+children. Further research and analysis are needed to better understand
+these relationships and to identify potential contributing factors.
+
+\hypertarget{impact-of-family-size-on-financial-satisfaction}{%
+\subsection{Impact of Family Size on Financial
+Satisfaction}\label{impact-of-family-size-on-financial-satisfaction}}
+
+The data from Figure~\ref{fig-six} reveals a connection between
+financial satisfaction and the number of children in a family. In
+general, families with higher financial satisfaction tend to have fewer
+children, while those with lower financial satisfaction have more
+children. This trend is observed across all three financial satisfaction
+levels, with the majority of families in all financial satisfaction
+levels having 0 babies. As the number of children increases, the
+percentages for all three financial satisfaction categories tend to
+decrease, suggesting that family size may play a role in financial
+satisfaction. However, it is important to note that this relationship
+may not be linear and that other factors could also influence the number
+of children in a family and their financial satisfaction.
 
@@
 \item
-  The data-set used in the study is small, consisting of only 5
-  observations and 10 variables, which may limit the generalization of
-  the findings.
-\item
-  The study only examines data from the year 1972, which may not be
-  representative of individuals' lives in the United States today or
-  even in the 1970s as a whole.
-\item
-  The study only uses graphical representation to analyze the
-  relationships between variables, which may not provide a comprehensive
-  understanding of the complex relationships between variables.
-\item
-  The study only examines a limited set of variables and does not
-  consider other factors that could impact individuals' level of
-  happiness and well-being, such as social support, employment status,
-  and cultural factors.
+  Sample representation: The data used in this analysis may not be
+  representative of all families or cultural contexts, which could limit
+  the generalization of the findings. Further research with more diverse
+  samples is needed to ensure the results are applicable across
+  different populations.
+\item
+  Confounding factors: The analysis does not account for potential
+  confounding factors that might influence the relationships between the
+  number of children, happiness, health, and financial satisfaction.
+  Factors such as age, education, income, and cultural background could
+  play a role in the observed patterns and should be considered in
+  future research.
+\item
+  Cross-sectional data: The data used in this analysis is
+  cross-sectional, which makes it challenging to establish causal
+  relationships between variables. Longitudinal data would allow for a
+  more in-depth understanding of how the variables change over time and
+  their potential causal relationships.
+\item
+  Non-linear relationships: The relationships between the variables in
+  this study may not be linear, and other forms of relationships could
+  exist. The analysis could be extended by exploring different types of
+  relationships between variables, such as quadratic or cubic functions.
 \end{itemize}
@@
 \item
-  Further research could expand the data-set to include more
-  observations and variables, which could provide a more comprehensive
-  understanding of individuals' lives during the early 1970s in the
-  United States.
-\item
-  Future studies could examine more recent data from the GSS to
-  investigate changes in the relationships between variables over time.
-\item
-  Future studies could use more advanced statistical methods to analyze
-  the relationships between variables, such as regression analysis, to
-  provide a more robust understanding of the relationships between
-  variables.
-\item
-  Future studies could consider other factors that may impact
-  individuals' level of happiness and well-being, such as social
-  support, employment status, and cultural factors.
+  Diversify the sample: Conduct further research with more diverse
+  samples, including participants from different cultural backgrounds,
+  age groups, and socioeconomic statuses, to better understand the
+  relationships between the number of children, happiness, health, and
+  financial satisfaction across various populations.
+\item
+  Consider potential confounding factors: Future research should
+  consider potential confounding factors that might influence the
+  relationships between variables. By controlling for these factors, the
+  analysis would provide a clearer understanding of the true
+  relationships between the number of children and happiness, health,
+  and financial satisfaction.
+\item
+  Longitudinal data analysis: Collect and analyze longitudinal data to
+  establish causal relationships between variables and observe how these
+  relationships change over time. This approach would provide a more
+  comprehensive understanding of the factors influencing family size and
+  well-being.
+\item
+  Explore non-linear relationships: Expand the analysis to consider
+  non-linear relationships between the variables in the study. By
+  exploring different types of relationships, the research could provide
+  a more nuanced understanding of how the number of children, happiness,
+  health, and financial satisfaction are interconnected.
+\item
+  Investigate additional variables: Consider other variables that might
+  influence family size and well-being, such as parenting styles, social
+  support networks, and access to childcare. Incorporating these
+  additional variables in the analysis could provide a more holistic
+  understanding of the factors that contribute to family well-being.
 \end{itemize}
@@
 
-\hypertarget{have-you-ever-been-divorced}{%
-\subsubsection{5. Have you ever been
-divorced?}\label{have-you-ever-been-divorced}}
+\hypertarget{what-is-your-biological-sex}{%
+\subsubsection{5. What is your biological
+sex?}\label{what-is-your-biological-sex}}
 
@@
 \item
-  Yes
-\item
-  No
+  Male
+\item
+  Female
 \end{enumerate}
 
-\hypertarget{what-is-your-current-living-area}{%
-\subsubsection{6. What is your current living
-area?}\label{what-is-your-current-living-area}}
+\hypertarget{how-would-you-rate-your-overall-level-of-well-being}{%
+\subsubsection{6 How would you rate your overall level of
+well-being?}\label{how-would-you-rate-your-overall-level-of-well-being}}
 
@@
 \item
-  Large city
-\item
-  Small city
-\item
-  Suburban
-\item
-  Rural
-\end{enumerate}
-
-\hypertarget{what-is-your-age-please-enter-a-number}{%
-\subsubsection{7. What is your age? (Please enter a
-number)}\label{what-is-your-age-please-enter-a-number}}
-
-\hypertarget{what-is-your-biological-sex}{%
-\subsubsection{8. What is your biological
-sex?}\label{what-is-your-biological-sex}}
-
-\begin{enumerate}
-\def\labelenumi{\alph{enumi}.}
-\tightlist
-\item
-  Male
-\item
-  Female
-\end{enumerate}
-
-\hypertarget{what-is-the-highest-level-of-education-you-have-completed}{%
-\subsubsection{9. What is the highest level of education you have
-completed?}\label{what-is-the-highest-level-of-education-you-have-completed}}
-
-\begin{enumerate}
-\def\labelenumi{\alph{enumi}.}
-\tightlist
-\item
-  Less than high school
-\item
-  High school or equivalent
-\item
-  Some college or associate degree
-\item
-  Bachelor's degree
-\item
-  Graduate or professional degree
-\end{enumerate}
-
-\hypertarget{how-would-you-rate-your-overall-level-of-well-being}{%
-\subsubsection{10. How would you rate your overall level of
-well-being?}\label{how-would-you-rate-your-overall-level-of-well-being}}
-
-\begin{enumerate}
-\def\labelenumi{\alph{enumi}.}
-\tightlist
-\item
   Very good
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-modelsummary}{}}%
+Arel-Bundock, Vincent. 2022. {``{modelsummary}: Data and Model Summaries
+in {R}.''} \emph{Journal of Statistical Software} 103 (1): 1--23.
+\url{https://doi.org/10.18637/jss.v103.i01}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-a}{}}%
+Brown, S. J. 2010. {``Marriage and Child Well-Being: Research and Policy
+Perspectives.''} \emph{Journal of Marriage and Family}, 1059--77.
+
 \leavevmode\vadjust pre{\hypertarget{ref-i}{}}%
-Barsky, \& Kilian, R. 2001. {``Do We Really Know That Oil Caused the
-Great Stagflation? A Monetary Alternative.''} \emph{Nber Macroeconomics
-Annual} 16 (5): 137--83.
-
-\leavevmode\vadjust pre{\hypertarget{ref-e}{}}%
-Çakar, F. S. 2020. {``The Role of Social Support in the Relationship
-Between Adolescents' Level of Loss and Grief and Well-Being.''}
-\emph{International Education Studies} 13 (12): 27.
+Brunstein, J. C. 1993. {``Personal Goals and Subjective Well-Being: A
+Longitudinal Study.''} \emph{Journal of Personality and Social
+Psychology}, 1061--70.
+
+\leavevmode\vadjust pre{\hypertarget{ref-b}{}}%
+Cheng, Rosenberg, Y. 2011. {``Aging, Health and Place in Residential
+Care Facilities in Beijing, China.''} \emph{Social Science \& Medicine},
+365--72.
 
 \leavevmode\vadjust pre{\hypertarget{ref-h}{}}%
-CBrunstein, J. C. 1993. {``Personal Goals and Subjective Well-Being: A
-Longitudinal Study.''} \emph{Journal of Personality and Social
-Psychology} 65 (5): 1061--70.
-
-\leavevmode\vadjust pre{\hypertarget{ref-g}{}}%
 Cooper, Scandura, C. D. 2005. {``Looking Forward but Learning from Our
 Past: Potential Challenges to Developing Authentic Leadership Theory and
-Authentic Leaders.''} \emph{Leadership Quarterly} 16 (3): 475--93.
-
-\leavevmode\vadjust pre{\hypertarget{ref-j}{}}%
-Diener, \& Biswas-Diener, E. 2009. {``Will Money Increase Subjective
-Well-Being?: A Literature Review and Guide to Needed Research.''}
-\emph{Springer EBooks}, 119--54.
+Authentic Leaders.''} \emph{Leadership Quarterly}, 475--93.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-o}{}}%
-Headey, \& Wearing, B. 1989. {``Personality, Life Events, and Subjective
-Well-Being: Toward a Dynamic Equilibrium Model.''} \emph{Journal of
-Personality and Social Psychology}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-l}{}}%
-Jenkins, H. 2009. {``Confronting the Challenges of Participatory
-Culture.''} \emph{The MIT Press EBooks}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-m}{}}%
-Keller, \& Zavalloni, S. 1964. {``Ambition and Social Class: A
-Respecification.''} \emph{A Respecification. Social Forces}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-f}{}}%
-Lucas, Clark, R. E. 2003. {``Reexamining Adaptation and the Set Point
-Model of Happiness: Reactions to Changes in Marital Status.''}
-\emph{Journal of Personality and Social Psychology} 84 (3): 527--39.
-
-\leavevmode\vadjust pre{\hypertarget{ref-n}{}}%
-Margolis, Hodge, J. 2014. {``The Teacher Educator's Role in Promoting
-Institutional Versus Individual Teacher Well-Being.''} \emph{Journal of
-Education for Teaching}.
+Montgomery, Chaviano, J. E. 2017. {``Parents at-Risk and Their Children:
+Intersections of Gender Role Attitudes and Parenting Practices.''}
+\emph{Child \& Family Social Work}, 1151--60.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-c}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-d}{}}%
 Ory, \& Cox, M. G. 1994. {``Forging Ahead: Linking Health and Behavior
 to Improve Quality of Life in Older People.''} \emph{Social Indicators
-Research} 33 (3): 89--120.
-
-\leavevmode\vadjust pre{\hypertarget{ref-d}{}}%
-Rothstein, \& Uslaner, B. 1994. {``All for All: Equality, Corruption,
-and Social Trust.''} \emph{World Politics} 58 (1): 41--72.
-
-\leavevmode\vadjust pre{\hypertarget{ref-a}{}}%
-RSiahpush, Spittal, M. 2008. {``Happiness and Life Satisfaction
-Prospectively Predict Self-Rated Health, Physical Health, and the
-Presence of Limiting, Long-Term Health Conditions.''} \emph{American
-Journal of Health Promotion,} 23 (1): 18--26.
-
-\leavevmode\vadjust pre{\hypertarget{ref-b}{}}%
-Vlaev, \& Elliott, I. 2014. {``Financial Well-Being Components.''}
-\emph{Social Indicators Research} 118 (3): 1103--23.
+Research}, 89--120.
+
+\leavevmode\vadjust pre{\hypertarget{ref-j}{}}%
+Perrin, Panyavin, P. B. 2015. {``Disproportionate Burden of Care: Gender
+Differences in Mental Health, Health-Related Quality of Life, and Social
+Support in Mexican Multiple Sclerosis Caregivers.''} \emph{Behavioural
+Neurology}, 1--9.
+
+\leavevmode\vadjust pre{\hypertarget{ref-f}{}}%
+Sherry, Thomas, M. 2001. {``International Students: A Vulnerable Student
+Population.''} \emph{Higher Education}, 33--46.
+
+\leavevmode\vadjust pre{\hypertarget{ref-g}{}}%
+Stewart, \& Healy, A. J. 1989. {``Linking Individual Development and
+Social Changes.''} \emph{American Psychologist}, 30--42.
+
+\leavevmode\vadjust pre{\hypertarget{ref-c}{}}%
+Waite, L. J. 1995. {``Does Marriage Matter?''} \emph{Demography},
+483--507.
+
+\leavevmode\vadjust pre{\hypertarget{ref-e}{}}%
+Watkins, Woodward, P. C. 2003. {``GRATITUDE AND HAPPINESS: DEVELOPMENT
+OF a MEASURE OF GRATITUDE, AND RELATIONSHIPS WITH SUBJECTIVE
+WELL-BEING.''} \emph{Social Behavior and Personality}, 431--51.
 
 \leavevmode\vadjust pre{\hypertarget{ref-k}{}}%
-Warr, P. 1992. {``Age and Occupational Well-Being.''} \emph{Psychology
-and Aging}.
+White, \& Rogers, L. T. 2000. {``Economic Circumstances and Family
+Outcomes: A Review of the 1990s.''} \emph{Behavioural Neurology},
+1035--51.
 

### 2023-04-06 scripts/00-simulate_data.R

@@ -1,0 +1,40 @@
+#### Preamble ####
+# Purpose: generate a simulated dataset with 100 observations, where each observation contains information 
+#about an individual's demographics, well-being, and satisfaction levels. The purpose of this simulated dataset 
+#is to explore relationships and trends among the variables, which can be useful for research, analysis, or practice
+#in understanding factors that may affect people's lives.
+# Author: shaohan chang
+# Date: 4 April 2023
+# Contact: shaohan.chang@utoronto.ca
+# License: MIT
+# Pre-requisites: Download package of tidyverse 
+# Any other information needed? None
+
+library(tidyverse)
+
+#### Simulate data ####
+set.seed(123) # set seed for reproducibility
+
+# generate 100 observations
+n <- 100
+
+# generate year variable (1972 to 2021)
+year <- sample(1972:2021, n, replace = TRUE)
+
+# generate sex variable
+sex <- sample(c("female", "male"), n, replace = TRUE)
+
+# generate babies variable (0 to 5)
+babies <- sample(0:5, n, replace = TRUE)
+
+# generate health variable
+health <- sample(c("excellent", "good", "fair", "poor"), n, replace = TRUE)
+
+# generate finance_satisfaction variable
+finance_satisfaction <- sample(c("not satisfied at all", "more or less satisfied", "pretty well satisfied"), n, replace = TRUE)
+
+# generate happiness variable
+happiness <- sample(c("not too happy", "happy", "very happy"), n, replace = TRUE)
+
+# create a data frame with the generated variables
+simulated_data <- data.frame(year, sex, babies, health, finance_satisfaction, happiness)

### 2023-04-07 outputs/paper/paper.qmd
Add files via upload

@@
 In this context, the objective of this study is to explore the complex interplay between family size and various aspects of family life.
-The study employs cross-sectional cumulative micro data from the United States spanning from 1972 to 2012.
-The paper aims to fill a gap in the existing literature by providing a comprehensive analysis of the relationship between the number of children in a family (0, 1, 2, 3, 4) and different variables such as happiness, health, sex distribution, and financial satisfaction, using multiple data sources.
+This paper analyzes the results of the General Social Survey, which was conducted between 1972 and 2012 to explore various aspects of society during that time frame.The paper aims to fill a gap in the existing literature by providing a comprehensive analysis of the relationship between the number of children in a family (0, 1, 2, 3, 4) and different variables such as happiness, health, sex distribution, and financial satisfaction, using multiple data sources.
 Previous research on this topic has often focused on specific aspects of family life or specific sub populations, leaving a gap in the understanding of the broader relationships between family size and different variables.
@@
 In regards to the variable "not too happy," the proportion of individuals who reported feeling unhappy was relatively high in 1974, 1985, 1993, 2004, 2006, and 2008.
-On the other hand, in regards to the variable "happy," the percentage of individuals reporting feeling happy was relatively high in 1973, 1977, 1994, 2006, and 2012.From the overall data, it can be seen that when people have 1 or 2 children, the most common self-rated health statuses are excellent, fair, and good.
+On the other hand, in regards to the variable "happy," the percentage of individuals reporting feeling happy was relatively high in 1973, 1977, 1994, 2006, and 2012.
+From the overall data, it can be seen that when people have 1 or 2 children, the most common self-rated health statuses are excellent, fair, and good.
+Generally speaking, although with the passage of time, the overall proportion of participation in families with one child is large, but it cannot be said that the number of children will affect the level of health scores.
 
@@
 #| label: fig-three
-#| fig-cap: Relationship between Number of Babies and Happiness by Year
+#| fig-cap: Percentage between Number of Babies and Happiness by Year
 #| echo: false
@@
 
-ggplot(data[data$happy == "very happy", ], aes(x = year, y = factor(babies))) +
-  geom_point(position = position_jitter(width = 0.2, height = 0.1), size = 2, color = "#4daf4a") +
+ggplot(data[data$happy == "very happy", ], aes(x = year, fill = factor(babies))) +
+  geom_bar(position = "fill") +
   facet_wrap(~health, ncol = 5, scales = "free_y") +
-  labs(x = "Year", y = "Number of Babies") +
+  labs(x = "Year", y = "Percentage of Babies", fill = "Number of Babies") +
   theme_bw() +
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.major.x = element_line(color = "grey", size = 0.1),
+  scale_y_continuous(labels = scales::percent_format(), expand = c(0.05, 0)) +
+  theme(panel.grid.major.x = element_line(color = "grey", size = 0.1),
         strip.text = element_text(size = 10),

### 2023-04-07 outputs/paper/paper.qmd
Add files via upload

@@
 The final sample size was determined by considering the availability of data and the need for a balanced representation of different family sizes.
-The sample includes families from diverse socioeconomic backgrounds, ethnicities, and geographic locations in the United States, ensuring a comprehensive representation of the population.
 
@@
 
-Used some R language packages, such as tidyverse [@ti], dplyr [@dplyr], janitor [@janitor] , knitr [@knitr], here [@here], haven [@haven], ggplot [@ggplot] , kableExtra [@kableExtra] , model summary [@modelsummary] to assist in data analysis, and the data from General Social Survey [@gss].
+This following data analysis is processed in R [@R] with packages of tidyverse [@ti], dplyr [@dplyr], janitor [@janitor] , knitr [@knitr], here [@here], haven [@haven], ggplot [@ggplot] , kableExtra [@kableExtra] , model summary [@modelsummary] to assist in data analysis, and the data from General Social Survey [@gss].
 

### 2023-04-11 scripts/03-test_data.R
Delete scripts directory

@@ -1,58 +1,0 @@
-#### Preamble ####
-# Purpose: The purpose of these tests is to check for missing values (NA values) in different variables of the "cleaned_data.csv" dataset. 
-#These tests ensure that the data is clean and complete, and suitable for further analysis. Test One checks the entire dataset for any NA values, 
-#while Tests Two to Five specifically check for NA values in the "happy", "year", "sex", and "health" variables, respectively. The if else() function
-#is used to print a message indicating whether the check has passed or failed.
-# Author: SHAOHAN CHANG 
-# Date: 29 March 2023 
-# Contact: SHAOHAN.CHANG@Toronto.ca 
-# License: MIT
-# Pre-requisites: The prerequisite for running these tests is that the "cleaned_data.csv" dataset has been cleaned and prepared for analysis. The dataset 
-#should also be in a format that is compatible with the readr::read_csv() function used to read the data into R. Additionally, the R environment must be set
-#up with the necessary packages for performing data analysis, such as readr. Finally, the user should have a basic understanding of R programming and data 
-#analysis techniques, including how to write and run R scripts.
-
-#### Work space setup ####
-library(tidyverse)
-library(janitor)
-library(dplyr)
-
-
-#### Test data ####
-
-
-data <- 
-  readr::read_csv("inputs/data/cleaned_data.csv")
-
-# Test One : Check for NA values in the data frame.
-# Explanation : as the result , there 0 NA value. 
-
-check_result <- ifelse(sum(is.na(data)) == 0, "Check passed", "Check failed")
-print(check_result)
-
-
-# Test Two : Check for NA values in happy. 
-
-# Explanation :  Three are 0 missing values in the happy. 
-
-check_result <- ifelse(sum(is.na(data$happy)) == 0, "Check passed", "Check failed")
-print(check_result)
-
-
-# Test Three : Check for NA values in year.
-# Explanation :There are 0 missing values in the year variable. 
-
-check_result <- ifelse(sum(is.na(data$year)) == 0, "Check passed", "Check failed")
-print(check_result)
-
-# Test Four : Check for NA values in sex. 
-# Explanation :There are 0 missing values in the sex variable.
-
-check_result <- ifelse(sum(is.na(data$sex)) == 0, "Check passed", "Check failed")
-print(check_result)
-
-# Test Five : Check for NA values in health. 
-# Explanation :There are 0 missing values in the health variable.
-
-check_result <- ifelse(sum(is.na(data$degree)) == 0, "Check passed", "Check failed")
-print(check_result)

### 2023-04-11 outputs/paper/paper.qmd
Add files via upload

@@
 date-format: "D MMMM YYYY"
-abstract: "This study explores the multifaceted impact of family size on happiness, health, gender dynamics, and financial well-being by analyzing cross-sectional cumulative microdata from the United States between 1972 and 2012.
-This study analyzed the relationship between family size, measured by the number of children, and various aspects of family life, such as happiness, health, and financial satisfaction.
-The findings suggest that happiness levels are highest among childless individuals, while families with one child report the best health status.
-Additionally, higher financial satisfaction is associated with fewer children in a family.
-These insights matter as they provide a better understanding of the factors influencing family size and the potential consequences of family planning decisions on overall wellbeing."
+abstract: "This study analyzed cross-sectional cumulative microdata from the United States spanning 1972 to 2012 to investigate the impact of family size on happiness, health, gender dynamics, and financial well-being.
+The number of children served as a proxy for family size, allowing the examination of relationships between happiness, health, and financial satisfaction in families.
+Findings indicate that childless individuals experience the highest happiness levels, and one-child families exhibit the best health.
+Furthermore, increased financial satisfaction correlates with fewer children within a family.
+These insights hold significance as they enhance our understanding of the factors influencing family size and the potential consequences of family planning decisions on overall well-being."
 format: pdf
@@
 
-This research investigates the diverse effects of family size on various aspects such as happiness, health, gender roles, and financial stability.
-The impact of the number of children in a family on various aspects of family life has been a topic of interest for researchers and policymakers alike [@a].
-Family size and structure play a crucial role in shaping the lives of individuals and communities.
-Understanding the connections between the number of children and factors such as happiness, health, sex distribution, and financial satisfaction can help inform decisions and policies aimed at promoting family well-being [@b].
+This research delves into the multifaceted effects of family size on aspects such as happiness, health, gender roles, and financial stability.
+The influence of a family's number of children on various facets of family life has captivated researchers and policymakers alike [@a].
+Family size and structure play a pivotal role in shaping individuals' and communities' lives.
+Comprehending the connections between child count and factors like happiness, health, sex distribution, and financial satisfaction can aid in developing decisions and policies that promote family well-being [@b].
 
-In this context, the objective of this study is to explore the complex interplay between family size and various aspects of family life.
-This paper analyzes the results of the General Social Survey, which was conducted between 1972 and 2012 to explore various aspects of society during that time frame.The paper aims to fill a gap in the existing literature by providing a comprehensive analysis of the relationship between the number of children in a family (0, 1, 2, 3, 4) and different variables such as happiness, health, sex distribution, and financial satisfaction, using multiple data sources.
+This paper analyzes the results of the General Social Survey, which was conducted between 1972 and 2012 to explore various aspects of society during that time period.
+The paper aims to fill a gap in the existing literature by providing a comprehensive analysis of the relationship between the number of children in a family (0, 1, 2, 3, 4) and relation with different variables such as happiness, health, sex distribution, and financial satisfaction, using multiple data sources.
 Previous research on this topic has often focused on specific aspects of family life or specific sub populations, leaving a gap in the understanding of the broader relationships between family size and different variables.
 
-The methodology of the study includes the analysis of several charts and tables to uncover patterns and trends in the data, suggesting connections between the number of children in a family and the variables of interest.
-For example, the data reveals that families with better health tend to have a higher likelihood of having one or more children, while families with lower financial satisfaction tend to have more children [@c].
-However, the relationships identified in this study may not be linear, and it is important to consider the potential influence of other factors on the number of children in a family.
+In the methodological research, the many charts and tables were examined to discover trends and patterns in the data, such as hints at connections between the relevant factors and the family size.
+For instance, the statistics indicate that families that are happier financially tend to have fewer children, whereas families who are healthier seem to be more likely to have one or more children [@c].
+But since the links shown in this research may not be linear, it is crucial to consider the possible influence of other variables on the number of children in a household.
 
-The structure of the paper is as follows: first, we present the data and methodology used in the study, followed by a detailed analysis of the relationships between the number of children in a family and the variables of interest.
-Next, we discuss the implications of the findings and their relevance to broader discussions on family well-being and policy.
-Finally, we conclude with a summary of the main findings and suggestions for future research in this area.
+The paper is organized as follows: first, presenting the data and methodology used in the study, then conducting a thorough analysis of how the number of children in a family and the relevant variables relate to one another variables.
+The implications of the findings and their applicability to more general discussions on family well-being and policy are then discussed.
+By summarizing the significant conclusions and recommend further study in this area.
 
@@
 
--   year: This variable indicates the year in which the data was collected. In this data-set, all the observations are from the year 1972 to 2012.
--   sex: This variable indicates the biological sex of the individual. It is a categorical variable with two levels: male and female.
--   babies: This variable indicates the number of babies the individual had at the time the data was collected.
-It is a categorical variable with different levels, depending on the number of babies: 0, 1, 2, 3, 4, or 5+.
--   health: This variable indicates the self-reported health status of the individual at the time the data was collected.
-It is a categorical variable with different levels, depending on the health status: excellent, good, fair, or poor.
--   finance_satisfied: This variable indicates the individual's level of satisfaction with their current financial situation.
-It is a categorical variable with different levels of satisfaction: very satisfied, more or less satisfied, not very satisfied, and not at all satisfied.
--   happy: This variable indicates the individual's level of happiness or life satisfaction.
-It is a categorical variable with different levels of happiness: very happy, pretty happy, not too happy, and not at all happy.
--   happy_score: The happy_score variable is an ordinal variable representing the self-reported happiness levels of the individuals in the dataset.
-It ranges from 0 to 3, with 0 representing "not too happy," 1 representing "happy," 2 representing "very happy," and 3 reserved for any unclassified or missing responses.
--   health_score: The health_score variable is an ordinal variable indicating the self-reported health status of the individuals in the dataset.
-It ranges from 1 to 4, with 1 denoting "poor" health, 2 signifying "fair" health, 3 representing "good" health, and 4 referring to "excellent" health.
+-   year: This variable indicates the year in which the data was collected from GSS. In this data-set, all the observations are from the year of 1972 to 2012.
+-   sex: Categorical variable with two levels: male and female.
+-   babies: Integer variable with different levels, depending on the number of babies, for instance : 0, 1, 2, 3, 4, or 5+.
+-   health: This variable indicates the self-reported health status of the individual at the time.
+It is a categorical variable with different levels, depending on the health status, for example : excellent, good, fair, or poor.
+-   finance_satisfied: This variable indicates the individual's different level of satisfaction with their current financial situation.
+It is a categorical variable with different satisfaction levels: very satisfied, more or less satisfied, not very satisfied, and not at all satisfied.
+-   happy: This variable indicates the individual's level of happiness or life satisfaction. It is a categorical variable with different levels of happiness: very happy, pretty happy, not too happy.
+-   happy_score: The happy_score variable is an integer that represents the individuals in the dataset's self-reported happiness levels.
+Its sign ranges from 0 to 3, with 0 denoting "not too happy," 1 denoting "happy," 2 denoting "very happy," and 3 holding any unclassified or missing responses.
+-   health_score: The health_score variable is an ordinal variable shows the self-reported health status of the individuals, which sign the ranges from 1 to 4.
+With 1 denoting "poor" health, 2 signifying "fair" health, 3 representing "good" health, and 4 referring to "excellent" health.
 The value 5 is reserved for any unclassified or missing responses.
@@
 
-In [@fig-two],which presented in the table indicates that the sex distribution varies depending on the number of babies in the family.
-A higher percentage of females compared to males is consistently observed across all groups.
-The lowest difference in sex distribution is found among families with no babies, where the female-to-male ratio is relatively closer.
-As the number of babies in a family increases, the percentage of females also increases, with the highest difference observed in families with one and four babies.
+In [@fig-two], as presented in the bar chart, the gender distribution varies depending on the number of babies in the family.
+By comparison, a higher percentage of females than males is consistently observed across all groups.
+On the other hand, the lowest difference in sex distribution is found among families with no babies, where the female-to-male ratio is relatively closer.
+As the number of babies in a family increases, the percentage of females increases, with the highest difference observed in families with one to four babies.
 In these groups, the sex distribution is more skewed towards females.
@@
 
-In [@fig-three], which to provide a more detailed and comprehensive view of the data, the chart displays an analysis and visualization of the number of children had each year from 1972 to 2012, in relation to the level of happiness.
-In regards to the variable "not too happy," the proportion of individuals who reported feeling unhappy was relatively high in 1974, 1985, 1993, 2004, 2006, and 2008.
-On the other hand, in regards to the variable "happy," the percentage of individuals reporting feeling happy was relatively high in 1973, 1977, 1994, 2006, and 2012.
-From the overall data, it can be seen that when people have 1 or 2 children, the most common self-rated health statuses are excellent, fair, and good.
-Generally speaking, although with the passage of time, the overall proportion of participation in families with one child is large, but it cannot be said that the number of children will affect the level of health scores.
+In [@fig-three],which shows analysis and visualization of the number of children born each year between 1972 and 2012 in connection to the degree of happiness to offer a more in-depth and complete perspective of the data.
+In 1974, 1985, 1993, 2004, 2006, and 2008, a relatively high percentage of people reported feeling unpleasant concerning the variable "not too happy." On the other hand, the proportion of people reporting being cheerful in 1973, 1977, 1994, 2006, and 2012 was relatively high.
+The data shows that excellent, fair, and sound are the most prevalent self-rated health statuses among adults with one or two children.
+It cannot be claimed that the number of children will impact the health scores, even though participation rates in families with one kid are generally high, even as time goes on.
 
@@
 
-In [@fig-four], which observed that when individuals have one child, there is a significantly higher proportion of participants who rate their health as 'good' or 'excellent' compared to other categories.
-In contrast, for participants who do not have any children, the proportion of those who rate their health as 'poor' is the highest, but no clear conclusion can be drawn from this finding.
-For individuals with three children, the feedback on their health status is evenly distributed among 'good', 'fair', and 'excellent', with a very small proportion of participants reporting 'poor' health.
-Overall, having one child is associated with the highest proportion of participants reporting 'excellent' health status.
+In [@fig-four].When individuals have one child, more participants rate their health as 'good' and 'excellent' compared to other self-health rating categories.
+By contrast, for the individuals who do not have children, the proportion of those who rate their health as "poor" is the highest; however, no clear conclusion can be drawn from this finding.
+For individuals with three children, the feedback on their health status is evenly distributed among "good," "fair," and "excellent," with a tiny proportion of participants reporting "poor" health.
+Overall, having one child is associated with most participants reporting an excellent health status.
 
@@
 
-In [@fig-five], which present the dot plot, which represent the each number of babies in different condition of health, which explores the relationship between health and the number of babies in the family.
-The data is organized into four health categories - 'excellent', 'fair', 'good', and 'poor' - and five categories based on the number of babies, ranging from 0 to 4.The data reveals a pattern suggesting a connection between health status and the number of babies in a family.
-Families with 'excellent' health have a more balanced distribution of babies, with a higher proportion of families having one or two babies compared to those with poorer health.
-This trend indicates that better health is associated with a higher likelihood of having one or more babies.As the number of babies increases, the percentages for all four health categories tend to decrease.
-This pattern is most noticeable in the 'poor' health category, where the decline in percentages is more pronounced as the number of babies increases.In summary, the data suggests a relationship between health and the number of babies in a family.
-Better health is generally associated with a higher likelihood of having one or more babies, while poorer health tends to correlate with a lower likelihood.
-However, it is essential to consider that the relationship may not be linear and that other factors could also influence the number of babies in a family.
+In [@fig-five].
+The association between health and the number of babies in the family is investigated via a dot plot.
+The information is divided into five categories depending on the number of babies, which from 0 to 4, and four categories based on health, including "excellent," "fair," "good," and "poor." from the year of 1970 to the 2010.
+The graph shows a trend that may point to a link between a family's health condition and the number of children they have.
+By comparison; with more kids are born to families with "excellent" health than to those with 'poor' health, with resulting in a more balanced distribution of births.
+As the result; this pattern suggests that having one or more children is more likely when one is in better health self-rate.
+The percentages for all four health categories tend to decline as the number of newborns rises.
+This trend is most apparent in the "poor" health category, where the percentage drop is more dramatic as the number of births rises.
+The information points to a connection between family size and health.
+The chance of having one or more children is often more significant when one is in better health than when one is in worse health.
+But it's important to remember that the link could not be direct and that other variables might also affect how many children a family has.
 
@@
 
-In [@fig-six], which appears that the number of babies in a family is related to the level of financial satisfaction.
-In general, families with lower financial satisfaction, regardless of the category, tend to have a higher number of babies.
-This trend is observed across all three financial satisfaction levels.It is interesting to note that the majority of families in all financial satisfaction levels have 0 babies.
-However, the percentage of families with 0 babies is notably higher in the 'pretty well satisfied' category compared to the 'more or less satisfied' and 'not satisfied at all' categories.As the number of babies increases, the percentages for all three financial satisfaction categories tend to decrease.
-This pattern is more pronounced in the 'pretty well satisfied' category, where the decline in percentages is steeper as the number of babies increases.In summary, the data suggests a connection between financial satisfaction and the number of babies in a family.
-Families with higher financial satisfaction generally have fewer babies, while those with lower financial satisfaction have more babies.
-It is essential to consider that this relationship may not be linear, and other factors could also influence the number of babies in a family.
+In [@fig-six].
+The graph suggests the connection between the number of babies and self financial satisfaction rate.
+Regardless of the group, the less financially satisfied families having one or more children.On the other hand; most families in all financial satisfaction levels have 0 children, which is intriguing.
+In contrast to the more or less content and 'not satisfied at all' categories, the proportion of families with no children is much higher in the 'very well satisfied' group.
+As the number of babies grows, the percentages for all three types of financial satisfaction tend to decrease.
+This trend is evident in the "pretty well satisfied" category, where the percentage decrease is steeper as the number of babies increases.
+In conclusion, the results point to a relationship between family size and financial contentment.
+Families that are more financially satisfied tend to have fewer children, whereas those who are less financially satisfied tend to have more.
+Remember that this link could not be linear and that other variables might affect how many children a family has.
 
@@
 
-In conclusion, the analysis of the data presented in [@fig-one] through [@fig-six] reveals several key findings related to the number of children in a family and its association with happiness, health, and financial satisfaction.
-Overall, families with no children report the highest levels of happiness, but this result could be influenced by the larger sample size of childless families.
-The sex distribution data indicates a higher percentage of females in families with more children, with the most significant differences observed in families with one and four children.
+In conclusion, the data analysis presented in [@fig-one] to [@fig-six] reveals several key findings related to the number of children in a family and its association with happiness, health, and financial satisfaction.
+Overall, the families without children reported that the highest happiness levels, however; the larger sample size of childless families could influence this result.
+The data on gender distribution shows that there are more women in families with more children compared with male.
+The most significant differences between families with one child and those with four children can be seen.
 
-The analysis of health status shows that having one child is associated with the highest proportion of participants reporting 'excellent' health.
-The relationship between health and the number of children suggests that better health is generally associated with a higher likelihood of having one or more children, while poorer health correlates with a lower likelihood.Financial satisfaction also appears to be connected to the number of children in a family, with families with higher financial satisfaction generally having fewer children, while those with lower financial satisfaction have more children.
+On the perspective of analyzing of health status.
+For having one child is linked to most people saying they are in "excellent" health self-rate.
+Moreover; the relationship between health and the number of children suggests with better health is generally associated with a higher likelihood of having one or more children; conversely, "poor" health correlates with a lower likelihood.
+Financial satisfaction is also related to the number of children in a family, with families with higher financial satisfaction generally having fewer children, while at the same time, those with lower financial satisfaction have more children.
 This relationship may not be linear, and other factors could influence the number of children in a family.
 
-It is important to acknowledge the limitations of this analysis, such as the potential influence of various confounding factors and the possibility of non-linear relationships between variables.
-Furthermore, the data may not be representative of all families or cultural contexts, so the findings should be interpreted with caution.
-Nevertheless, this study provides valuable insights into the complex relationships between family size and factors such as happiness, health, and financial satisfaction.
-Future research could explore these relationships in greater depth, considering additional variables, longitudinal data, and diverse populations to provide a more comprehensive understanding of the factors influencing family size and well-being.
+In the limitations of this analysis, such as the possibility that different aspect of confounding factors could have an effect and that the relationships between variables might not be linear.
+In addition, the GSS data may not be representative of all families or cultures, so the results should be taken with care.
+On the other hand; in this study provided the essential information on about how family size affects things like happiness, health, and financial satisfaction.
+On the other hand; in the Future research , which could explore these relationships in greater depth, by considering additional variables, longitudinal data, and diverse populations to understand better the factors influencing family size and well-being.
 
@@
 
-The observation that families with more children have a higher percentage of females, particularly in families with one and four children, highlights the importance of examining the impact of gender distribution within families.
-In many societies, traditional gender roles dictate that women assume primary responsibilities for children, which could lead to a disproportionate burden on women in larger families.
-This unequal distribution of responsibilities might impact women's well-being, including their mental and physical health, career opportunities, and financial stability [@j].
-Moreover, the unequal distribution of resources within families due to gender biases could exacerbate these disparities, further impacting the well-being of women in larger families [@k].
+The observation shows that families with more children have a higher percentage of females, particularly in families with one and four children, in this case , which highlights the importance of examining the impact of gender distribution within families.
+In many societies, traditional gender roles dictated that the women assume primary responsibilities for children, which could lead to a disproportionate burden on women in larger families.
+This unequal distribution of responsibilities might impact women's well-being, including their mental and physical health, career opportunities, and financial stability due to spend on more time on their kid [@j].
+In addition, the unequal distribution of resources within families due to gender biases could exacerbate these disparities, in addition; by impacting the well-being of women in larger families [@k].
 Additionally, societal expectations and norms surrounding gender roles may influence the decision-making process of couples when considering family size.
@@
 
-To gain a more comprehensive understanding of the role of gender in family well-being, future research should examine how gender roles and expectations evolve as family size changes, as well as how these dynamics impact overall happiness, health, and financial satisfaction.
-This research could help inform policies and interventions that promote gender equity within families, ensuring that the well-being of all family members is considered and supported, regardless of family size.
+In order to gain a more comprehensive understanding of the role of gender in family well-being, and future research should have to examine on how the gender roles and expectations evolve as family size changes, in addition to how these dynamics impact overall level of the happiness, health, and financial satisfaction.
 
@@
 
-The study's findings on the positive relationship between financial satisfaction, health, and happiness underscore the importance of financial stability and access to healthcare for overall well-being.
-These findings have important implications for policymakers and practitioners working to improve individuals' quality of life[@d].
-For example, policies aimed at increasing access to affordable healthcare and financial assistance programs can help individuals improve their financial stability and access to essential services, ultimately contributing to overall well-being.
+In this study's findings on the positive relationship between level of the financial satisfaction, health, and happiness the importance of financial stability and access to healthcare for overall well-being.
+In this paper have important implications for policymakers and practitioners working to improve individuals' quality of life[@d].
+For instance; policies aimed at increasing access to affordable healthcare and financial assistance programs can help individuals improve their financial stability and access to essential services.
 
@@
 Overall, this study demonstrates the importance of considering various factors that can influence individuals' well-being and happiness.
-By understanding the complex relationships between different variables, policymakers and practitioners can develop targeted interventions aimed at improving individuals' quality of life.
-Additionally, the findings can serve as a foundation for further research on the topic, particularly in examining changes in these relationships over time.
+Moreover; by understanding the several relationships between different variables, which may can develop targeted interventions aimed at improving individuals' quality of life.
+In addition; this findings can serve as a foundation for further research on the topic in the future ,particularly in examining changes in these relationships over time.
 
@@
 
-The historical context of the early 1970s in the United States is essential in understanding individuals' well-being during that period.
-Societal norms, values, and attitudes during this time were different from those of today, and these differences could have influenced individuals' well-being [@g].
-These social movements may have influenced individuals' attitudes towards social stratification, gender roles, and family dynamics, which, in turn, could have affected their well-being.
+The historical context of the early 1970s in the United States is essential in understanding individuals' well-being during that past period, for example; the Societal norms, values, and the attitudes during this time were different from those of nowadays, and these differences could have influenced individuals' well-being [@g].
+These social movements may have influenced people's attitudes towards social, gender roles, and family dynamics, which in order to affect citizen's well-being.
 
@@
 
-The analysis of the data presented in [@fig-one] and [@fig-five] suggests a relationship between the number of children in a family and the overall happiness and health status of individuals.
-Families with no children seem to have the highest proportion of 'very happy', 'pretty happy', and 'not too happy' responses, although this could be influenced by the larger amount of data collected for childless individuals.
-Furthermore, families with 'excellent' health tend to have a more balanced distribution of children, with a higher likelihood of having one or more children compared to families with poorer health.
+The analysis of the GSS data showed in [@fig-one] and [@fig-five], which suggested the relationship between the number of children in a family and the level of the happiness and health status of individuals.
+In compare; the families with no children seem to have the highest proportion of 'very happy', 'pretty happy' responses rate.
+Although this could be influenced by the larger amount of data collected for childless individuals.
+On the other hand, the families with 'excellent' health tend to have a more balanced distribution of children, with a higher likelihood of having one or more children compared to families with poorer health.
 
-In addition to the relationship between family size and happiness, as well as family size and health, the analysis of data in [@fig-two] also indicates a connection between family size and gender distribution.
-The data suggests that the sex distribution varies depending on the number of babies in the family, with a higher percentage of females compared to males observed across all groups.
-As the number of babies in a family increases, the percentage of females also increases, with the highest difference observed in families with one and four babies.
-In these groups, the sex distribution is more skewed towards females.
-This finding suggests that the presence and number of babies in a family may also influence the gender composition of the family.
+In addition, the relationship between family size and happiness, as well as family size and health.
+The data analysis in [@fig-two] also indicated the relationship between family size and gender distribution.
+This paper suggested that the sex distribution varies depending on the number of babies in the family, with a higher percentage of females than males observed across all groups.
+As the number of babies in a family increases, at the same time, the percentage of females also increases, with the highest difference observed in families with one and four babies.
+By comparison, in these groups, the gender distribution is more skewed towards females.
+This finding suggested that the presence and number of babies in a family may also influence the gender composition of the family.
 
-The data from [@fig-three] and [@fig-four] further supports the relationship between family size, happiness, and health.
-The analysis of the number of children had each year from 1972 to 2012 in relation to the level of happiness shows fluctuations in the proportion of individuals who reported feeling "not too happy" and "happy" over the years.
+On the other hand, the data from [@fig-three] and [@fig-four] supports the relationship between family size, happiness, and health.
+The analysis of the number of children each year from 1972 to 2012 about the level of happiness shows the proportion of individuals who reported feeling "not too happy" and "happy" over the years.
 This finding highlights the potential influence of horticultural and economic factors on happiness and family size over time.
 
-Additionally, the data from [@fig-four] reveals that having one child is associated with the highest proportion of participants reporting 'excellent' health status.
+Additionally, the data from [@fig-four] shows that families with one child are associated with the highest proportion of participants reporting 'excellent' health status.
 This finding might suggest that having a smaller family size could be related to better health outcomes for individuals.
-However, it is crucial to consider other factors that could potentially influence the health status of individuals, such as access to healthcare, lifestyle choices, and overall well-being.
+However, it is crucial to consider other factors that could influence the health status of individuals, such as access to healthcare, lifestyle choices, and overall well-being.
 
-In summary, the relationship between family size and happiness, health, and gender distribution is complex and multifaceted.
-While the data suggests certain trends and connections, it is important to recognize that other factors may also play a role in determining happiness, health, and gender distribution in families with varying numbers of children.
-Further research and analysis are needed to better understand these relationships and to identify potential contributing factors.
+In summary, the relationship between family size and happiness, health, and gender distribution is complex.
+While the data suggested certain trends and relation.
+Therefore;it is important to notice that other factors may also play a key role in determining happiness, health, and gender distribution in families with varying numbers of children.
+In the further research and analysis are needed to better understand these relationships and to identify potential contributing factors.
 
@@
 
-The data from [@fig-six] reveals a connection between financial satisfaction and the number of children in a family.
-In general, families with higher financial satisfaction tend to have fewer children, while those with lower financial satisfaction have more children.
+The data from [@fig-six] shows the connection between level rate of financial satisfaction and the number of children in a family.
+In general, the families with higher financial satisfaction tend to have fewer children, while those with lower financial satisfaction have more children.
 This trend is observed across all three financial satisfaction levels, with the majority of families in all financial satisfaction levels having 0 babies.
@@
 
--   Sample representation: The data used in this analysis may not be representative of all families or cultural contexts, which could limit the generalization of the findings.
-Further research with more diverse samples is needed to ensure the results are applicable across different populations.
--   Confounding factors: The analysis does not account for potential confounding factors that might influence the relationships between the number of children, happiness, health, and financial satisfaction.
-Factors such as age, education, income, and cultural background could play a role in the observed patterns and should be considered in future research.
--   Cross-sectional data: The data used in this analysis is cross-sectional, which makes it challenging to establish causal relationships between variables.
-Longitudinal data would allow for a more in-depth understanding of how the variables change over time and their potential causal relationships.
--   Non-linear relationships: The relationships between the variables in this study may not be linear, and other forms of relationships could exist.
-The analysis could be extended by exploring different types of relationships between variables, such as quadratic or cubic functions.
+-   Sample representation: The GSS data utilized in this analysis might not accurately represent all family structures or cultural environments, potentially restricting the applicability of the findings and outcomes.
+Future research with more varied samples is essential to confirm the relevance of the results across distinct populations.
+-   Confounding factors: This analysis may not consider possible confounding variables that could affect the connections between child count, happiness, health, and financial satisfaction.
+Aspects such as age, education, income, and cultural background might contribute to the observed trends and warrant investigation in subsequent studies.
+-   Cross-sectional data: The employed data in this analysis is cross-sectional, posing difficulties in determining causality between factors.
+Utilizing longitudinal data would facilitate a more comprehensive comprehension of how these variables evolve over time and any potential causal links.
+-   Non-linear relationships: The relationships between the variables in this study may not be linear,in addition; in other forms of relationships could exist.
+This analysis could be extended by exploring different types of relationships between variables, such as quadratic or cubic functions.
 
@@
 
--   Diversify the sample: Conduct further research with more diverse samples, including participants from different cultural backgrounds, age groups, and socioeconomic statuses, to better understand the relationships between the number of children, happiness, health, and financial satisfaction across various populations.
--   Consider potential confounding factors: Future research should consider potential confounding factors that might influence the relationships between variables.
-By controlling for these factors, the analysis would provide a clearer understanding of the true relationships between the number of children and happiness, health, and financial satisfaction.
--   Longitudinal data analysis: Collect and analyze longitudinal data to establish causal relationships between variables and observe how these relationships change over time.
-This approach would provide a more comprehensive understanding of the factors influencing family size and well-being.
--   Explore non-linear relationships: Expand the analysis to consider non-linear relationships between the variables in the study.
-By exploring different types of relationships, the research could provide a more nuanced understanding of how the number of children, happiness, health, and financial satisfaction are interconnected.
--   Investigate additional variables: Consider other variables that might influence family size and well-being, such as parenting styles, social support networks, and access to childcare.
-Incorporating these additional variables in the analysis could provide a more holistic understanding of the factors that contribute to family well-being.
+-   Diversify the sample: Undertake further studies using more varied samples, encompassing participants from distinct cultural backgrounds, age brackets, and socioeconomic statuses.
+This will enhance the comprehension of the relationships between child count, happiness, health, and financial satisfaction across diverse populations.
+-   Consider potential confounding factors: Subsequent research should address potential confounding variables influencing the relationships between factors.
+By adjusting for these elements, the analysis can offer a clearer insight into the genuine associations between child count and happiness, health, and financial satisfaction.
+-   Longitudinal data analysis: Gather and evaluate longitudinal data to identify causal connections between variables and monitor how these associations evolve over time.
+This method will yield a more thorough understanding of the factors affecting family size and well-being.
+-   Examine non-linear relationships: Broaden the analysis to include non-linear connections between the study's variables.
+Investigating various relationship types can deliver a more intricate understanding of how child count, happiness, health, and financial satisfaction interrelate.
+-   Investigate additional variables: Consider other factors that may impact family size and well-being, such as parenting approaches, social support networks, and childcare accessibility.
+Integrating these extra variables into the analysis can offer a more comprehensive view of the factors contributing to family well-being.
 

### 2023-04-11 scripts/01-download_data.R

@@ -1,0 +1,31 @@
+
+#### Preamble ####
+# Purpose:The General Social Survey (GSS) is a comprehensive survey conducted in the United States since 1972 to 2012, 
+#providing insight into various social and demographic trends and attitudes. Accessing and analyzing the data 
+#requires downloading the data package from the GSS website and cleaning and processing the data to select relevant 
+#variables for the research question. This may involve dropping irrelevant variables, transforming or recording variables, 
+#and creating new variables. Once the data cleaning is complete, the selected variables can be analyzed using statistical software 
+#or other analytically tools to explore patterns and relationships. Despite being a valuable source of information, careful attention #
+#to data cleaning and analysis is crucial to ensure the validity and reliability of the findings.
+# Author: shaohan chang
+# Date: 4 April 2023
+# Contact: shaohan.chang@utoronto.ca
+# License: MIT
+# Pre-requisites: Download all the packages under the Work space section
+# Any other information needed? None
+
+
+#### Work space setup ####
+library(haven)
+library(tidyverse)
+
+#### Download data ####
+raw_data <- read_dta("inputs/data/gss7221_r3b.dta")
+
+raw_data <-
+  labelled::to_factor(raw_data)
+
+
+#### Save data ####
+# change the_raw_data to whatever name you assigned when you downloaded it.
+write_csv(raw_data, "inputs/data/raw_data.csv") 

### 2023-04-11 scripts/02-data_cleaning.R

@@ -1,0 +1,114 @@
+#### Preamble ####
+# Purpose: The purpose of the final line write_csv(data, "inputs/data/cleaned_data.csv") is to save the 
+#cleaned and transformed data into a CSV file named "cleaned_data.csv" in the directory "inputs/data". 
+#This line is saving the cleaned data as a CSV file so that it can be easily loaded and used in future 
+#analysis or modeling.This is a good practice because it ensures that the cleaned data can be easily accessed
+#and used later on without having to repeat the cleaning and transformation process every time. It also allows 
+#for easier sharing of the cleaned data with others who may need to use it.
+# Author: SHAOHAN CHANG  
+# Date: 14 March 2023 
+# Contact: SHAOHAN.CHANG@utoronto.ca 
+# License: MIT
+# Pre-requisites:
+## 1. Go to the GSS website by entering https://gss.norc.org/get-the-data/stata into your web browser.
+## 2.Scroll down the page until you find the "Stata Data" section, and then click on the "Download the GSS Stata data files" link.
+## 3. Select the years of interest from the list provided, and if you need to download multiple years, hold down the "Ctrl" key while clicking to select each year.
+## 4. Click the "Download Selected Files" button located at the bottom of the page. 
+## 5. On the next page, select the "Stata" file format.
+## 6. To download all variables, choose "ALL" from the drop-down menu next to the green "ALL" button.
+## 7. Click the "Create File" button and wait for the file to be generated. This may take a few moments, depending on the size of the file and your internet connection.
+## 8. Once the file has been created, click the "Download File" button to save it to your computer. Make sure to save the file in a location where you can easily find it later.
+
+# Any other information needed?
+## 1. Take note of the file path where the downloaded data file is saved on your computer, as this information is necessary to read the data into R.
+## 2. Keep in mind that the GSS data file can be quite large, especially if you have downloaded multiple years of data. To work with it more efficiently, consider filtering the data to a specific time period or a subset of variables using functions like subset() or dplyr::select().
+## 3. Because the downloaded data file is in Stata format, you'll need to use a package like "haven" or "foreign" to read the data into R. For example, you can use the haven::read_dta() function.
[…]

### 2023-04-12 outputs/paper/paper.qmd
Minor changes

@@
 author: 
-  - SHAOHAN CHANG
+  - Shaohan Chang
 thanks: "Code and data are available at: https://github.com/lucas11333/Of_Wellbeing"
@@
 
-This following data analysis is processed in R [@R] with packages of tidyverse [@ti], dplyr [@dplyr], janitor [@janitor] , knitr [@knitr], here [@here], haven [@haven], ggplot [@ggplot] , kableExtra [@kableExtra] , model summary [@modelsummary] to assist in data analysis, and the data from General Social Survey [@gss].
+This following data analysis is processed in `R` [@R] with packages of `tidyverse` [@ti], `dplyr` [@dplyr], `janitor` [@janitor], `knitr` [@knitr], `here` [@here], `haven` [@haven], `ggplot` [@ggplot], `kableExtra` [@kableExtra], `modelsummary` [@modelsummary] to assist in data analysis, and the data from General Social Survey [@gss].
 
@@
 
-The following table shows the first five rows of data and their corresponding parameters.The following data section provides a more detailed explanation of the selected variables for the data.
+This section provides a more detailed explanation of the selected variables for the data.
 
@@
 library(modelsummary)
+
 data <- read_csv(here::here("inputs/data/cleaned_data.csv"))
@@
 
-In @tbl-var contains information on various personal and demographic characteristics of individuals, collected between the years 1972 and 2012.
+@tbl-var illustrates the nature of the data-set.
+The data-set contains information on various personal and demographic characteristics of individuals, collected between the years 1972 and 2012.
 The data-set comprises of 10 variables, namely age, sex, number of babies, divorce status, self-reported health status, financial satisfaction, level of happiness, and additional variables.
@@
 #| label: tbl-var
-#| tbl-cap: Report Data (First 5 rows)
+#| tbl-cap: First five rows of the dataset, for illustrative purposes
+
 data %>%
@@
   slice(1:5) %>%
-  kable() %>%
-  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
-
+  kable(
+    col.names = c(
+      "Year",
+      "Sex",
+      "No. of children",
+      "Self-reported health",
+      "Financial satisfaction",
+      "Happiness"
+    ),
+    booktabs = TRUE,
+    linesep = ""
+  )
 ```
 
-```{r}
-#| echo: false
-#| warning: false
-data %>%
-  select(7:10) %>%
-  slice(1:5) %>%
-  kable() %>%
-  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
-```
-
--   year: This variable indicates the year in which the data was collected from GSS. In this data-set, all the observations are from the year of 1972 to 2012.
--   sex: Categorical variable with two levels: male and female.
--   babies: Integer variable with different levels, depending on the number of babies, for instance : 0, 1, 2, 3, 4, or 5+.
--   health: This variable indicates the self-reported health status of the individual at the time.
+-   "year": This variable indicates the year in which the data was collected from GSS. In this data-set, all the observations are from the year of 1972 to 2012.
+-   "sex": Categorical variable with two levels: male and female.
+-   "babies": Integer variable with different levels, depending on the number of babies, for instance : 0, 1, 2, 3, 4, or 5+.
+For analysis purposes we construct "babies_number".
+The babies_number variable is an ordinal variable denoting the number of babies an individual in the dataset has.
+It ranges from 0 to 4, where 0 represents "0" babies, 1 denotes "1" baby, 2 signifies "2" babies, 3 indicates "3" babies, and 4 refers to "4" babies.
+The value 5 is reserved for any unclassified or missing responses.
+-   "health": This variable indicates the self-reported health status of the individual at the time.
 It is a categorical variable with different levels, depending on the health status, for example : excellent, good, fair, or poor.
--   finance_satisfied: This variable indicates the individual's different level of satisfaction with their current financial situation.
-It is a categorical variable with different satisfaction levels: very satisfied, more or less satisfied, not very satisfied, and not at all satisfied.
--   happy: This variable indicates the individual's level of happiness or life satisfaction. It is a categorical variable with different levels of happiness: very happy, pretty happy, not too happy.
--   happy_score: The happy_score variable is an integer that represents the individuals in the dataset's self-reported happiness levels.
-Its sign ranges from 0 to 3, with 0 denoting "not too happy," 1 denoting "happy," 2 denoting "very happy," and 3 holding any unclassified or missing responses.
--   health_score: The health_score variable is an ordinal variable shows the self-reported health status of the individuals, which sign the ranges from 1 to 4.
+We also use an analogous "health_score", which is an ordinal variable shows the self-reported health status of the individuals, which sign the ranges from 1 to 4.
 With 1 denoting "poor" health, 2 signifying "fair" health, 3 representing "good" health, and 4 referring to "excellent" health.
 The value 5 is reserved for any unclassified or missing responses.
--   finance_score: This ordinal variable represents the financial satisfaction level of the individuals in the dataset.
+-   "finance_satisfied": This variable indicates the individual's different level of satisfaction with their current financial situation.
+It is a categorical variable with different satisfaction levels: very satisfied, more or less satisfied, not very satisfied, and not at all satisfied.
+We also develop the analogous "finance_score".
+This ordinal variable represents the financial satisfaction level of the individuals in the dataset.
 It ranges from 1 to 3, with 1 indicating "Not at all satisfied," 2 denoting "more or less satisfied," and 3 signifying "pretty well satisfied." The value 4 is reserved for any unclassified or missing responses.
--   babies_number: The babies_number variable is an ordinal variable denoting the number of babies an individual in the dataset has.
-It ranges from 0 to 4, where 0 represents "0" babies, 1 denotes "1" baby, 2 signifies "2" babies, 3 indicates "3" babies, and 4 refers to "4" babies.
-The value 5 is reserved for any unclassified or missing responses.
+-   "happy": This variable indicates the individual's level of happiness or life satisfaction.
+It is a categorical variable with different levels of happiness: very happy, pretty happy, not too happy.
+We create an analogous happiness score ""happy_score".
+The happy_score variable is an integer that represents the individuals in the dataset's self-reported happiness levels.
+Its sign ranges from 0 to 3, with 0 denoting "not too happy," 1 denoting "happy," 2 denoting "very happy," and 3 holding any unclassified or missing responses.
 
@@
 
-In [@fig-one],which analysis explores the relationship between the number of children in a family and happiness levels, categorized as 'very happy,' 'pretty happy,' and 'not too happy.' Although childless families show the highest numbers in each happiness category, the data collected for such families is more abundant, necessitating an analysis of happiness proportions within each family size.
+@fig-one explores the relationship between the number of children in a family and happiness levels, categorized as 'very happy,' 'pretty happy,' and 'not too happy.' Although childless families show the highest numbers in each happiness category, the data collected for such families is more abundant, necessitating an analysis of happiness proportions within each family size.
 The findings reveal no linear correlation between the number of children and overall family happiness, with happiness varying across family sizes without a consistent pattern.
@@
 #| warning: false
+
 data %>%
@@
         legend.position = "bottom")
-
 ```
 
-In [@fig-two], as presented in the bar chart, the gender distribution varies depending on the number of babies in the family.
+@fig-two illustrates how gender distribution varies depending on the number of babies in the family.
 By comparison, a higher percentage of females than males is consistently observed across all groups.
@@
         legend.position = "bottom")
-
 ```
 
-In [@fig-three],which shows analysis and visualization of the number of children born each year between 1972 and 2012 in connection to the degree of happiness to offer a more in-depth and complete perspective of the data.
+@fig-three shows analysis and visualization of the number of children born each year between 1972 and 2012 in connection to the degree of happiness to offer a more in-depth and complete perspective of the data.
 In 1974, 1985, 1993, 2004, 2006, and 2008, a relatively high percentage of people reported feeling unpleasant concerning the variable "not too happy." On the other hand, the proportion of people reporting being cheerful in 1973, 1977, 1994, 2006, and 2012 was relatively high.
@@
   geom_bar(position = "fill") +
-  facet_wrap(~health, ncol = 5, scales = "free_y") +
+  facet_wrap(~health, nrow = 5, scales = "free_y") +
   labs(x = "Year", y = "Percentage of Babies", fill = "Number of Babies") +
@@
         panel.spacing = unit(0.2, "lines"))
-
 ```
@@
 
-In [@fig-four].When individuals have one child, more participants rate their health as 'good' and 'excellent' compared to other self-health rating categories.
+@fig-four shows that when individuals have one child, more participants rate their health as 'good' and 'excellent' compared to other self-health rating categories.
 By contrast, for the individuals who do not have children, the proportion of those who rate their health as "poor" is the highest; however, no clear conclusion can be drawn from this finding.
@@
 
-In [@fig-five].
-The association between health and the number of babies in the family is investigated via a dot plot.
+@fig-five illustrates the association between health and the number of babies in the family is investigated via a dot plot.
 The information is divided into five categories depending on the number of babies, which from 0 to 4, and four categories based on health, including "excellent," "fair," "good," and "poor." from the year of 1970 to the 2010.
@@
 ggplot(data[data$happy == "very happy", ], aes(x = year, y = factor(babies))) +
-  geom_point(position = position_jitter(width = 0.2, height = 0.1), size = 2, color = "#4daf4a") +
+  geom_point(position = position_jitter(width = 0.2, height = 0.1), alpha = 0.3, size = 2, color = "#4daf4a") +
   facet_wrap(~health, ncol = 5, scales = "free_y") +
@@
 
-In [@fig-six].
-The graph suggests the connection between the number of babies and self financial satisfaction rate.
+@fig-six suggests the connection between the number of babies and self financial satisfaction rate.
 Regardless of the group, the less financially satisfied families having one or more children.On the other hand; most families in all financial satisfaction levels have 0 children, which is intriguing.
@@
 #| warning: false
+
 ggplot(data, aes(x = finance_satified, fill = factor(babies))) +
@@
   coord_flip()
-
 ```
 
-# Model : Linear Regression
+# Model
+
+We use linear regression to estimate the following equation:
 
@@
 
-In conclusion, the data analysis presented in [@fig-one] to [@fig-six] reveals several key findings related to the number of children in a family and its association with happiness, health, and financial satisfaction.
+In conclusion, the data analysis presented in @fig-one to @fig-six reveals several key findings related to the number of children in a family and its association with happiness, health, and financial satisfaction.
 Overall, the families without children reported that the highest happiness levels, however; the larger sample size of childless families could influence this result.
@@
 
-## Table of Relationship between Number of Children and Gender.
+## Relationship between the number of children and their gender.
 
-In the @tbl-sex, which presented in the table indicate that the sex distribution varies depending on the number of babies in the family.Across all groups, there is a consistent pattern of a higher percentage of females compared to males.
+@tbl-sex indicates that the sex distribution varies depending on the number of babies in the family.
+Across all groups, there is a consistent pattern of a higher percentage of females compared to males.
 The lowest difference in sex distribution is observed among families with no babies, where the female-to-male ratio is relatively closer 54.53% female vs.
@@
 #| warning: false
+
 sex_table <- data %>% 
@@
   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
-
 ```
 
-## Distribution of Happiness Levels Across Families with Different Numbers of Babies
+## Happiness between families with different numbers of babies
 
-In the @tbl-happ, which suggests that families with 4 babies have the highest proportion of "happy" individuals at 63.41%.
-In contrast, families with 3 babies have the highest proportion of "not too happy" individuals at 16.57% and the lowest proportion of "happy" individuals at 50.30%.
+@tbl-happ suggests that families with 4 babies have the highest proportion of "happy" individuals at 63%.
+In contrast, families with 3 babies have the highest proportion of "not too happy" individuals at 16% and the lowest proportion of "happy" individuals at 50%.
 Families with 0, 1, and 2 babies have relatively similar distributions of happiness levels.
-It is worth noting that families with 3 babies have the highest proportion of "very happy" individuals at 33.14%, followed closely by families with 2 babies at 32.95%.
-Families with 4 babies have the lowest proportion of "very happy" individuals at 24.39%.
+It is worth noting that families with 3 babies have the highest proportion of "very happy" individuals at 33%, followed closely by families with 2 babies at 32%.
+Families with 4 babies have the lowest proportion of "very happy" individuals at 24%.
 
@@
 #| warning: false
+
 happy_table <- data %>% 
@@
   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
-
 ```
 
-## Distribution of Self-Rated Health Status Across Families with Different Numbers of Babies
+## Self-rated health and the number of babies
 
-In @tbl-heal, which appears suggests that individuals without any babies tend to have higher percentages in all health categories, especially in the "poor" health category (93.52%).
+In @tbl-heal, which appears suggests that individuals without any babies tend to have higher percentages in all health categories, especially in the "poor" health category (93%).
 As the number of babies in a family increases, the proportion of individuals in the "excellent," "fair," and "good" health categories generally decreases.
@@
 #| warning: false
+
 health_happy_table <- data %>%
@@
   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
-
 ```
@@
 
-In @tbl-fin, which appears suggests that families with 0 babies have the highest percentages of financial satisfaction across all categories.
+@tbl-fin suggests that families with 0 babies have the highest percentages of financial satisfaction across all categories.
 As the number of babies in a family increases, the proportion of families in each financial satisfaction category generally decreases.
@@
 
-The analysis of the GSS data showed in [@fig-one] and [@fig-five], which suggested the relationship between the number of children in a family and the level of the happiness and health status of individuals.
+The analysis of the GSS data showed in @fig-one and @fig-five, which suggested the relationship between the number of children in a family and the level of the happiness and health status of individuals.
 In compare; the families with no children seem to have the highest proportion of 'very happy', 'pretty happy' responses rate.
@@
 In addition, the relationship between family size and happiness, as well as family size and health.
-The data analysis in [@fig-two] also indicated the relationship between family size and gender distribution.
+The data analysis in @fig-two also indicated the relationship between family size and gender distribution.
 This paper suggested that the sex distribution varies depending on the number of babies in the family, with a higher percentage of females than males observed across all groups.
@@
 
-On the other hand, the data from [@fig-three] and [@fig-four] supports the relationship between family size, happiness, and health.
+On the other hand, the data from @fig-three and @fig-four supports the relationship between family size, happiness, and health.
 The analysis of the number of children each year from 1972 to 2012 about the level of happiness shows the proportion of individuals who reported feeling "not too happy" and "happy" over the years.
@@
 
-Additionally, the data from [@fig-four] shows that families with one child are associated with the highest proportion of participants reporting 'excellent' health status.
+Additionally, the data from @fig-four shows that families with one child are associated with the highest proportion of participants reporting 'excellent' health status.
 This finding might suggest that having a smaller family size could be related to better health outcomes for individuals.
@@
 
-The data from [@fig-six] shows the connection between level rate of financial satisfaction and the number of children in a family.
+The data from @fig-six shows the connection between level rate of financial satisfaction and the number of children in a family.
 In general, the families with higher financial satisfaction tend to have fewer children, while those with lower financial satisfaction have more children.
@@
 
-## Weakness:
+## Weakness
 
@@
 
-## Next Steps:
+## Next Steps
 
@@
 
-NAME : SHAOHAN CHANG Institution/Department : Department of statistics (University of Toronto) Email Address : shaohan.chang\@utoronto.ca
+NAME : SHAOHAN CHANG Institution/Department : Department of Statistical Sciences (University of Toronto) Email Address : shaohan.chang\@utoronto.ca
 

### 2023-04-12 scripts/00-simulate_data.R

@@ -1,40 +1,39 @@
 #### Preamble ####
-# Purpose: generate a simulated dataset with 100 observations, where each observation contains information 
-#about an individual's demographics, well-being, and satisfaction levels. The purpose of this simulated dataset 
+# Purpose: generate a simulated dataset with 100 observations, where each observation contains information
+#about an individual's demographics, well-being, and satisfaction levels. The purpose of this simulated dataset
 #is to explore relationships and trends among the variables, which can be useful for research, analysis, or practice
 #in understanding factors that may affect people's lives.
 # Author: shaohan chang
 # Date: 4 April 2023
 # Contact: shaohan.chang@utoronto.ca
 # License: MIT
-# Pre-requisites: Download package of tidyverse 
+# Pre-requisites: Download package of tidyverse
 # Any other information needed? None
 
+#### Work space setup ####
 library(tidyverse)
 
 #### Simulate data ####
-set.seed(123) # set seed for reproducibility
-
-# generate 100 observations
+set.seed(123)
 n <- 100
 
-# generate year variable (1972 to 2021)
+# Generate individual variables
 year <- sample(1972:2021, n, replace = TRUE)
-
-# generate sex variable
 sex <- sample(c("female", "male"), n, replace = TRUE)
-
-# generate babies variable (0 to 5)
 babies <- sample(0:5, n, replace = TRUE)
+health <-
+  sample(c("excellent", "good", "fair", "poor"), n, replace = TRUE)
+finance_satisfaction <-
+  sample(c(
+    "not satisfied at all",
+    "more or less satisfied",
+    "pretty well satisfied"
+  ),
+  n,
+  replace = TRUE)
+happiness <-
+  sample(c("not too happy", "happy", "very happy"), n, replace = TRUE)
 
-# generate health variable
-health <- sample(c("excellent", "good", "fair", "poor"), n, replace = TRUE)
-
-# generate finance_satisfaction variable
-finance_satisfaction <- sample(c("not satisfied at all", "more or less satisfied", "pretty well satisfied"), n, replace = TRUE)
-
-# generate happiness variable
-happiness <- sample(c("not too happy", "happy", "very happy"), n, replace = TRUE)
-
-# create a data frame with the generated variables
-simulated_data <- data.frame(year, sex, babies, health, finance_satisfaction, happiness)
+# Bring them together
+simulated_data <-
+  tibble(year, sex, babies, health, finance_satisfaction, happiness)

### 2023-04-12 scripts/01-download_data.R

@@ -1,14 +1,12 @@
-
 #### Preamble ####
-# Purpose:The General Social Survey (GSS) is a comprehensive survey conducted in the United States since 1972 to 2012, 
-#providing insight into various social and demographic trends and attitudes. Accessing and analyzing the data 
-#requires downloading the data package from the GSS website and cleaning and processing the data to select relevant 
-#variables for the research question. This may involve dropping irrelevant variables, transforming or recording variables, 
-#and creating new variables. Once the data cleaning is complete, the selected variables can be analyzed using statistical software 
-#or other analytically tools to explore patterns and relationships. Despite being a valuable source of information, careful attention #
-#to data cleaning and analysis is crucial to ensure the validity and reliability of the findings.
+# Purpose:The General Social Survey (GSS) is a comprehensive survey conducted in 
+# the United States since 1972 to 2012, providing insight into various social 
+# and demographic trends and attitudes. Accessing and analyzing the data requires 
+# downloading the data package from the GSS website and cleaning and processing 
+# the data to select relevant variables for the research question. This is a manual
+# process. Here we assume the dataset has been saved into `inputs/data/gss7221_r3b.dta`.
 # Author: shaohan chang
-# Date: 4 April 2023
+# Date: 12 April 2023
 # Contact: shaohan.chang@utoronto.ca
 # License: MIT
 # Pre-requisites: Download all the packages under the Work space section
@@ -25,7 +23,5 @@ raw_data <- read_dta("inputs/data/gss7221_r3b.dta")
 raw_data <-
   labelled::to_factor(raw_data)
 
-
 #### Save data ####
-# change the_raw_data to whatever name you assigned when you downloaded it.
 write_csv(raw_data, "inputs/data/raw_data.csv") 

### 2023-04-12 scripts/02-data_cleaning.R

@@ -1,19 +1,19 @@
 #### Preamble ####
-# Purpose: The purpose of the final line write_csv(data, "inputs/data/cleaned_data.csv") is to save the 
-#cleaned and transformed data into a CSV file named "cleaned_data.csv" in the directory "inputs/data". 
-#This line is saving the cleaned data as a CSV file so that it can be easily loaded and used in future 
+# Purpose: The purpose of the final line write_csv(data, "inputs/data/cleaned_data.csv") is to save the
+#cleaned and transformed data into a CSV file named "cleaned_data.csv" in the directory "inputs/data".
+#This line is saving the cleaned data as a CSV file so that it can be easily loaded and used in future
 #analysis or modeling.This is a good practice because it ensures that the cleaned data can be easily accessed
-#and used later on without having to repeat the cleaning and transformation process every time. It also allows 
+#and used later on without having to repeat the cleaning and transformation process every time. It also allows
 #for easier sharing of the cleaned data with others who may need to use it.
-# Author: SHAOHAN CHANG  
-# Date: 14 March 2023 
-# Contact: SHAOHAN.CHANG@utoronto.ca 
+# Author: SHAOHAN CHANG
+# Date: 14 March 2023
+# Contact: SHAOHAN.CHANG@utoronto.ca
 # License: MIT
 # Pre-requisites:
 ## 1. Go to the GSS website by entering https://gss.norc.org/get-the-data/stata into your web browser.
 ## 2.Scroll down the page until you find the "Stata Data" section, and then click on the "Download the GSS Stata data files" link.
 ## 3. Select the years of interest from the list provided, and if you need to download multiple years, hold down the "Ctrl" key while clicking to select each year.
-## 4. Click the "Download Selected Files" button located at the bottom of the page. 
+## 4. Click the "Download Selected Files" button located at the bottom of the page.
 ## 5. On the next page, select the "Stata" file format.
 ## 6. To download all variables, choose "ALL" from the drop-down menu next to the green "ALL" button.
 ## 7. Click the "Create File" button and wait for the file to be generated. This may take a few moments, depending on the size of the file and your internet connection.
@@ -29,24 +29,21 @@
 #### Work space setup ####
 library(tidyverse)
 library(janitor)
-library(tidyverse)
 
 #### Clean data ####
 the_raw_data <- read_csv("inputs/data/raw_data.csv")
 
-data <- 
+data <-
   the_raw_data |>
-  select(
[…]

### 2023-04-12 scripts/03-test_data.R

@@ -14,45 +14,34 @@
 
 #### Work space setup ####
 library(tidyverse)
-library(janitor)
-library(dplyr)
-
 
 #### Test data ####
-
-
 data <- 
-  readr::read_csv("inputs/data/cleaned_data.csv")
+  read_csv("inputs/data/cleaned_data.csv")
 
 # Test One : Check for NA values in the data frame.
 # Explanation : as the result , there 0 NA value. 
-
 check_result <- ifelse(sum(is.na(data)) == 0, "Check passed", "Check failed")
 print(check_result)
 
 
 # Test Two : Check for NA values in happy. 
-
 # Explanation :  Three are 0 missing values in the happy. 
-
 check_result <- ifelse(sum(is.na(data$happy)) == 0, "Check passed", "Check failed")
 print(check_result)
 
 
 # Test Three : Check for NA values in year.
 # Explanation :There are 0 missing values in the year variable. 
-
 check_result <- ifelse(sum(is.na(data$year)) == 0, "Check passed", "Check failed")
 print(check_result)
 
 # Test Four : Check for NA values in sex. 
 # Explanation :There are 0 missing values in the sex variable.
-
 check_result <- ifelse(sum(is.na(data$sex)) == 0, "Check passed", "Check failed")
 print(check_result)
 
 # Test Five : Check for NA values in health. 
 # Explanation :There are 0 missing values in the health variable.
-
 check_result <- ifelse(sum(is.na(data$degree)) == 0, "Check passed", "Check failed")
 print(check_result)
